### 2020-03-11 tex/abstract.tex
first writeup draft

\begin{abstract}
This document introduces several aspects related to the confirm activity problem in 
the NuCypher KMS network. These include the current adopted solution, its relation 
with both the fees and the inflation rewards, and three potential solutions that can be 
used to provide a proof that an Ursula has served a specific number of re-encryption 
requests within a given a period. We argue that the latter is a better option to be used 
for computing the fees that Alice paid for an Ursula in the network, but not for 
computing the inflation rewards.
\end{abstract}

### 2020-03-11 tex/future-work.tex
first writeup draft

\section{Future Work}
\label{future-work}
Most of the future work on the confirm service activity issue 
will be dedicated to construct a concrete PCD-based solution. This 
includes the following:
\begin{itemize}
\item Understand PCD and its applications in a greater depth. This 
also requires exploring NIZK in general and SNARKs in specific.

\item Define an efficient output correctness predicate that characterizes 
the correctness of the statement that PCD will attest for. This could be 
hard for the confirm activity issue as the value of the output is dynamic 
based on the workload Ursula may receive.

\item Define a way to compose the proofs efficiently and produce 
a single proof at the end. This will be tied to the formulated predicate.

\item Argue about the correctness and security of the concrete scheme.
\end{itemize}

The above will take time, but the good news that this will be also helpful 
to the work on PPSC. So it is more like developing part of the  
background needed for PPSC.

### 2020-03-11 tex/intro.tex
first writeup draft

\section{Introduction}
\label{intro}
NuCypher KMS~\cite{egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral  scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
a ciphertext encrypted under Alice's public key into a ciphertext under the delegatee's, or Bob's,  
public key. This enables the latter to decrypt the data without revealing anything about the 
encryption keys or the raw data to the intermediate servers.

Joining the NuCypher network is governed by consensus rules defining the service setup 
and the monetary incentives paid to provide the service. In order to join the 
system, an Ursula needs to stake an amount of NU tokens for a specific period 
and will be released when the pre-specified staking period is over. Alice chooses an  
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. As such, the stake value influences the amount of service load Ursula 
may receive. This stake is also used to punish Ursula financially, by revoking part 
of it, when cheating is detected.

Alice joins the network by creating a policy to be implemented by a 
set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
need to answer requests coming from Bob(s), as well as the duration of the policy, which 
is basically the timeframe curing which Bob is authorized to access Alice's data.  Furthermore, 
Alice will lock an amount of Ether into the policy to be used to pay Ursula for the re-encryption 
service. As noted, Alice is not exposed to the NU token. All what she needs is an Ethereum 
wallet, being aware of the NuCypher network architecture to select Ursulas, and knowing the 
NuCypher rules of preparing access control policies.

Bob, on the other hand, does not deal with currency in the system. It interacts with the storage 
network to retrieve the encrypted data, and with Ursulas in the NuCypher network to ask for the  
re-encryption service.

\subsection{Monetary Incentives in the NuCypher KMS Network}
Ursulas are rewarded for the re-encryption service by using two sources; 
the first is the service fees collected from the policy or data 
owner Alice, while the second is an inflation rewards, i.e., newly minted 
NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage 
adoption. It is expected that these rewards will disappear as the token cap is 
reached, much similar to other cryptocurrencies out there.

Currently, the inflation rewards are computed for each Ursula based on the number of 
active policies it holds conditioned on being online during the period of each of these 
policies. Confirming the status of being online is done by having each Ursula call a 
simple function in one of the NuCypher contracts to signal that she is around.

Same for the fees, Ursula will collect some of the Ether locked by Alice at the end 
of the policy duration given that this Ursula stays online for the whole duration. 
Again, the latter is tracked by watching the confirm activity function calls Ursula 
make during the policy period.

\subsection{Problems with Current Reward Computation Approach}
The current approach of computing Ursula's rewards suffers from two 
main problems: 
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation is agnostic to the number of 
requests Ursula serves. Thus an active Ursula who may serve a huge number of 
requests, and an idle one who does not receive any requests (or a 
malicious Ursula that does not answer the requests she receives from Bob), will 
both collect the same rewards if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
an stay offline offline, not answering any Bob, and be online just to call the confirm activity 
function. This allows Ursula to collect both inflation rewards 
and fees without doing anything, and even worse, it will be able to get her stake back at 
the end of a policy duration.
\end{itemize}

\subsection{Proposed Solutions}
We need a provably secure mechanism to be used by Ursula to report the 
number of distinct Bob requests it handled during a specific period, and use this number 
to compute the fees to be collected from Alice. Thus, we call this confirm 
service activity, as opposed to confirm activity that refers to solely being available 
online.

Although we can use the number of served requests to compute the inflation 
rewards as well, this will encourage Ursula to collude with Bob to issue large 
number of requests. Even it may encourage Ursula to deploy its own Alice(s) 
and Bob(s) to increase the demand, and thus, the cut of the inflation rewards.

In this document, we introduce several solutions for confirming service activity. 
These solutions differ in the trust, efficiency, interactivity, and resource 
requirements, in addition to their security guarantees. We present each of these 
solution, where one of them is still a work in progress, discuss the aforementioned 
trade-offs and requirements of each of them, with the goal of selecting one of these 
solutions to be adopted in the NuCypher network.

\subsection{Roadmap}
The rest of this document is organized as follows. Section~\ref{threat-network-model} 
outlines the network and threat models adopted by the proposed solutions. 
Section~\ref{prelim} provides an overview of the underlying cryptographic primitives and 
protocols, while the proposed solutions are presented 
in Section~\ref{solutions} with their security and efficiency aspects analyzed in 
Section~\ref{analysis}. Lastly, directions of future work on the confirm activity issue 
are outlined in Section~\ref{future-work}.

### 2020-03-11 tex/prelim.tex
first writeup draft

\section{Preliminaries}
\label{prelim}
This section provides an overview of two concepts that we use in the 
proposed solutions. These include the framework of proof carrying data (PCD) 
and the collective signing (CoSi) protocol.

\subsection{Proof Carrying Data (PCD)}
The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
computation involving untrusted parties. It produces a single proof for the output 
that attests not only the correctness of the final result, but also 
the correctness of the entire history of intermediate computations that produced 
this result. Correctness here is defined as a polynomially computable predicate that 
abstracts the properties, or invariants, that must be satisfied.

\begin{figure}[h!]
\centerline{
\includegraphics[height= 1.3in, width = 1.0\columnwidth]{figures/pcd-diagram.pdf}}
\caption{An example of a PCD application. A distributed computation involving parties $P_i$, for 
$i \in \{1, \dots, 6\}$, each 
of which has a local input $x_i$ and produces an output $y_i$ with a proof $\pi_i$. }
\label{pcd-diagram}
\end{figure}

To clarify how PDC works, consider a distributed computation task that involves 
the set of parties shown in Figure~\ref{pcd-diagram}. Party $P_1$ starts the computation with its 
own input, produces an intermediate output with a proof saying that it performed 
the computation as defined by the protocol. It then sends both the output and the proof 
to the next party, which is $P_2$ in this case. Here, $P_2$ will 
have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) 
as input to the computation it will perform. Similarly, $P_2$ will produce another 
intermediate output and a proof. This proof not only attests to the correctness of the 
computation done by $P_2$, but also the history that lead to the result $y_2$. In other 
words, it implicitly includes 
the proof from $P_1$. The same process continues until the full computation is finished. 
Anyone can verify the correctness or compliance of the whole distributed protocol by 
only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.

As shown, PCDs enable untrusted parties to work with each other in a fully distributed 
fashion, without overwhelming the system with the storage and verification of individual 
proofs for each step of the performed protocol. Also, they attest to correctness or compliance  
to the prescribed protocol without re-executing any of the intermediate computations. Thus, 
they provide a promising paradigm for confirming service activity in a compact way.

\subsection{Collective Signing (CoSi)}
\label{cosi}
CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
statement together in a way that produces a single signature. As such, both the 
verification time and the space requirements are just like having a single signer. The 
difference is that this signature attests that all parties agree with the signed 
statement instead of only one.

CoSi builds upon Schnorr 
multisignatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines 
them with communication trees to speed up the signing process in 
case of large number of cosigners. In what follows, we only present the protocol 
with a plain communication architecture as it suffices for the confirm service activity 
solution introduced in this document.

Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and 
generator $g$, such that the discrete log is believed to be hard in this group. 
Take $n$ parties that want to sign a statement together. 
Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key 
$pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$. To sign a message $m$, 
one of these parties, let's say $P_1$, coordinates the signing process as follows: 
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item $P_1$ prepares a message $m$ and sends it to the rest of the signers.

\item Each party $P_i$, possibly after verifying 
$m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and compute $V_i = g^{\tau_i}$, 
then it sends $V_i$ back to $P_1$.

\item $P_1$ aggregates all random values received from 
the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.

\item $P_1$ then computes 
$c = H(V||m)$, where $H$ is an appropriate hash function. $P_1$ then 
sends $c$ to the rest of the parties.

\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and 
sends it to $P_1$.

\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the 
collective signature over $m$ as $(c, r)$.
\end{enumerate}

Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with 
one difference. An aggregated public key $pk$ is used in the verification process, 
which is computed as $pk = \Pi_{i=1}^{n} pk_i$.

The work in~\cite{syta2016keeping} tackles several issues related to 
the availability of the 
signing parties, and optimizing the communication between them. 
We believe that such techniques can be used in the NuCypher network if we adopt the 
CoSi-based solution for the confirm service activity issue.

### 2020-03-11 tex/solutions.tex
first writeup draft

\section{Potential Solutions}
\label{solutions}
This section outlines several potential solutions for how to let Ursula prove 
that she served a given number of distinct requests in a publicly verifiable way. 
One of these solutions, the PCD-based one, is still a work in progress. The goal 
is to share the high level idea of each of these solutions to chose the best one, 
after we define the meaning of best, to be adopted by the NuCypher network.

\subsection{PCD-based Scheme}
The main idea here is to adapt the PCD framework so Ursula 
can combine the correctness proofs she computes for Bobs' requests in a single proof 
attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
requests correctly."

Thus, in this setup, there is only one computation party, or prover, namely, Ursula. 
For each round, where a round could be the time needed to mine a block on the 
blockchain, Ursula starts with an input $x_1$, which is a signed and fresh request 
from Bob. It answers this request with $cFarg_{x_1}$ and produces a correctness 
proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
which is the input for the next step in the computation, Ursula answers 
this request as before and produces $cFarg_{x_2}$ and a correctness proof $\pi_2$, then 
it uses $(x_2, cFarg_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
$\hat{\pi}_2$ does not only 
attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
two valid distinct requests until now. The same process is repeated until the end of the 
round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
this process pictorially.

\begin{figure}[h!]
\centerline{
\includegraphics[height= 0.7in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
\caption{PCD-based solution diagram. Ursula starts a round in the idle state. When 
the first request arrives, Ursula responds to the request and starts composing the 
proofs as new requests arrive. At the end of the round, Ursula announces the number of 
served requests and a single proof attesting to its claim to the network. }
\label{pcd-based-sol}
\end{figure}

The final proof will be processed by the contract that governs Alice's policy. A valid proof 
allows Ursula to claim fees out of Alice's Ether escrow as a payment for $\omega$ re-encryption  
requests.

The above is a high level description of the idea. However, more time is need to 
understand PCD and SNARKs in order to come up with a concrete construction 
(if possible). Please see Section~\ref{future-work} for more information.

\subsection{CoSi-based Scheme}
This solution utilizes the idea of collective signing by electing a committee 
that will sign a report submitted by a specific Ursula after verifying that 
the report supports the claim that ``Ursula has served $\omega$ distinct 
re-encryption requests correctly."

At a high level, the scheme works as follows. For each round, a working Ursula keeps 
a full record of all the requests that she served during the round. These 
include the signed requests received from Bob(s), and the produced $cFrag$ 
and the correctness proof $\pi$ (as in the Umbral scheme) for 
each request. At the end of the round, a committee of $t$ Ursulas is 
elected, where $t$ is a small integer, e.g., $t = 5$. The working Ursula 
initiates the CoSi protocol to sign the message $m$ stated above while 
replacing $\omega$ with the actual number of served 
requests in the round. This Ursula sends $m$ along with the full report to 
each member in the committee. Each member Ursula (i.e., member in the 
elected committee) verifies $m$ by checking the report as follows:
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item Check that each request is distinct and valid by verifying Bob's 
signature over the request. (Here the policy will contain Bob's public 
key to allow the committee use the right verification key.)

\item Verify the correctness of each $cFarg$ as in the Umbral 
scheme.

\item Check that the value of $\omega$ inside $m$ agrees with the 
record.
\end{enumerate}

If everything is fine, each member of the committee and the working 
Ursula finalize the CoSi signing protocol as described in Section~\ref{cosi}. 
At the end, the working Ursula publishes the collective signature, which can be 
verified using the accumulated public keys of the cosigning Ursulas.

\subsubsection{On the committee election.} This can be done 
by using some deterministic computation over a block hash and mapping 
the output to Ursulas' public keys. So the selection is not in the hand of the 
working Ursula to prevent any potential collusion.

The above scheme works under the assumption that at least one Ursula 
in the elected committee is honest, which pertains to an assumption on the 
least number of honest Ursulas in the network.

Another approach is to have a changing set of external verifiers, like 
trusted partners, that all working Ursulas go to for the CoSi signing 
of their records.

A third approach, is to keep the deterministic selection of the committee 
but with an external member, e.g., either a trusted partner verifier 
or a special verifier node deployed and maintained by the NuCypher company. 
Thus, achieving the assumption of at least one member of the elected 
committee is honest.

\subsubsection{On the publicity of the signed records.} Having a 
valid collective signature from a committee (that has at least one honest 
member) suffices for the correctness of the signed statement. However, 
it could be better to keep the records that produced the message $m$  
available for a while so any party can verify them (like the verifying 
parties maintain such a public record for a given period after which 
the logs can be discarded).

We can resort to this option just at the beginning to convince the 
participants of the trustworthy of the committee or the validity of the 
assumption that at least one Ursula in the elected committee is honest.

\subsubsection{On compensating the committee.} This solution may 
raise the question of why would the elected committee (especially if it 
is composed of other Ursulas in the system) participate in the CoSi 
process, which also involves verifying the full request record presented 
by the working Ursula. This can be either pictured as a collaborative 
work, the committee does the work so others will do the same later 
when the committee members play the role of working Ursulas.

Another option, is to pay the committee for the work, either as 
part of the inflation rewards, or by having working Ursulas pay for 
that (however, this may complicate the system operation).

\subsection{Challenge/Open-based Scheme}
This solution utilizes the idea of commit/challenge/open protocols. 
In details, Ursula keeps track of the requests coming from Bob(s) 
during a time round and assign each of them a unique sequence 
number. That is, Ursula replies with $cFrag$ and the correctness proof 
along with a sequence number showing the order of the request within 
the batch of requests handled during a round. At the end of the round, 
Ursula constructs a Merkle tree of all requests, where 
the requests (and their replies) are the leaves of the tree ordered based on their sequence 
numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
to the network (recall that $\omega$ is the number of served requests).

To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
This can be done by having the policy contract select at random (like based 
on the block hash or any other mechanism) the leave IDs to be opened. If 
Ursula fails to open them correctly within a predefined timeframe, she loses the 
whole feed she was supposed to collect for serving $\omega$ requests.

An alternative approach to the challenge/open scheme described above is to 
have Ursula publish the full Merkle tree on, e.g., some known public space, but 
not on the blockchain. Make the full record available online for a specific period 
to allow anyone to verify the work. If no one file a complaint about the tree (we 
still need to define correctness properties, like checking all Bob public keys are 
defined in the policy created by Alice, and that the response is valid by checking the 
proof produced by Umbral), Ursula collects the fees of the service. On the other 
hand, a valid complaint or proof-of-cheating costs Ursula the full amount of fees.

### 2020-03-11 tex/threat-network-model.tex
first writeup draft

\section{Threat and Network Models}
\label{threat-network-model}
This section describes a modification for the network model of NuCypher 
KMS required by the proposed confirm service activity solutions, in 
addition to the threat model we adopt in this document.

\subsection{Network Model}
In order for the proposed solutions to work, we need to ensure freshness, 
integrity, and authenticity of the requests issued by Bob. This can be achieved 
by requiring Bob to sign each request it issues and to include a timestamp, or 
sequence number, in each request to ensure freshness.

The following approach can be used here; given that Umbral already requires Bob to 
have a key pair, this pair can be used for signing and verifying the signed requests. 
This also means that Ursula should be aware  the secret key can be used for the 
signing the requests and the public 
key should be known to Ursula to verify the signatures.

\subsection{Threat Model}
We do not place trust in any party and we assume that all participants are 
self-interested. This means that a party may 
follow the protocol or deviate from it, either on its own or by colluding 
with other attackers, is solely based on what maximizes the financial profits 
of this party. As such, Ursula may collude with Bob or Alice (by spinning 
its own Alice and/or Bob for example) to achieve her financial goals.

We also assume that when sampling a subset of Ursulas in the network, 
at least one of them is honest. This assumption can be achieved by 
having a global assumption regarding the lower bound of the number of 
honest Ursulas with respect to the total number of Ursulas in the system. 
(Or it can be achieved by deploying a special entity like an external verifier, 
that changes on periodic basis, or one by the NuCypher company, that is 
trusted to faithfully participate in the confirm 
service activity protocol. This verifier does not provide any other services 
in the system.)

Other than the above, we have usual assumptions like dealing with 
computationally bounded adversaries 
that cannot break secure cryptographic primitives with non-negligible probability. 
(We may need to work in the random oracle model, but this depends on the 
security requirements of proposed solutions.)

### 2020-03-11 tex/intro.tex
Small corrections and initial additional thoughts

@@
 
-Currently, the inflation rewards are computed for each Ursula based on the number of 
-active policies it holds conditioned on being online during the period of each of these 
-policies. Confirming the status of being online is done by having each Ursula call a 
+Currently, the inflation rewards are computed for each Ursula based on the size of their stake, and their confirmation that they are online, once per period.
+Confirming the status of being online is done by having each Ursula call a
 simple function in one of the NuCypher contracts to signal that she is around.
 
-Same for the fees, Ursula will collect some of the Ether locked by Alice at the end 
-of the policy duration given that this Ursula stays online for the whole duration. 
-Again, the latter is tracked by watching the confirm activity function calls Ursula 
-make during the policy period.
+As for fees, Ursula collects the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed their online status.
 
@@
 not require any input or proofs from Ursula on providing the service. Ursula 
-an stay offline offline, not answering any Bob, and be online just to call the confirm activity 
+can stay offline, not answering any Bob, and be online just to call the confirm activity 
 function. This allows Ursula to collect both inflation rewards 
-and fees without doing anything, and even worse, it will be able to get her stake back at 
-the end of a policy duration.
+and fees without doing anything, and even worse, it will be able to get her stake back once it unlocks (policies being managed by Ursula will have expired by this point). 
 \end{itemize}
@@
 rewards as well, this will encourage Ursula to collude with Bob to issue large 
-number of requests. Even it may encourage Ursula to deploy its own Alice(s) 
+number of requests.
+If inflation rewards were to be distributed based on the earning of fees (which is desirable, as it would link node subsidization more closely with the network service), this might encourage Ursula to deploy its own Alice(s)
 and Bob(s) to increase the demand, and thus, the cut of the inflation rewards.

### 2020-03-11 tex/solutions.tex
Small corrections and initial additional thoughts

@@
 blockchain, Ursula starts with an input $x_1$, which is a signed and fresh request 
-from Bob. It answers this request with $cFarg_{x_1}$ and produces a correctness 
+from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
 proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
@@
 which is the input for the next step in the computation, Ursula answers 
-this request as before and produces $cFarg_{x_2}$ and a correctness proof $\pi_2$, then 
-it uses $(x_2, cFarg_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
+this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then 
+it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
 $\hat{\pi}_2$ does not only 
@@
 
-\item Verify the correctness of each $cFarg$ as in the Umbral 
+\item Verify the correctness of each $cFrag$ as in the Umbral 
 scheme.
@@
 working Ursula to prevent any potential collusion.
+The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance they control the entire committee.
 
@@
 in the elected committee is honest, which pertains to an assumption on the 
-least number of honest Ursulas in the network.
+least number of honest Ursulas in the network. If the latter assumption is under threat, one mitigating approach is to increase $t$ (the committee size).
 
@@
 This can be done by having the policy contract select at random (like based 
-on the block hash or any other mechanism) the leave IDs to be opened. If 
+on the block hash or any other mechanism) the leaf IDs to be opened. If 
 Ursula fails to open them correctly within a predefined timeframe, she loses the 
@@
 proof produced by Umbral), Ursula collects the fees of the service. On the other 
-hand, a valid complaint or proof-of-cheating costs Ursula the full amount of fees.
+hand, a valid complaint or proof-of-cheating costs Ursula the full amount of fees, or potentially involves slashing her stake.

### 2020-03-11 tex/threat-network-model.tex
Fix minor typos. Added some initial comments.

@@
 This section describes a modification for the network model of NuCypher 
-KMS required by the proposed confirm service activity solutions, in 
+required by the proposed confirm service activity solutions, in 
 addition to the threat model we adopt in this document.
@@
 
+\david{NuCrypher currently supports this by allowing Bob to include a blockhash,
+although it's not being used for the moment.}
+
 The following approach can be used here; given that Umbral already requires Bob to 
 have a key pair, this pair can be used for signing and verifying the signed requests. 
-This also means that Ursula should be aware  the secret key can be used for the 
+This also means that Ursula should be aware the secret key can be used for 
 signing the requests and the public 
 key should be known to Ursula to verify the signatures.
+
+\david{Reusing the same keypair for encryption and signing may introduce some key management problems. Is it possible to find a solution that supports separate keypairs?}
 

### 2020-03-11 tex/intro.tex

@@
 \label{intro}
-NuCypher KMS~\cite{egorov2017nucypher} is a decentralized key management 
+The NuCypher network ~\cite{egorov2017nucypher} is a decentralized key management 
 system, encryption, and access control service. It uses proxy re-encryption, namely, the 
@@
 owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
-a ciphertext encrypted under Alice's public key into a ciphertext under the delegatee's, or Bob's,  
+a ciphertext encrypted under Alice's public key into a ciphertext decryptable by the delegatee's, or Bob's,  
 public key. This enables the latter to decrypt the data without revealing anything about the 
-encryption keys or the raw data to the intermediate servers.
+decryption keys or the raw data to the intermediate servers.
 
@@
 is basically the timeframe curing which Bob is authorized to access Alice's data.  Furthermore, 
-Alice will lock an amount of Ether into the policy to be used to pay Ursula for the re-encryption 
+Alice will lock an amount of Ether into the policy to be used to pay Ursulas for the re-encryption 
 service. As noted, Alice is not exposed to the NU token. All what she needs is an Ethereum 
@@
 
-\subsection{Monetary Incentives in the NuCypher KMS Network}
+\subsection{Monetary Incentives in the NuCypher Network}
 Ursulas are rewarded for the re-encryption service by using two sources; 
@@
 main problems: 
+\david{It's important to clarify here if we're talking about inflation rewards, service fees, or both.}
 \begin{itemize}
@@
 both collect the same rewards if they hold identical policies.
-
+\david{We should make a distinction between being idle because there are no requests or being off-line.
+The former is a legitimate situation driven by factors outside Ursula's control, while the latter is a punishable action.}
 \item Confirming being online is flawed in the sense that this function does 

### 2020-03-11 tex/solutions.tex

@@
 (if possible). Please see Section~\ref{future-work} for more information.
+
+\david{I think it is possible to aggregate current Umbral proofs. I started to explore this option in the past but there was no use for it at that moment.}
 
@@
 Ursula fails to open them correctly within a predefined timeframe, she loses the 
-whole feed she was supposed to collect for serving $\omega$ requests.
+whole fee she was supposed to collect for serving $\omega$ requests.
 

### 2020-03-11 tex/intro.tex

@@
 owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
-a ciphertext encrypted under Alice's public key into a ciphertext decryptable by the delegatee's, or Bob's,  
+ciphertext encrypted under Alice's public key into ciphertext encrypted under the delegatee's, or Bob's,
 public key. This enables the latter to decrypt the data without revealing anything about the
@@
 and the monetary incentives paid to provide the service. In order to join the 
-system, an Ursula needs to stake an amount of NU tokens for a specific period 
-and will be released when the pre-specified staking period is over. Alice chooses an  
+system, Ursula needs to stake an amount of NU tokens for a specific period
+which will be released when the pre-specified staking period is over. Alice chooses an
 Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
-pledged in the system. As such, the stake value influences the amount of service load Ursula 
+pledged in the system. As such, the stake value influences the amount of service load an Ursula
 may receive. This stake is also used to punish Ursula financially, by revoking part 
@@
 need to answer requests coming from Bob(s), as well as the duration of the policy, which 
-is basically the timeframe curing which Bob is authorized to access Alice's data.  Furthermore, 
+is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
 Alice will lock an amount of Ether into the policy to be used to pay Ursulas for the re-encryption 
-service. As noted, Alice is not exposed to the NU token. All what she needs is an Ethereum 
-wallet, being aware of the NuCypher network architecture to select Ursulas, and knowing the 
+service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
+wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
 NuCypher rules of preparing access control policies.
@@
 Bob, on the other hand, does not deal with currency in the system. It interacts with the storage 
-network to retrieve the encrypted data, and with Ursulas in the NuCypher network to ask for the  
+network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
 re-encryption service.
@@
 the first is the service fees collected from the policy or data 
-owner Alice, while the second is an inflation rewards, i.e., newly minted 
+owner Alice, while the second is inflation rewards, i.e., newly minted
 NU tokens, coming from the NuCypher network. The latter will be provided during the 
@@
 adoption. It is expected that these rewards will disappear as the token cap is 
-reached, much similar to other cryptocurrencies out there.
+reached, similar to other cryptocurrencies out there.
 
@@
 Confirming the status of being online is done by having each Ursula call a
-simple function in one of the NuCypher contracts to signal that she is around.
+simple function in one of the NuCypher contracts to signal that she is online.
 
@@
 \subsection{Problems with Current Reward Computation Approach}
-The current approach of computing Ursula's rewards suffers from two 
+The current approach of computing Ursula's inflation rewards and service fees suffers from two
 main problems:
-\david{It's important to clarify here if we're talking about inflation rewards, service fees, or both.}
 \begin{itemize}
@@
 requests Ursula serves. Thus an active Ursula who may serve a huge number of 
-requests, and an idle one who does not receive any requests (or a 
+requests, and one who does not receive any requests (or a
 malicious Ursula that does not answer the requests she receives from Bob), will 
 both collect the same rewards if they hold identical policies.
-\david{We should make a distinction between being idle because there are no requests or being off-line.
-The former is a legitimate situation driven by factors outside Ursula's control, while the latter is a punishable action.}
 \item Confirming being online is flawed in the sense that this function does 
 not require any input or proofs from Ursula on providing the service. Ursula 
-can stay offline, not answering any Bob, and be online just to call the confirm activity 
+can stay offline and not respond to Bobs' requests, and simply come online merely to call the confirm activity
 function. This allows Ursula to collect both inflation rewards 
@@
 Although we can use the number of served requests to compute the inflation 
-rewards as well, this will encourage Ursula to collude with Bob to issue large 
+rewards as well, this will encourage Ursula to collude with Bob to issue a large
 number of requests.
 If inflation rewards were to be distributed based on the earning of fees (which is desirable, as it would link node subsidization more closely with the network service), this might encourage Ursula to deploy its own Alice(s)
-and Bob(s) to increase the demand, and thus, the cut of the inflation rewards.
+and Bob(s) to increase the demand, and thus increase its cut of the inflation rewards.
 
@@
 requirements, in addition to their security guarantees. We present each of these 
-solution, where one of them is still a work in progress, discuss the aforementioned 
+solutions, where one of them is still a work in progress, discuss the aforementioned
 trade-offs and requirements of each of them, with the goal of selecting one of these 

### 2020-03-11 tex/prelim.tex

@@
 them with communication trees to speed up the signing process in 
-case of large number of cosigners. In what follows, we only present the protocol 
+case of a large number of cosigners. In what follows, we only present the protocol
 with a plain communication architecture as it suffices for the confirm service activity 

### 2020-03-11 tex/solutions.tex

@@
 One of these solutions, the PCD-based one, is still a work in progress. The goal 
-is to share the high level idea of each of these solutions to chose the best one, 
+is to share the high-level idea of each of these solutions and to chose the best one,
 after we define the meaning of best, to be adopted by the NuCypher network.
@@
 \subsection{PCD-based Scheme}
-The main idea here is to adapt the PCD framework so Ursula 
+The main idea here is to adapt the PCD framework so that Ursula
 can combine the correctness proofs she computes for Bobs' requests in a single proof 
@@
 For each round, where a round could be the time needed to mine a block on the 
-blockchain, Ursula starts with an input $x_1$, which is a signed and fresh request 
+blockchain, Ursula starts with input $x_1$, which is a signed and fresh request
 from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
@@
 
+\derek{Signature only validates request, but for distinct requests, presumably blockhash/sequence number needs to also be checked?}
+
 \item Verify the correctness of each $cFrag$ as in the Umbral 
@@
 by using some deterministic computation over a block hash and mapping
-the output to Ursulas' public keys. So the selection is not in the hand of the 
+the output to Ursulas' public keys. So the selection is not determined by the
 working Ursula to prevent any potential collusion.
-The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance they control the entire committee.
+The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.
 
@@
 Another approach is to have a changing set of external verifiers, like
-trusted partners, that all working Ursulas go to for the CoSi signing 
+trusted partners, that all working Ursulas must use for the CoSi signing
 of their records.
 
-A third approach, is to keep the deterministic selection of the committee 
+A third approach is to keep the deterministic selection of the committee
 but with an external member, e.g., either a trusted partner verifier
@@
 it could be better to keep the records that produced the message $m$  
-available for a while so any party can verify them (like the verifying 
-parties maintain such a public record for a given period after which 
+available for a while so that any party can verify them (the verifying
+parties could maintain such a public record for a given period after which
 the logs can be discarded).
@@
 We can resort to this option just at the beginning to convince the 
-participants of the trustworthy of the committee or the validity of the 
+participants of the trustworthiness of the committee or the validity of the
 assumption that at least one Ursula in the elected committee is honest.
@@
 process, which also involves verifying the full request record presented 
-by the working Ursula. This can be either pictured as a collaborative 
-work, the committee does the work so others will do the same later 
+by the working Ursula. This can be pictured as a collaborative
+work, the committee does the work so that others will do the same
 when the committee members play the role of working Ursulas.
 
-Another option, is to pay the committee for the work, either as 
+Another option is to pay the committee for their work, either as
 part of the inflation rewards, or by having working Ursulas pay for 
-that (however, this may complicate the system operation).
+it (however, this may complicate the system operation).
 
@@
 Ursula constructs a Merkle tree of all requests, where 
-the requests (and their replies) are the leaves of the tree ordered based on their sequence 
+the requests (and their replies) are the leaves of the tree ordered by the sequence
 numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
@@
 To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
-This can be done by having the policy contract select at random (like based 
+This can be done by having the policy contract select at random (e.g. based
 on the block hash or any other mechanism) the leaf IDs to be opened. If 
@@
 An alternative approach to the challenge/open scheme described above is to 
-have Ursula publish the full Merkle tree on, e.g., some known public space, but 
-not on the blockchain. Make the full record available online for a specific period 
-to allow anyone to verify the work. If no one file a complaint about the tree (we 
+have Ursula publish the full Merkle tree on some known public space but
+not on the blockchain, and make the full record available online for a specific period
+to allow anyone to verify the work. If no one files a complaint about the tree (we
 still need to define correctness properties, like checking all Bob public keys are 
 defined in the policy created by Alice, and that the response is valid by checking the 
-proof produced by Umbral), Ursula collects the fees of the service. On the other 
-hand, a valid complaint or proof-of-cheating costs Ursula the full amount of fees, or potentially involves slashing her stake.
+proof produced by Umbral), Ursula collects the fees for the provided service. On the other
+hand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.

### 2020-03-11 tex/threat-network-model.tex

@@
 have a key pair, this pair can be used for signing and verifying the signed requests. 
-This also means that Ursula should be aware the secret key can be used for 
+This also means that Ursula should be aware that the secret key can be used for
 signing the requests and the public 
@@
 follow the protocol or deviate from it, either on its own or by colluding 
-with other attackers, is solely based on what maximizes the financial profits 
+with other attackers, and decisions are solely based on what maximizes the financial profits
 of this party. As such, Ursula may collude with Bob or Alice (by spinning 
@@
 (Or it can be achieved by deploying a special entity like an external verifier, 
-that changes on periodic basis, or one by the NuCypher company, that is 
+that changes on a periodic basis, or one by the NuCypher company, that is
 trusted to faithfully participate in the confirm 

### 2020-03-23 tex/confirm-service-activity.tex
reorganize the document

\section{Confirm Service Activity}

\input{tex/confirm-service-activity/threat-network-model}
\input{tex/confirm-service-activity/prelim}
\input{tex/confirm-service-activity/solutions}
\input{tex/confirm-service-activity/analysis}
\input{tex/confirm-service-activity/future-work}

### 2020-03-23 tex/confirm-service-activity/prelim.tex
reorganize the document

--- 2020-03-11 tex/prelim.tex
@@
-\section{Preliminaries}
+\subsection{Preliminaries}
 \label{prelim}
@@
 
-\subsection{Proof Carrying Data (PCD)}
+\subsubsection{Proof Carrying Data (PCD)}
 The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
@@
 
-\subsection{Collective Signing (CoSi)}
+\subsubsection{Collective Signing (CoSi)}
 \label{cosi}

### 2020-03-23 tex/confirm-service-activity/solutions.tex
reorganize the document

--- 2020-03-11 tex/solutions.tex
@@
-\section{Potential Solutions}
+\subsection{Potential Solutions}
 \label{solutions}
@@
 
-\subsection{PCD-based Scheme}
+\subsubsection{PCD-based Scheme}
 The main idea here is to adapt the PCD framework so that Ursula
@@
 
-\subsection{CoSi-based Scheme}
+\subsubsection{CoSi-based Scheme}
 This solution utilizes the idea of collective signing by electing a committee 
@@
 
-\subsubsection{On the committee election.} This can be done
+\paragraph{On the committee election.} This can be done
 by using some deterministic computation over a block hash and mapping
@@
 
-\subsubsection{On the publicity of the signed records.} Having a 
+\paragraph{On the publicity of the signed records.} Having a 
 valid collective signature from a committee (that has at least one honest 
@@
 
-\subsubsection{On compensating the committee.} This solution may 
+\paragraph{On compensating the committee.} This solution may 
 raise the question of why would the elected committee (especially if it 
@@
 
-\subsection{Challenge/Open-based Scheme}
+\subsubsection{Challenge/Open-based Scheme}
 This solution utilizes the idea of commit/challenge/open protocols. 

### 2020-03-23 tex/confirm-service-activity/threat-network-model.tex
reorganize the document

--- 2020-03-11 tex/threat-network-model.tex
@@
-\section{Threat and Network Models}
+\subsection{Threat and Network Models}
 \label{threat-network-model}
@@
 
-\subsection{Network Model}
+\subsubsection{Network Model}
 In order for the proposed solutions to work, we need to ensure freshness, 
@@
 
-\subsection{Threat Model}
+\subsubsection{Threat Model}
 We do not place trust in any party and we assume that all participants are 

### 2020-03-25 tex/abstract.tex
edit abstract

@@
 This document introduces several aspects related to the confirm activity problem in 
-the NuCypher KMS network. These include the current adopted solution, its relation 
-with both the fees and the inflation rewards, and three potential solutions that can be 
-used to provide a proof that an Ursula has served a specific number of re-encryption 
-requests within a given a period. We argue that the latter is a better option to be used 
-for computing the fees that Alice paid for an Ursula in the network, but not for 
-computing the inflation rewards.
+the NuCypher network. These include the different definitions of this problem, the 
+underlying threat model, the current adopted solution, and its relation 
+to both the fees and the inflation rewards. Then we present potential solutions 
+for the two types of the confirm activity issue, namely, confirm availability 
+and confirm service activity. The former confirms that Ursula is available all the time 
+and replies to all requests coming from Bob, while the latter provides a proof that an 
+Ursula has served a specific number of distinct re-encryption 
+requests within a given a period. We discuss the different solutions and outline at 
+what stage of the network operation they are likely to be used.
 \end{abstract}

### 2020-03-25 tex/intro.tex
edit intro

@@
 \label{intro}
-The NuCypher network ~\cite{egorov2017nucypher} is a decentralized key management 
+The NuCypher network~\cite{egorov2017nucypher} is a decentralized key management 
 system, encryption, and access control service. It uses proxy re-encryption, namely, the 
@@
 owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
-ciphertext encrypted under Alice's public key into ciphertext encrypted under the delegatee's, or Bob's,
+ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
 public key. This enables the latter to decrypt the data without revealing anything about the
@@
 Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
-pledged in the system. As such, the stake value influences the amount of service load an Ursula
+pledged in the system. Therefore, the stake value influences the amount of service load an Ursula
 may receive. This stake is also used to punish Ursula financially, by revoking part 
-of it, when cheating is detected.
+of it, if it cheats and this cheating is detected.
 
@@
 Ursulas are rewarded for the re-encryption service by using two sources; 
-the first is the service fees collected from the policy or data 
+the first is the service fees collected from the policy  
 owner Alice, while the second is inflation rewards, i.e., newly minted
@@
 
-As for fees, Ursula collects the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed their online status.
+As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed its online status.
 
@@
 \setlength{\itemsep}{0pt}
-\item The rewards computation is agnostic to the number of 
+\item The rewards computation (both fees and inflation rewards) is agnostic to the number of 
 requests Ursula serves. Thus an active Ursula who may serve a huge number of 
 requests, and one who does not receive any requests (or a
-malicious Ursula that does not answer the requests she receives from Bob), will 
-both collect the same rewards if they hold identical policies.
+malicious/lazy Ursula that does not answer the requests she receives from Bob), will 
+both collect the same amount of rewards if they hold identical policies.
+
 \item Confirming being online is flawed in the sense that this function does 
@@
 function. This allows Ursula to collect both inflation rewards 
-and fees without doing anything, and even worse, it will be able to get her stake back once it unlocks (policies being managed by Ursula will have expired by this point). 
+and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks (i.e., when policies being managed by Ursula expire). 
 \end{itemize}
 
-\subsection{Proposed Solutions}
-We need a provably secure mechanism to be used by Ursula to report the 
-number of distinct Bob requests it handled during a specific period, and use this number 
-to compute the fees to be collected from Alice. Thus, we call this confirm 
-service activity, as opposed to confirm activity that refers to solely being available 
-online.
+\subsection{Overview}
+The confirm activity problem is defined differently based on the stage of the 
+NuCypher network. In early network operation, when inflation rewards are 
+still distributed, we are concerned with the availability of Ursulas and being willing to 
+serve all requests coming from Bob. In other words, regardless of the number of 
+requests served, the rewards value will be computed based on the period during which Ursula 
+is online and well-behaving. While in later stages, when inflation rewards disappear 
+and only fees exist, confirm activity will be tied to providing the re-encryption 
+service in the sense that the payment will be computed based on the amount of 
+service provided. Thus, Ursula needs to confirm its activity by proving that she served 
+a given number of distinct re-encryption requests during a give period. To make the distinction 
+clear, we refer to the first as confirm availability, and for the second as confirm 
+service activity.
 
-Although we can use the number of served requests to compute the inflation 
-rewards as well, this will encourage Ursula to collude with Bob to issue a large
-number of requests.
-If inflation rewards were to be distributed based on the earning of fees (which is desirable, as it would link node subsidization more closely with the network service), this might encourage Ursula to deploy its own Alice(s)
-and Bob(s) to increase the demand, and thus increase its cut of the inflation rewards.
+In terms of the underlying threat model, for both problem definitions we do not consider collusion 
+between Bob and Ursula as a practical threat. This means that cases of Bob pretending  
+that he got service from Ursula (while no service is delivered) is not an issue (we do not 
+suspect this will be of any importance and there is no motivation to do it given that 
+the work Ursula does for re-encryption is minimal).
 
-In this document, we introduce several solutions for confirming service activity. 
+In this document, we introduce several solutions for both forms of confirming activity. 
 These solutions differ in the trust, efficiency, interactivity, and resource 
-requirements, in addition to their security guarantees. We present each of these 
-solutions, where one of them is still a work in progress, discuss the aforementioned
+requirements, in addition to their security guarantees. We divide the document into 
+two parts, the first is about confirm availability, while the second is about confirm 
+service activity. We present each of our solutions, discuss the aforementioned
 trade-offs and requirements of each of them, with the goal of selecting one of these 
-solutions to be adopted in the NuCypher network.
-
-\subsection{Roadmap}
-The rest of this document is organized as follows. Section~\ref{threat-network-model} 
-outlines the network and threat models adopted by the proposed solutions. 
-Section~\ref{prelim} provides an overview of the underlying cryptographic primitives and 
-protocols, while the proposed solutions are presented 
-in Section~\ref{solutions} with their security and efficiency aspects analyzed in 
-Section~\ref{analysis}. Lastly, directions of future work on the confirm activity issue 
-are outlined in Section~\ref{future-work}.
+solutions to be adopted in each operational stage of the NuCypher network.

### 2020-03-25 tex/confirm-service-activity.tex
edit confirm service activity section

@@
 \section{Confirm Service Activity}
+In this section, we present potential solutions for the confirm service activity 
+problem. The goal is to come up with provably secure solutions that allows an 
+Ursula to prove that it has served a given number of distinct re-encryption 
+requests within a given period.
+
+The rest of this section outlines the network and threat models adopted by 
+the proposed solutions, provides an overview of the underlying cryptographic primitives and 
+protocols, after which it discusses the proposed solutions along with an analysis of 
+their security and efficiency aspects. Lastly, the section concludes with directions of 
+future work on the confirm service activity issue.
 

### 2020-03-25 tex/confirm-service-activity/solutions.tex
edit confirm service activity section

@@
 
-\david{I think it is possible to aggregate current Umbral proofs. I started to explore this option in the past but there was no use for it at that moment.}
-
 \subsubsection{CoSi-based Scheme}
@@
 \setlength{\itemsep}{0pt}
-\item Check that each request is distinct and valid by verifying Bob's 
+\item Check that each request is distinct by checking the sequence 
+number of the request (or any value that is used for freshaness), and valid by verifying Bob's 
 signature over the request. (Here the policy will contain Bob's public 
 key to allow the committee use the right verification key.)
-
-\derek{Signature only validates request, but for distinct requests, presumably blockhash/sequence number needs to also be checked?}
 

### 2020-03-25 tex/confirm-service-activity/threat-network-model.tex
edit confirm service activity section

@@
 by requiring Bob to sign each request it issues and to include a timestamp, or 
-sequence number, in each request to ensure freshness.
+sequence number, in each request to ensure freshness. The keypair used for the 
+signature should be separate from the keypair Bob uses for proxy encryption in the 
+system.
 
-\david{NuCrypher currently supports this by allowing Bob to include a blockhash,
-although it's not being used for the moment.}
-
-The following approach can be used here; given that Umbral already requires Bob to 
-have a key pair, this pair can be used for signing and verifying the signed requests. 
-This also means that Ursula should be aware that the secret key can be used for
-signing the requests and the public 
-key should be known to Ursula to verify the signatures.
-
-\david{Reusing the same keypair for encryption and signing may introduce some key management problems. Is it possible to find a solution that supports separate keypairs?}
+Until now we assume that Alice pays for the service by using the Ether she locks 
+in the policy contract. Other arrangement may emerge in the system like having 
+Bob pay for each requests he issues. Such arrangement and its implication on the 
+confirm service activity issue will be studied once it becomes part of the NuCypher 
+network protocol.
 
@@
 with other attackers, and decisions are solely based on what maximizes the financial profits
-of this party. As such, Ursula may collude with Bob or Alice (by spinning 
+of this party. Thus, Ursula may collude with Bob or Alice (by spinning 
 its own Alice and/or Bob for example) to achieve her financial goals. 
+The latter is assumed in the current proposed solutions (PCD, CoSi, and 
+challenge/open based schemes). This means that solutions provide higher 
+security guarantees. It could be the case that relaxing the requirement of 
+accounting for Bob/Ursula collusion allows deploying more efficient solutions. 
+In order to make an educated decision of the plausibility of this threat, we need 
+more data about the system operation and the behavior of the participants 
+once the inflation rewards disappears in the system. As such, we leave this 
+issue until later when fees become the only source of rewards for Ursulas.
 

### 2020-04-28 tex/confirm-service-activity.tex
edit intro part

--- 2020-03-23 tex/confirm-service-activity.tex
@@
 \section{Confirm Service Activity}
+\label{confirm-service-actiivty}
+In this section, we present potential solutions for the confirm service activity 
+problem. The goal is to come up with provably secure solutions that allows an 
+Ursula to prove that it has served a given number of distinct re-encryption 
+requests within a given period.
 
-\input{tex/confirm-service-activity/threat-network-model}
+The rest of this section provides an overview of the underlying cryptographic primitives and 
+protocols, after which it discusses the proposed solutions along with an analysis of 
+their security and efficiency aspects. Lastly, the section concludes with directions of 
+future work on the confirm service activity issue.
+
 \input{tex/confirm-service-activity/prelim}

### 2020-04-28 tex/confirm-service-activity/prelim.tex
edit intro part

@@
 
-\subsubsection{Proof Carrying Data (PCD)}
+\subsubsection{Proof Carrying Data (PCD).}
 The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
@@
 
-\subsubsection{Collective Signing (CoSi)}
+\subsubsection{Collective Signing (CoSi).}
 \label{cosi}

### 2020-04-28 tex/confirm-service-activity/solutions.tex
edit intro part

@@
 
-\subsubsection{PCD-based Scheme}
+\subsubsection{PCD-based Scheme.}
 The main idea here is to adapt the PCD framework so that Ursula
@@
 
-\subsubsection{CoSi-based Scheme}
+\subsubsection{CoSi-based Scheme.}
 This solution utilizes the idea of collective signing by electing a committee 
@@
 
-\subsubsection{Challenge/Open-based Scheme}
+\subsubsection{Commit/Challenge/Open-based Scheme.}
 This solution utilizes the idea of commit/challenge/open protocols. 

### 2020-04-28 tex/intro.tex
edit intro part

@@
 ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
-public key. This enables the latter to decrypt the data without revealing anything about the
+public key. This enables the latter to decrypt the ciphertext without revealing anything about the
 decryption keys or the raw data to the intermediate servers.
@@
 may receive. This stake is also used to punish Ursula financially, by revoking part 
-of it, if it cheats and this cheating is detected.
+of it, if she cheats and this cheating is detected.
 
@@
 adoption. It is expected that these rewards will disappear as the token cap is 
-reached, similar to other cryptocurrencies out there.
+reached, similar to other cryptocurrencies i the space.
 
-Currently, the inflation rewards are computed for each Ursula based on the size of their stake, and their confirmation that they are online, once per period.
+Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake, and the confirmation that she is online.
 Confirming the status of being online is done by having each Ursula call a
@@
 
-As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed its online status.
+As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
 
@@
 \item The rewards computation (both fees and inflation rewards) is agnostic to the number of 
-requests Ursula serves. Thus an active Ursula who may serve a huge number of 
+requests Ursula serves. Thus, an active Ursula who may serve a huge number of 
 requests, and one who does not receive any requests (or a
@@
 
-\subsection{Overview}
+\subsection{Problem Statement}
 The confirm activity problem is defined differently based on the stage of the 
@@
 service provided. Thus, Ursula needs to confirm its activity by proving that she served 
-a given number of distinct re-encryption requests during a give period. To make the distinction 
+a given number of distinct re-encryption requests during a given period. To make the distinction 
 clear, we refer to the first as confirm availability, and for the second as confirm 
 service activity.
-
-In terms of the underlying threat model, for both problem definitions we do not consider collusion 
-between Bob and Ursula as a practical threat. This means that cases of Bob pretending  
-that he got service from Ursula (while no service is delivered) is not an issue (we do not 
-suspect this will be of any importance and there is no motivation to do it given that 
-the work Ursula does for re-encryption is minimal).
 
@@
 two parts, the first is about confirm availability, while the second is about confirm 
-service activity. We present each of our solutions, discuss the aforementioned
+service activity. We begin with outlining the adopted threat model for each problem 
+definition, as well as the network model Then we present our solutions for each 
+of these problems, discuss the aforementioned
 trade-offs and requirements of each of them, with the goal of selecting one of these 
-solutions to be adopted in each operational stage of the NuCypher network.
+solutions to be adopted in each stage of the NuCypher network operation.
+
+\subsection{Threat and Network Models}
+\label{threat-network-model}
+This section describes a modification for the network model of NuCypher 
+required by the proposed solutions, in 
+addition to the threat model adopted in this work.
+
+\subsubsection{Network Model.}
+In order for the proposed solutions to work, we need to ensure freshness, 
+integrity, and authenticity of the requests (or service compliants) issued by Bob. This can be achieved 
+by requiring Bob to sign each request it issues and to include a timestamp, or 
+sequence number, in each request to ensure freshness. The keypair used for the 
+signature should be separate from the keypair Bob uses for proxy encryption in the 
+system.
+
+Until now we assume that Alice pays for the service by using the Ether she locks 
+in the policy contract. Other arrangement may emerge in the system like having 
+Bob pay for each requests he issues. Such an arrangement and its implication on the 
+confirm service activity issue will be studied once it becomes part of the NuCypher 
+network protocol.
+
+\subsubsection{Threat Model.}
+We do not place trust in any party and we assume that all participants are 
+self-interested. This means that a party may decide to 
+follow the protocol or deviate from it, either on its own or by colluding 
+with other attackers, and such decision is solely based on what maximizes the financial profits
+of this party. Thus, if it is profitable, an Ursula may, for example, spin out  
+its own Alice and/or Bob or collude with Alice. We do not consider collusion 
+between Bob and Ursula as a practical threat. This means that cases of Bob pretending  
+that he got service from Ursula (while no service is delivered) is not an issue. We do not 
+suspect this will be of any importance and there is no motivation to do it given that 
+the work Ursula does for re-encryption is minimal.
+
+The above non-collusion assumption does not affect the solutions proposed to handle 
+the confirm service activity discussed in Section~\ref{confirm-service-actiivty}. This 
+means that these solutions provide higher 
+security guarantees and address the issue f potential collusion between Bob and Ursula. 
+It could be the case that relaxing the requirement of 
+addressing this collusion case allows deploying more efficient solutions. 
+In order to make an educated decision of the plausibility of this threat, we need 
+more data about the system operation and the behavior of the participants 
+once the inflation rewards disappears in the system. As such, we leave this 
+issue until later when fees become the only source of rewards for Ursulas.
+
+We also assume that when sampling a subset of Ursulas in the network, 
+at least one of them is honest. This assumption can be achieved by 
+having a global assumption regarding the lower bound of the number of 
+honest Ursulas with respect to the total number of Ursulas in the system. 
+(Or it can be achieved by deploying a special entity like an external verifier, 
+that changes on a periodic basis, or one by the NuCypher company, that is
+trusted to faithfully participate as a member of each samples set. This 
+verifier does not provide any other services 
+in the system.)
+
+Other than the above, we have usual assumptions like dealing with 
+computationally bounded adversaries 
+that cannot break secure cryptographic primitives with non-negligible probability. 
+(We may need to work in the random oracle model, but this depends on the 
+security requirements of the proposed solutions.)

### 2020-04-28 tex/confirm-service-activity.tex
reorganize the files

@@
 
-\input{tex/confirm-service-activity/prelim}
-\input{tex/confirm-service-activity/solutions}
-\input{tex/confirm-service-activity/analysis}
-\input{tex/confirm-service-activity/future-work}
+\subsection{Preliminaries}
+\label{prelim}
+This section provides an overview of two concepts that we use in the 
+proposed solutions. These include the framework of proof carrying data (PCD) 
+and the collective signing (CoSi) protocol.
+
+\subsubsection{Proof Carrying Data (PCD).}
+The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
+computation involving untrusted parties. It produces a single proof for the output 
+that attests not only the correctness of the final result, but also 
+the correctness of the entire history of intermediate computations that produced 
+this result. Correctness here is defined as a polynomially computable predicate that 
+abstracts the properties, or invariants, that must be satisfied.
+
+\begin{figure}[h!]
+\centerline{
+\includegraphics[height= 1.3in, width = 1.0\columnwidth]{figures/pcd-diagram.pdf}}
+\caption{An example of a PCD application. A distributed computation involving parties $P_i$, for 
+$i \in \{1, \dots, 6\}$, each 
+of which has a local input $x_i$ and produces an output $y_i$ with a proof $\pi_i$. }
+\label{pcd-diagram}
+\end{figure}
+
+To clarify how PDC works, consider a distributed computation task that involves 
+the set of parties shown in Figure~\ref{pcd-diagram}. Party $P_1$ starts the computation with its 
+own input, produces an intermediate output with a proof saying that it performed 
+the computation as defined by the protocol. It then sends both the output and the proof 
+to the next party, which is $P_2$ in this case. Here, $P_2$ will 
+have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) 
+as input to the computation it will perform. Similarly, $P_2$ will produce another 
+intermediate output and a proof. This proof not only attests to the correctness of the 
+computation done by $P_2$, but also the history that lead to the result $y_2$. In other 
+words, it implicitly includes 
+the proof from $P_1$. The same process continues until the full computation is finished. 
+Anyone can verify the correctness or compliance of the whole distributed protocol by 
+only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.
+
+As shown, PCDs enable untrusted parties to work with each other in a fully distributed 
+fashion, without overwhelming the system with the storage and verification of individual 
+proofs for each step of the performed protocol. Also, they attest to correctness or compliance  
+to the prescribed protocol without re-executing any of the intermediate computations. Thus, 
+they provide a promising paradigm for confirming service activity in a compact way.
+
+\subsubsection{Collective Signing (CoSi).}
+\label{cosi}
+CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
+statement together in a way that produces a single signature. As such, both the 
+verification time and the space requirements are just like having a single signer. The 
+difference is that this signature attests that all parties agree with the signed 
+statement instead of only one.
+
+CoSi builds upon Schnorr 
+multisignatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines 
+them with communication trees to speed up the signing process in 
+case of a large number of cosigners. In what follows, we only present the protocol
+with a plain communication architecture as it suffices for the confirm service activity 
+solution introduced in this document.
+
+Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and 
+generator $g$, such that the discrete log is believed to be hard in this group. 
+Take $n$ parties that want to sign a statement together. 
+Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key 
+$pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$. To sign a message $m$, 
+one of these parties, let's say $P_1$, coordinates the signing process as follows: 
+\begin{enumerate}
+\setlength{\itemsep}{0pt}
+\item $P_1$ prepares a message $m$ and sends it to the rest of the signers.
+
+\item Each party $P_i$, possibly after verifying 
+$m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and compute $V_i = g^{\tau_i}$, 
+then it sends $V_i$ back to $P_1$.
+
+\item $P_1$ aggregates all random values received from 
+the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.
+
+\item $P_1$ then computes 
+$c = H(V||m)$, where $H$ is an appropriate hash function. $P_1$ then 
+sends $c$ to the rest of the parties.
+
+\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and 
+sends it to $P_1$.
+
+\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the 
+collective signature over $m$ as $(c, r)$.
+\end{enumerate}
+
+Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with 
+one difference. An aggregated public key $pk$ is used in the verification process, 
+which is computed as $pk = \Pi_{i=1}^{n} pk_i$.
+
+The work in~\cite{syta2016keeping} tackles several issues related to 
+the availability of the 
+signing parties, and optimizing the communication between them. 
+We believe that such techniques can be used in the NuCypher network if we adopt the 
+CoSi-based solution for the confirm service activity issue.
+
+\subsection{Potential Solutions}
+\label{solutions}
+This section outlines several potential solutions for how to let Ursula prove 
+that she served a given number of distinct requests in a publicly verifiable way. 
+One of these solutions, the PCD-based one, is still a work in progress. The goal 
+is to share the high-level idea of each of these solutions and to chose the best one,
+after we define the meaning of best, to be adopted by the NuCypher network.
+
+\subsubsection{PCD-based Scheme.}
+The main idea here is to adapt the PCD framework so that Ursula
+can combine the correctness proofs she computes for Bobs' requests in a single proof 
+attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
+requests correctly."
+
+Thus, in this setup, there is only one computation party, or prover, namely, Ursula. 
+For each round, where a round could be the time needed to mine a block on the 
+blockchain, Ursula starts with input $x_1$, which is a signed and fresh request
+from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
+proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
+proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
+which is the input for the next step in the computation, Ursula answers 
+this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then 
+it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
+$\hat{\pi}_2$ does not only 
+attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
+two valid distinct requests until now. The same process is repeated until the end of the 
+round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
+served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
+this process pictorially.
+
+\begin{figure}[h!]
+\centerline{
+\includegraphics[height= 0.7in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
+\caption{PCD-based solution diagram. Ursula starts a round in the idle state. When 
+the first request arrives, Ursula responds to the request and starts composing the 
+proofs as new requests arrive. At the end of the round, Ursula announces the number of 
+served requests and a single proof attesting to its claim to the network. }
+\label{pcd-based-sol}
+\end{figure}
+
+The final proof will be processed by the contract that governs Alice's policy. A valid proof 
+allows Ursula to claim fees out of Alice's Ether escrow as a payment for $\omega$ re-encryption  
+requests.
+
+The above is a high level description of the idea. However, more time is need to 
+understand PCD and SNARKs in order to come up with a concrete construction 
+(if possible). Please see Section~\ref{future-work} for more information.
+
+\subsubsection{CoSi-based Scheme.}
+This solution utilizes the idea of collective signing by electing a committee 
+that will sign a report submitted by a specific Ursula after verifying that 
+the report supports the claim that ``Ursula has served $\omega$ distinct 
+re-encryption requests correctly."
+
+At a high level, the scheme works as follows. For each round, a working Ursula keeps 
+a full record of all the requests that she served during the round. These 
+include the signed requests received from Bob(s), and the produced $cFrag$ 
+and the correctness proof $\pi$ (as in the Umbral scheme) for 
+each request. At the end of the round, a committee of $t$ Ursulas is 
+elected, where $t$ is a small integer, e.g., $t = 5$. The working Ursula 
+initiates the CoSi protocol to sign the message $m$ stated above while 
+replacing $\omega$ with the actual number of served 
+requests in the round. This Ursula sends $m$ along with the full report to 
+each member in the committee. Each member Ursula (i.e., member in the 
+elected committee) verifies $m$ by checking the report as follows:
+\begin{enumerate}
+\setlength{\itemsep}{0pt}
+\item Check that each request is distinct by checking the sequence 
+number of the request (or any value that is used for freshaness), and valid by verifying Bob's 
+signature over the request. (Here the policy will contain Bob's public 
+key to allow the committee use the right verification key.)
+
+\item Verify the correctness of each $cFrag$ as in the Umbral 
+scheme.
+
+\item Check that the value of $\omega$ inside $m$ agrees with the 
+record.
+\end{enumerate}
+
+If everything is fine, each member of the committee and the working 
+Ursula finalize the CoSi signing protocol as described in Section~\ref{cosi}. 
+At the end, the working Ursula publishes the collective signature, which can be 
+verified using the accumulated public keys of the cosigning Ursulas.
+
+\paragraph{On the committee election.} This can be done
+by using some deterministic computation over a block hash and mapping
+the output to Ursulas' public keys. So the selection is not determined by the
+working Ursula to prevent any potential collusion.
+The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.
+
+The above scheme works under the assumption that at least one Ursula
+in the elected committee is honest, which pertains to an assumption on the
+least number of honest Ursulas in the network. If the latter assumption is under threat, one mitigating approach is to increase $t$ (the committee size).
+
+Another approach is to have a changing set of external verifiers, like
+trusted partners, that all working Ursulas must use for the CoSi signing
+of their records.
+
+A third approach is to keep the deterministic selection of the committee
+but with an external member, e.g., either a trusted partner verifier
+or a special verifier node deployed and maintained by the NuCypher company.
+Thus, achieving the assumption of at least one member of the elected
+committee is honest.
+
+\paragraph{On the publicity of the signed records.} Having a 
+valid collective signature from a committee (that has at least one honest 
+member) suffices for the correctness of the signed statement. However, 
+it could be better to keep the records that produced the message $m$  
+available for a while so that any party can verify them (the verifying
+parties could maintain such a public record for a given period after which
+the logs can be discarded).
+
+We can resort to this option just at the beginning to convince the 
+participants of the trustworthiness of the committee or the validity of the
+assumption that at least one Ursula in the elected committee is honest.
+
+\paragraph{On compensating the committee.} This solution may 
+raise the question of why would the elected committee (especially if it 
+is composed of other Ursulas in the system) participate in the CoSi 
+process, which also involves verifying the full request record presented 
+by the working Ursula. This can be pictured as a collaborative
+work, the committee does the work so that others will do the same
+when the committee members play the role of working Ursulas.
+
+Another option is to pay the committee for their work, either as
+part of the inflation rewards, or by having working Ursulas pay for 
+it (however, this may complicate the system operation).
+
+\subsubsection{Commit/Challenge/Open-based Scheme.}
+This solution utilizes the idea of commit/challenge/open protocols. 
+In details, Ursula keeps track of the requests coming from Bob(s) 
+during a time round and assign each of them a unique sequence 
+number. That is, Ursula replies with $cFrag$ and the correctness proof 
+along with a sequence number showing the order of the request within 
+the batch of requests handled during a round. At the end of the round, 
+Ursula constructs a Merkle tree of all requests, where 
+the requests (and their replies) are the leaves of the tree ordered by the sequence
+numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
+a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
+to the network (recall that $\omega$ is the number of served requests).
+
+To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
+This can be done by having the policy contract select at random (e.g. based
+on the block hash or any other mechanism) the leaf IDs to be opened. If 
+Ursula fails to open them correctly within a predefined timeframe, she loses the 
+whole fee she was supposed to collect for serving $\omega$ requests.
+
+An alternative approach to the challenge/open scheme described above is to 
+have Ursula publish the full Merkle tree on some known public space but
+not on the blockchain, and make the full record available online for a specific period
+to allow anyone to verify the work. If no one files a complaint about the tree (we
+still need to define correctness properties, like checking all Bob public keys are 
+defined in the policy created by Alice, and that the response is valid by checking the 
+proof produced by Umbral), Ursula collects the fees for the provided service. On the other
+hand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.
+
+\subsection{Discussion and Analysis}
+\label{analysis}
+Here we will discuss the security, financial, and performance implications of the 
+proposed solutions to choose the best. This will be delayed until we crystallize the 
+details of each of the solutions.
+
+\subsection{Future Work}
+\label{future-work}
+Most of the future work on the confirm service activity issue 
+will be dedicated to construct a concrete PCD-based solution. This 
+includes the following:
+\begin{itemize}
+\item Understand PCD and its applications in a greater depth. This 
+also requires exploring NIZK in general and SNARKs in specific.
+
+\item Define an efficient output correctness predicate that characterizes 
+the correctness of the statement that PCD will attest for. This could be 
+hard for the confirm activity issue as the value of the output is dynamic 
+based on the workload Ursula may receive.
+
+\item Define a way to compose the proofs efficiently and produce 
+a single proof at the end. This will be tied to the formulated predicate.
+
+\item Argue about the correctness and security of the concrete scheme.
+\end{itemize}
+
+The above will take time, but the good news that this will also be helpful
+to the work on PPSC. So it is more like developing part of the
+background needed for PPSC.

### 2020-04-28 tex/confirm-availability.tex
first cut of confirm availability scheme

\section{Confirm Availability}
In this section, we present a solution for the issue of confirming availability of 
Ursulas. As mentioned before, in the early stage of the network launch we only 
require Ursulas to be online and responsive to any reencryption 
requests issued by Bob.

We begin with the design details of our solution, after which we discuss its 
resilience to any potential security attacks and its efficiency in terms of implementation 
requirements and compatibility with the current status of the NuCypher network.

\subsection{Optimistic Challenge-based Approach}
The proposed solution is centered around two important concepts: requiring minimal 
changes to the current network implementation, and minimizing the additional overhead.

Recall that in the NuCypher network, Bob receives a map from Alice containing 
the set of Ursulas that has the key fragments needed to implement the access control policy. 
When issuing a reencryption request, Bob uses this map to reach each of these Ursulas to obtain 
the service. This communication is one-to-one meaning that no other Ursulas (or any 
NuCypher network participant) mediates the communication between Bob and the target  
Ursula. This in turn means that no one can attest to whether Ursula has responded if Bob 
complains that he did nit hear back.

The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor 
a specific target Ursula and challenge its responsiveness. Hence, it is an optimistic protocol invoked 
only when Bob complains about not receiving the service. In detail, for each round (where a 
round is the time needed to mine a block on the blockchain) a set of Ursulas is selected at 
random. We call these gateway Ursulas. Bob contacts a target Ursula for its request as usual. 
If this Ursula does not respond, Bob complains to a gateway that this target Ursula 
did not respond. At this point, the gateway will act as an intermediary and forwards 
Bob's request to the target Ursula on behalf of Bob and waits for the answer. If the target 
Ursula does not answer, this will trigger other gateways to perform the same process, and if the target 
Ursula is still unresponsive, these gateways will collectively sign a witness against 
this Ursula and publish it (see Section~\ref{cosi} for an overview of collective signing). 
Once this witness is verified by the NuCypher smart contract responsible of service policies, 
part of the target Ursula's stake will be slashed as a punishment.

\paragraph{Gateway Ursulas election.}

\paragraph{Selecting gateway Ursulas to handle a Bob's complaint.}

\paragraph{Witness verification.}

\paragraph{Quantifying the financial punishment or slashing value.}

\paragraph{Operating only during challenge phase.}

\paragraph{DoS attacks.}

\subsection{Security Analysis}

\subsection{Performance Analysis}

### 2020-05-05 tex/intro.tex
fix intro

@@
 adoption. It is expected that these rewards will disappear as the token cap is 
-reached, similar to other cryptocurrencies i the space.
+reached, similar to other cryptocurrencies in the space.
 
-Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake, and the confirmation that she is online.
-Confirming the status of being online is done by having each Ursula call a
-simple function in one of the NuCypher contracts to signal that she is online.
+Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round.
+Confirming the status of being online is done by calling a
+simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
 
@@
 \setlength{\itemsep}{0pt}
-\item The rewards computation (both fees and inflation rewards) is agnostic to the number of 
+\item The rewards computation (both fees and inflation) is agnostic to the number of 
 requests Ursula serves. Thus, an active Ursula who may serve a huge number of 
-requests, and one who does not receive any requests (or a
-malicious/lazy Ursula that does not answer the requests she receives from Bob), will 
+re-encryption requests, and one who does not receive any requests (or a
+malicious/lazy Ursula that does not answer Bob's requests), will 
 both collect the same amount of rewards if they hold identical policies.
@@
 not require any input or proofs from Ursula on providing the service. Ursula 
-can stay offline and not respond to Bobs' requests, and simply come online merely to call the confirm activity
+can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activity
 function. This allows Ursula to collect both inflation rewards 
-and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks (i.e., when policies being managed by Ursula expire). 
+and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire). 
 \end{itemize}
@@
 service activity. We begin with outlining the adopted threat model for each problem 
-definition, as well as the network model Then we present our solutions for each 
-of these problems, discuss the aforementioned
+definition, as well as the network model. Then, we present the proposed solutions, discuss the aforementioned
 trade-offs and requirements of each of them, with the goal of selecting one of these 
-solutions to be adopted in each stage of the NuCypher network operation.
+solutions to be adopted for each stage of the NuCypher network operation.
 
@@
 In order for the proposed solutions to work, we need to ensure freshness, 
-integrity, and authenticity of the requests (or service compliants) issued by Bob. This can be achieved 
-by requiring Bob to sign each request it issues and to include a timestamp, or 
+integrity, and authenticity of the requests (as well as service complaints as we will see later) issued by Bob. This can be achieved 
+by requiring Bob to sign each re-encryption request it issues and to include a timestamp, or 
 sequence number, in each request to ensure freshness. The keypair used for the 
@@
 Bob pay for each requests he issues. Such an arrangement and its implication on the 
-confirm service activity issue will be studied once it becomes part of the NuCypher 
+confirm activity issue will be studied once it becomes part of the NuCypher 
 network protocol.
@@
 \subsubsection{Threat Model.}
-We do not place trust in any party and we assume that all participants are 
+In our threat model, we make the following set of assumptions:
+\begin{itemize}
+\item {\bf Self-interested parties:} We do not place trust in any party and we assume that all participants are 
 self-interested. This means that a party may decide to 
@@
 with other attackers, and such decision is solely based on what maximizes the financial profits
-of this party. Thus, if it is profitable, an Ursula may, for example, spin out  
+of this party.
+
+\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out  
 its own Alice and/or Bob or collude with Alice. We do not consider collusion 
@@
 The above non-collusion assumption does not affect the solutions proposed to handle 
-the confirm service activity discussed in Section~\ref{confirm-service-actiivty}. This 
+the confirm service activity discussed in Section~\ref{confirm-service-activity}. This 
 means that these solutions provide higher 
-security guarantees and address the issue f potential collusion between Bob and Ursula. 
+security guarantees and address the issue of potential collusion between Bob and Ursula. 
 It could be the case that relaxing the requirement of 
@@
 more data about the system operation and the behavior of the participants 
-once the inflation rewards disappears in the system. As such, we leave this 
+once the inflation rewards disappears in the system. Therefore, we leave this 
 issue until later when fees become the only source of rewards for Ursulas.
 
-We also assume that when sampling a subset of Ursulas in the network, 
+\item {\bf Honest Ursulas:} We also assume that when sampling a subset of Ursulas in the network, 
 at least one of them is honest. This assumption can be achieved by 
@@
 in the system.)
+\end{itemize}
 

### 2020-05-05 tex/confirm-availability.tex
confirm availability solution - second cut

@@
 
-Recall that in the NuCypher network, Bob receives a map from Alice containing 
+\paragraph{Discovering working Ursulas.} Recall that in the NuCypher network, Bob receives a map from Alice containing 
 the set of Ursulas that has the key fragments needed to implement the access control policy. 
-When issuing a reencryption request, Bob uses this map to reach each of these Ursulas to obtain 
-the service. This communication is one-to-one meaning that no other Ursulas (or any 
-NuCypher network participant) mediates the communication between Bob and the target  
+When issuing a re-encryption request, Bob uses this map (in association with the network discovery protocol) to reach each of these Ursulas and obtain 
+the service.
+
+In particular, in the NuCypher network there is a separation between the role of a staker and a working Ursula.
+All stakers' Ethereum addresses, along with their stake values, are recorded in one of the NuCypher network smart contracts, namely, the \stakeescrow contract.
+Each of these stakers will be tied, or bonded, to a working Ursula to provide the re-encryption service by having its address listed next to the staker's address.
+
+Note that the \stakeescrow contract does not contain any information about how to reach a specific working Ursula.
+Thus, the map that Bob receives includes only the Ethereum addresses of the working Ursulas.
+To allow the parties to communicate with each other, each participant, i.e., Alice, Bob, Ursula, employs a discovery protocol (more like a gossiping protocol) to discover the IP addresses and ports of the working Ursulas in the network.
+
+The discovery process also includes retrieving the keypair a working Ursula uses for the re-encryption service purposes.
+We call this keypair the stamp of a working Ursula, and we require an Ursula to use its stamp when signing all messages related to the proposed confirm availability protocol.
+
+\paragraph{Optimistic Ursula Challenging.} Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests.
+As noted, this communication is one-to-one meaning that no other Ursulas (or any
+NuCypher network participant) mediates the communication between Bob and each working  
 Ursula. This in turn means that no one can attest to whether Ursula has responded if Bob 
-complains that he did nit hear back.
+complains later that he did not hear back.
 
 The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor 
-a specific target Ursula and challenge its responsiveness. Hence, it is an optimistic protocol invoked 
+a specific working Ursula and challenge its responsiveness. Hence, it is an optimistic protocol invoked 
 only when Bob complains about not receiving the service. In detail, for each round (where a 
 round is the time needed to mine a block on the blockchain) a set of Ursulas is selected at 
-random. We call these gateway Ursulas. Bob contacts a target Ursula for its request as usual. 
-If this Ursula does not respond, Bob complains to a gateway that this target Ursula 
+random. We call these gateway Ursulas. Bob contacts a working Ursula asking for the re-encryption service as usual. 
+If this Ursula does not respond, Bob complains to a gateway that this Ursula 
 did not respond. At this point, the gateway will act as an intermediary and forwards 
-Bob's request to the target Ursula on behalf of Bob and waits for the answer. If the target 
-Ursula does not answer, this will trigger other gateways to perform the same process, and if the target 
-Ursula is still unresponsive, these gateways will collectively sign a witness against 
+Bob's request to this working Ursula on behalf of Bob and waits for the answer. If the working 
+Ursula does not answer, this will trigger other gateways to perform the same process, i.e., forward the request on behalf of Bob and wait for an answer. If the working 
+Ursula is still unresponsive, these gateways will collectively sign a witness, basically a statement saying that the working Ursula was contacted by these gateways and she did not respond, against 
 this Ursula and publish it (see Section~\ref{cosi} for an overview of collective signing). 
-Once this witness is verified by the NuCypher smart contract responsible of service policies, 
-part of the target Ursula's stake will be slashed as a punishment.
+Once this witness is verified by the NuCypher network, 
+part of the working Ursula's stake will be slashed as a punishment.
 
-\paragraph{Gateway Ursulas election.}
+\paragraph{Gateway Ursulas Selection.} Let's assume that for each challenge phase a set of $n$ gateways Ursulas is selected.
+A witness will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).
 
-\paragraph{Selecting gateway Ursulas to handle a Bob's complaint.}
+A simple idea to select the gateways is to use a high entropy source of randomness to obtain a random beacon for each round.
+Then feed this beacon, concatenated with the hash of Bob's request, to an iterative hashing process.
+After each iteration, map the hash to a working Ursula index as listed in the \stakeescrow contract.
+That is, the working Ursula bonded with the first staker listed in the contract has index 0, the next has index 1, and so on.
+Then, rehash the previous hash and map the output to an index.
+If any collision happens, i.e., a previous index is produced again, discard it and proceed to the next hash iteration.
+This process is repeated until a distinct set of $n$ indices is computed.
 
-\paragraph{Witness verification.}
+Note that the selection process may contain Ursulas for which Bob does not have a contact information.
+Hence, Bob has to discover these Ursulas before being able to submit a complain.
+To reduce the delays, and as outlined earlier, Bob starts with complaining to one gateway Ursula and involves the rest if the working Ursula does not respond to the challenge from this gateway.
+Hence, Bob can start with a gateway that he already knows how to reach (if any) and in the meantime works on discovering the rest of the selected gateways (if he does not already have their contact information).
 
-\paragraph{Quantifying the financial punishment or slashing value.}
+Furthermore, the above protocol assumes working in the random oracle model, meaning that hash functions are modeled as random oracles.
+Thus, the iterative hashing process selects at random the working Ursulas.
+Although, we believe this is sufficient for our purposes, this can be replaced with more sophisticated approaches to produce random strings (that are then mapped to indices), e.g., a verifiable random function~\cite{micali1999verifiable}.
+We leave this as part of our future work in case we decide to pursue this path.
 
-\paragraph{Operating only during challenge phase.}
+As for the high entropy source of randomness, there are several potential approaches here.
+We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon} or a combination of multiple sources, for that.
+Or we can work also in the random oracle model and assume that block hashes on the blockchain are drawn from a uniform distribution, and thus, use the block hash as a random beacon.
+In particular, for the current round, the hash of the block that was mined $y$ rounds ago is used ($y$ is confirmation interval in the underlying cryptocurrency system).
+Alternatively, and to avoid the random oracle assumption, we can use randomness extractors to produce a high entropy beacon from the block hashes which itself could be low entropy~\cite{bonneau2015bitcoin}.
 
-\paragraph{DoS attacks.}
+\paragraph{Witness Verification.}
+
+\paragraph{Quantifying the Financial Punishment or Slashing Value.}
+
+\paragraph{Operating Only During The Challenge Phase.}
+
+\paragraph{DoS Attacks.}
+
+\paragraph{Unresponsive Gateways.}
 

### 2020-05-06 tex/confirm-availability.tex
finalize confirm availability solution

@@
 \section{Confirm Availability}
-In this section, we present a solution for the issue of confirming availability of 
-Ursulas. As mentioned before, in the early stage of the network launch we only 
-require Ursulas to be online and responsive to any reencryption 
+In this section, we present a solution for confirming availability of 
+Ursulas. As mentioned before, in the early operation stage of the network we only 
+require Ursulas to be online and responsive to the re-encryption 
 requests issued by Bob.
 
-We begin with the design details of our solution, after which we discuss its 
-resilience to any potential security attacks and its efficiency in terms of implementation 
-requirements and compatibility with the current status of the NuCypher network.
+We introduce the design details of our solution, after which we discuss some potential security attacks and how to address them.
 
@@
 The proposed solution is centered around two important concepts: requiring minimal 
-changes to the current network implementation, and minimizing the additional overhead.
+changes to the current network implementation, and minimizing the additional overhead. \\
 
-\paragraph{Discovering working Ursulas.} Recall that in the NuCypher network, Bob receives a map from Alice containing 
+\noindent{\bf Discovering Working Ursulas.} Recall that in the NuCypher network, Bob receives a map from Alice containing 
 the set of Ursulas that has the key fragments needed to implement the access control policy. 
@@
 
-Note that the \stakeescrow contract does not contain any information about how to reach a specific working Ursula.
+The \stakeescrow contract does not contain any information about how to reach a specific working Ursula.
 Thus, the map that Bob receives includes only the Ethereum addresses of the working Ursulas.
@@
 The discovery process also includes retrieving the keypair a working Ursula uses for the re-encryption service purposes.
-We call this keypair the stamp of a working Ursula, and we require an Ursula to use its stamp when signing all messages related to the proposed confirm availability protocol.
+We call this keypair a stamp, and we require an Ursula to use her stamp when signing all messages related to the proposed confirm availability protocol.
+\\
 
-\paragraph{Optimistic Ursula Challenging.} Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests.
+\noindent{\bf Optimistic Ursula Challenging.} Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests.
 As noted, this communication is one-to-one meaning that no other Ursulas (or any
-NuCypher network participant) mediates the communication between Bob and each working  
+NuCypher network participant) mediates the communication between Bob and working  
 Ursula. This in turn means that no one can attest to whether Ursula has responded if Bob 
-complains later that he did not hear back.
+complains later that he was not served.
 
-The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor 
-a specific working Ursula and challenge its responsiveness. Hence, it is an optimistic protocol invoked 
-only when Bob complains about not receiving the service. In detail, for each round (where a 
-round is the time needed to mine a block on the blockchain) a set of Ursulas is selected at 
-random. We call these gateway Ursulas. Bob contacts a working Ursula asking for the re-encryption service as usual. 
-If this Ursula does not respond, Bob complains to a gateway that this Ursula 
-did not respond. At this point, the gateway will act as an intermediary and forwards 
-Bob's request to this working Ursula on behalf of Bob and waits for the answer. If the working 
-Ursula does not answer, this will trigger other gateways to perform the same process, i.e., forward the request on behalf of Bob and wait for an answer. If the working 
-Ursula is still unresponsive, these gateways will collectively sign a witness, basically a statement saying that the working Ursula was contacted by these gateways and she did not respond, against 
-this Ursula and publish it (see Section~\ref{cosi} for an overview of collective signing). 
-Once this witness is verified by the NuCypher network, 
-part of the working Ursula's stake will be slashed as a punishment.
+The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor a specific working Ursula and challenge its responsiveness.
+Hence, it is an optimistic protocol invoked only when Bob complains about not receiving the service.
+In detail, for each round (where a
+round is the time needed to mine a block or several blocks on the blockchain) a set of Ursulas is selected at random.
+We call these gateway Ursulas.
+Bob contacts a working Ursula asking for the re-encryption service as usual.
+If this Ursula does not respond, Bob complains to a gateway about it.
+At this point, the gateway will act as an intermediary and forwards Bob's request to this working Ursula on behalf of Bob and waits for the answer.
+If no answer is received, this gateway will trigger other gateways to perform the same process, i.e., forward the request on behalf of Bob and wait for an answer.
+If the working
+Ursula is still unresponsive, these gateways will collectively sign a proof-of-unavailability, which is basically a statement saying that the working Ursula was contacted by these gateways and she did not respond, and publish it through the \stakeescrow contract (see Section~\ref{cosi} for an overview of collective signing).
+Once the proof-of-unavailability is verified, part of the working Ursula's stake will be slashed as a punishment.
+\\
 
-\paragraph{Gateway Ursulas Selection.} Let's assume that for each challenge phase a set of $n$ gateways Ursulas is selected.
-A witness will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).
+\noindent{\bf Gateways Selection.} For each round a set of $n$ gateways Ursulas will be selected.
+A proof-of-unavailability will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).
 
 A simple idea to select the gateways is to use a high entropy source of randomness to obtain a random beacon for each round.
-Then feed this beacon, concatenated with the hash of Bob's request, to an iterative hashing process.
+Then feed this beacon into an iterative hashing process.
 After each iteration, map the hash to a working Ursula index as listed in the \stakeescrow contract.
-That is, the working Ursula bonded with the first staker listed in the contract has index 0, the next has index 1, and so on.
-Then, rehash the previous hash and map the output to an index.
-If any collision happens, i.e., a previous index is produced again, discard it and proceed to the next hash iteration.
-This process is repeated until a distinct set of $n$ indices is computed.
+That is, the working Ursula bonded with the first staker listed in the contract has index 0, the next has index 1, etc.
+Then, rehash the previous hash and map the output to an index, and so no.
+In case of a collision, i.e., an already selected index is produced again, discard it and proceed to the next hash iteration.
+This process is repeated until a set of distinct $n$ indices is computed.
 
 Note that the selection process may contain Ursulas for which Bob does not have a contact information.
-Hence, Bob has to discover these Ursulas before being able to submit a complain.
-To reduce the delays, and as outlined earlier, Bob starts with complaining to one gateway Ursula and involves the rest if the working Ursula does not respond to the challenge from this gateway.
+Hence, Bob has to discover these Ursulas before being able to submit a complaint.
+To reduce the delays, and as outlined earlier, Bob starts with complaining to one gateway and involves the rest if the working Ursula does not respond to the challenge from this gateway.
 Hence, Bob can start with a gateway that he already knows how to reach (if any) and in the meantime works on discovering the rest of the selected gateways (if he does not already have their contact information).
@@
 As for the high entropy source of randomness, there are several potential approaches here.
-We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon} or a combination of multiple sources, for that.
-Or we can work also in the random oracle model and assume that block hashes on the blockchain are drawn from a uniform distribution, and thus, use the block hash as a random beacon.
-In particular, for the current round, the hash of the block that was mined $y$ rounds ago is used ($y$ is confirmation interval in the underlying cryptocurrency system).
+We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon} or even a combination of multiple sources, for that.
+Or we can work also in the random oracle model and assume that block hashes are drawn from a uniform distribution, and thus, use the block hash as a random beacon.
+In particular, for the current round, the hash of the block that was mined $y$ rounds ago is used ($y$ is the confirmation interval in the underlying cryptocurrency system).
 Alternatively, and to avoid the random oracle assumption, we can use randomness extractors to produce a high entropy beacon from the block hashes which itself could be low entropy~\cite{bonneau2015bitcoin}.
+\\
 
-\paragraph{Witness Verification.}
+\noindent{\bf Proof-of-unavailability processing.} As mentioned previously, a proof-of-unavailability against a working Ursula is a statement stating that this Ursula was unavailable during a specific round signed by at least $t$ gateways out of the $n$ gateways selected for that round.
+Such a proof is submitted to the \stakeescrow contract and is verified as follows:
+\begin{itemize}
+\item Produce the list of gateways selected for the current round. This is done by using the same process described previously.
 
-\paragraph{Quantifying the Financial Punishment or Slashing Value.}
+\item Verify the collective signature over the signed statement (see Section~\ref{cosi}).
 
-\paragraph{Operating Only During The Challenge Phase.}
+\item If everything is fine, the \stakeescrow contract revokes part of the stake bonded to the working Ursula as a punishment.
+\end{itemize}
 
-\paragraph{DoS Attacks.}
+Note that the above assumes that the \stakeescrow contract is aware of the gateways' stamps (or keys) that are used in signing the proof-of-unavailability.
+This can be done by either expanding the staker list in the contract to contain not only the Ethereum addresses of working Ursulas, but also their stamps.
+Another option is to piggyback the stamps (signed by using the key corresponding to the working Ursula's Ethereum address) with the proof-of-unavailability.
+A more simpler, and efficient, option is to sign the proof-of-unavailability by using the key corresponding to the working Ursula's Ethereum address in the first place, and thus, the \stakeescrow contract will not need an additional information.
+Which option to use depends merely on efficiency considerations.
+\\
 
-\paragraph{Unresponsive Gateways.}
+\noindent{\bf Quantifying the Financial Punishment or Slashing Value.}
+A question that comes to mind is how much should be revoked from Ursula's stake once a proof-of-unavailability is approved?
+Quantifying this amount should be driven by two factors; the unavailability duration and the utility gain (or profits) of this cheating behavior in terms of the collected fees and inflation rewards for that duration.
 
-\subsection{Security Analysis}
+Accordingly, we can compute this value to be equal to the fees and inflation rewards that an Ursula is supposed to receive in a round (recall that a round is the time needed to mine a block or several blocks on the blockchain).
+Hence, the working Ursula will, first, lose her fees and inflation rewards from the network, and second, lose the same amount from her stake.
+Such a loss will take place even if a single proof-of-unavailability is received against a working Ursula within a round.
+In fact, the \stakeescrow contract will process only one proof against a working Ursula per round to reduce computational costs in the system.
+\\
 
-\subsection{Performance Analysis}
+\noindent{\bf Working Only During the Challenge Phase.}
+A potential issue under the proposed optimistic scheme is that a working Ursula may operate only during the challenge phase.
+That is, she ignores any fresh request coming from Bob, and just replies afterwards when receiving the same request again (i.e., when it is forwarded by the gateways during the challenge phase).
+
+We argue that such a behavior is not a practical issue since a rational Ursula will be online eitherway to monitor whether this is a challenge phase or not, and that the amount of work needed to respond to a re-encryption request is minimal.
+Hence, there is no incentive at all to follow this strategy, meaning that a rational Ursula will act honestly.
+\\
+
+\noindent{\bf DoS Attacks.} 
+Another potential issue is exploiting the unavailability complaints to perform a DoS attack against the gateways and working Ursulas.
+In detail, Bob may lie and issue complaints against working Ursulas even though they are responsive just to slash their stakes.
+Or an attacker may replay these complaints, or issue them on behalf of Bob, to slash a working Ursula.
+Or the goal could be to overwhelm the gateways with the challenge process and make them unavailable to perform the re-encryption service (recall that the gateways are originally working Ursulas in the NuCypher network).
+
+This issues can be handled using a collection of techniques as follows:
+\begin{itemize}
+\item Require Bob to sign all the complaints (so no one can impersonate Bob unless they know his signing key), and include a timestamp or a sequence number in each of them (to ensure freshness and prevent replay attacks).
+
+\item Increase the cost of issuing complaints.
+That is, require Bob to do some work in order to produce a valid complaint (in a similar way to proof-of-work, i.e., produce a hash over the complaint with specific number of leading zeros).
+\end{itemize}
+
+\noindent{\bf Unresponsive Gateways.}
+A third issue that we may encounter in the proposed solution is that the gateways themselves could be unresponsive.
+This will stall the challenge phase and make it infeasible to prove that some working Ursula is unavailable.
+We believe that such an issue will be organically handled by the network.
+That is, the larger the number of Ursulas in the network, the higher the chances of having more honest Ursulas.
+By increasing the number of selected gateways $n$, and given that the selection process is random, the chances of having at least $t$ honest gateways in a round will be high.
+
+Another mechanism is to incentivize the gateways to do the work in the form of a small fee paid out of the revoked stake.
+
+It could be the case that all gateways in a round are responsive (although we believe that the probability this happens is very low).
+In this case, it could be viable to perform the challenge phase in a recursive way.
+In other words, Bob can send an unavailability complaint against the gateways of the current round to the gateways of the previous round.
+The previous round gateways will in turn challenge the current round gateways by forwarding Bob's complaint to them and sign a proof-of-unavailability if no response is received.

### 2020-05-06 tex/confirm-service-activity.tex
fix intro
finalize confirm availability solution

@@
 \section{Confirm Service Activity}
-\label{confirm-service-actiivty}
+\label{confirm-service-activity}
 In this section, we present potential solutions for the confirm service activity 
@@
 \end{itemize}
-
-The above will take time, but the good news that this will also be helpful
-to the work on PPSC. So it is more like developing part of the
-background needed for PPSC.

### 2020-06-03 CESC-submission/paper.tex
add CESC submission

\documentclass{llncs}
\pdfoutput=1

\usepackage{algorithm, algpseudocode}
\renewcommand{\algorithmiccomment}[1]{/*#1*/}
\usepackage{epsfig, endnotes, url, color, graphicx}
\usepackage{mathtools, amsmath, amsfonts}
\usepackage{diagbox, booktabs, colortbl}
\usepackage{breakurl, listings, framed}
\usepackage{multirow, caption, subcaption}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace, slashbox, enumitem, bm}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}

\pagestyle{plain}

\captionsetup[subfigure]{justification=raggedright}

\captionsetup{compatibility=false}
\def\UrlBreaks{\do\/\do-}
{\renewcommand{\arraystretch}{1.2}
\makeatletter
\newcommand{\@chapapp}{\relax}%
\makeatother

\usepackage[title]{appendix}

\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\newcommand{\ignore}[1]{}
\newcommand\ghada[1]{\nbc{GA}{#1}{blue}}
\newcommand{\fake}[1]{{\color{magenta} [fake: #1]}}

\input{annotations}

% Ghada: added to remove running headers
\pagestyle{plain}

\begin{document}
%
% paper title
\title{\Large \bf Rethinking Service Systems: \\
A Path Towards Secure and Equitable Resource Markets
}

\author{Ghada Almashaqbeh} 
%
\authorrunning{G. Almashaqbeh}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{NuCypher \\
\email{ghada@nucypher.com}}

\maketitle

\begin{abstract}
Escalating demand for digital services has motivated building non-traditional solutions to reduce costs and achieve a greater level of flexibility. Among these solutions, peer-assisted models are gaining more popularity in replacing infrastructure-based (possibly) centralized approaches. Cryptocurrencies have strengthened this trend by providing a fully distributed mechanism to reward for the service, and their blockchains and consensus protocols offer a trustless and publicly verifiable way to govern the system. We present a generic framework for building distributed service markets by utilizing these new technologies. We also discuss the security and efficiency challenges, with a focus on how the economic aspects impact system design and threat mitigation, and conclude with some potential solutions.
\end{abstract}

\section{Introduction}
Usually, when obtaining digital services, we deal with traditional systems that are centrally managed. Most of the time, we resort to third party providers, e.g., commercial companies,  to obtain services like file storage, content distribution, computation outsourcing, and many others. Despite being effective and widely deployed, this centrally-managed paradigm introduces several trust, cost, and transparency issues. It requires establishing complex business relationships with these companies, where customers usually overprovision their needs in order to handle future peak demands~\cite{Kassa13,Nicolae14}. Also, it constrains the customers with the service specifications these companies can offer, like the geographic coverage and service speed, not to mention the limited visibility into the real status of the system regarding its performance and the available amount of resources.

These issues motivated the community to revisit old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others. In order to encourage the collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources. This paradigm builds flexible systems, where anyone can start or stop the service at any time. It also scales more easily with demand and extends the network coverage because peers from anywhere can join. Furthermore, this paradigm builds transparent and equitable ecosystems in which participants can negotiate service terms and price directly instead of having a few entities monopolizing the market.

\begin{table}[t!]
\caption{Examples of centrally-managed digital services and their counterparts of P2P-based ones.} 
\label{service-examples}
%\vspace{-10 pt}
\centering 
\begin{tabular}{| p{0.32\columnwidth}  | p{0.32\columnwidth} | p{0.32\columnwidth} |}\hline\hline

{\bf Service Type} & {\bf Traditional Solution} & {\bf P2P-based Solution}  \\[0.5ex] \hline \hline

Payments & Banks & Bitcoin  \\[0.5ex] \hline

File storage & Dropbox~\cite{dropbox} &  Filecoin~\cite{filecoin}  \\ [0.5ex]  \hline

Content distribution & Akamai~\cite{akamai} & CacheCash~\cite{almashaqbeh2019cachecash}  \\ [0.5ex]  \hline

Key management system & Azure Key Vault~\cite{azure} & NuCypher~\cite{nucypher}  \\ [0.5ex]  \hline

\end{tabular}
\end{table}

Although monetary-incentivized P2P-based systems are an old idea, especially for content sharing, most of existing solutions introduce some form of centralization or trust. They either rely on centralized payment services, place trust in specific parties to handle these payments and solve disputes, or even rely on some centralized entities to manage participants and defend against some security threats~\cite{Kassa13,Nair08,Zhang09}. Such design choices bring us back to the central management model and the trust issues of traditional solutions.

The evolution of cryptocurrencies and blockchain technology~\cite{bitcoin,ethereum} has provided templates for reshaping large-scale distributed systems and services. Cryptocurrencies implement a decentralized virtual currency exchange medium that permits participants to be rewarded without any pre-authentication or identification requirements. And their underlying blockchains and consensus protocols support public verifiability, auditing, and decentralized governance without needing to place trust in any entity. These features can be exploited in P2P-based schemes to manage and pay for the correct service without driving the system toward centralization (see Table~\ref{service-examples} for examples of traditional service solutions and their P2P counterparts).

However, the open access environment of P2P networks (i.e., allowing anyone to join and dealing with untrusted participants) introduces several security and performance challenges that need to be addressed before having any practical deployment. In addition, having monetary incentives motivates attackers to attack the system in novel ways to maximize their financial profits. Thus, traditional practices of secure systems design need to be modified and adapted to account for such factors.

To address these issues, in this talk we present a generic framework for designing secure, scalable, and equitable resource markets to provide services in a fully distributed way. This framework accounts for the economic aspects of this service paradigm covering both market viability (compared with traditional ones) and the impact of monetary incentives on system security (in terms of identifying financially-motivated threats and building economic or game-theoretic mitigation techniques). We conclude with zooming on one of the important security facets of monetary-incentivized decentralized services, namely, addressing accounting attacks, i.e., how to prove that service has been delivered, or alternatively payments are well deserved. We elaborate on our experience in designing distributed access control services at NuCypher~\cite{nucypher} and the solutions we developed to thwart these attacks. We also show how the financial motivations of attackers vary based on the operation stage of the network (early launch vs. long term operation) and how threat mitigation techniques vary accordingly.

\section{Distributed Resource Markets Design}
One of the effective ideas for building fully decentralized and equitable services is to build distributed markets to trade resources. That is, implement a protocol that allows anyone to join to serve others and collect payments in return. Such an approach needs to solve several challenges introduced by the open access and decentralized work environment. In other words, dealing with untrusted, possibly financially motivated participants requires deploying additional measures that may impact efficiency, usability, and compatibility with existing infrastructures. Consequently, there is a need for carefully-tailored threat mitigation techniques and efficiency optimization mechanisms in order to promote the adoption of these systems.

\begin{figure}[ht!]
\centerline{
\includegraphics[height= 1.2in, width = 1.0\columnwidth]{figures/design-steps.pdf}}
\caption{Design process of distributed resource markets.} \label{design-steps}
\vspace{-12pt}
\end{figure}

In this section, we discuss the main steps and challenging issues that need to be considered when designing a distributed service system. These steps are captured at a high level in Figure~\ref{design-steps}, which we discuss in greater details in the following paragraphs. \\

\noindent{\bf Viability Assessment.} Before looking into building a distributed resource market, one has to assess its viability. This includes studying the demand side (who is interested in the service) and the supply side (who can provide it) to answer several questions; Are there tangible advantages to encourage replacing traditional solutions with fully distributed ones? Can the system match the reliability and performance offered by these traditional solutions? and does providing the service require large amounts of resources that exceed the capabilities of average end-users? Such a viability study is an important step to assess the potential for practical adoption before investing time and effort into building the system. \\

\noindent{\bf Threat Modeling.} Despite the many advantages they offer — decentralization, transparency, and lowered service costs — there is still a big gap between the promise of P2P-based systems and their performance in practice. Adding monetary incentives, by using another P2P-based payment service, i.e., cryptocurrencies, widens this gap. This is due to the perception that these systems are not secure, where the recent large number of security breaches give credence to these doubts~\cite{benebit-scam,binance-hack,bitcoin-cash-hack,bitcoingold-double-spending,exchange-hack-b,bitfloor-hack,korea-exchange-hack,eth-hack,ico-hack-b,exchange-hack,enigma-hack,mine-hack}.

The best practice for designing a secure system requires a threat modeling step to investigate potential security risks. Such a model can guide designers in deploying the proper countermeasures, and evaluating the security level of a system. For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion.

This observation encouraged the community to visit old threat modeling frameworks and adapt them to address these issues. For example, the ABC framework~\cite{Almashaqbeh19} was designed to achieve these goals by accounting for both the underlying cryptocurrency medium and the service provided on top of it. ABC enables building comprehensive threat models by holistically analyzing the threat space while managing its complexity, and distilling the impactful cases that need to be neutralized to secure the system. It also allows classifying threats based on their mitigation techniques, i.e., threats that can be addressed cryptographically or algorithmically, and these that require game theoretic means, thus providing insights about the proper measures to deploy.

It should be noted that the threat modeling step need to be revisited each time the system design is altered. Furthermore, it should be performed as the last step before shipping the system to argue formally about its security.  \\

\noindent{\bf Unique Aspects of Operating a Distributed Market.} The open access work environment helps to create flexible services and transparent ecosystems. However, this comes at a cost. Dealing with untrusted parties means that fair exchange is impossible~\cite{Even80,Pagnia99}, which raises the question of when to pay servers - before or after providing the service? If paid first, a malicious server may not serve the customer, and if served first, a malicious customer may not pay afterwards.

Furthermore, accounting attacks, in which participants collude with each other pretending that the service has been delivered, could be a hammer that may destroy the market. This is a particular problem in systems that require sponsoring service requests. For example, in content distribution, a publisher (e.g., Netflix) can hire caches to distribute content to its clients, and hence, it pays for the service. In this case, caches (or servers in general) and clients may collude so that clients pretend to be served, allowing servers to collect payments from the sponsor for free.

The above security issues (an many others depending on the service type) require a careful design of a decentralized service-payment exchange protocol that can reduce the risks of dealing with untrusted, possibly colluding parties. Such a protocol represents the backbone of the resource market; if it fails the whole market fails. Servers will not be willing to participate if they are not being paid, and same for customers, they will not be willing to use the system if they pay for a service that they do not receive. Operating the market also requires devising mechanisms for service pricing, term negotiation for server recruiting, and matching protocols to match these servers with interested customers. \\

\noindent{\bf Financial and Cryptographic Security Measures.} Usually, security threats are mitigated by using cryptographic means (e.g., encryption and digital signatures), or algorithmic approaches (e.g., ordering the actions in a way that enforces secure behavior). Monetary-incentivized systems introduce new types of attacks that cannot be addressed using conventional approaches. In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means. These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock a penalty deposit that is forfeited if he/she is caught cheating. Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly. And third, designing service pricing policies that make it more profitable on the long run to act honestly in every service request than cheating (even if cheating is not detected). Such techniques make cheating unprofitable so that rational parties will choose to follow the protocol.

For example, to reduce the risks of the impossibility of fair exchange, micropayments can be employed. That is, instead of paying a large chunk of money for the full service, the payment is divided into small values, each of which is exchanged for a small service amount. For instance, one can pay for retrieving a file in small data chunks instead of paying for the full retrieval all at once. Hence, a server loses a small payment if a client does not pay after receiving a chunk. Similarly, a client loses a small payment if it pays in advance and the server does not send a data chunk in return.

On the other hand, to thwart accounting attacks, system designers need to incorporate suitable techniques to prove or confirm resource expenditure, and consequently, confirm that payments are well deserved. In online content delivery, for example, the CAPnet puzzle~\cite{Almashaqbeh19b} can be used to ensure that caches have delivered the requested content. The design of this puzzle follows the second category mentioned above, where solving the puzzle without doing the work is more expensive (resources-wise) than solving it after retrieving the content. In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a server is still storing the clients’ files with the agreed-upon number of replicas. Here, a detect-and-punish mechanism is used, where failing in providing a correct proof leads to slashing part of the deposit a server pledged when joining the system~\cite{filecoin}. Thus, the type of the provided service directly influences the delivery confirmation mechanism that need to be deployed. \\

\noindent{\bf Optimize for Efficiency.} Although designing a secure system is the ultimate goal, efficiency is an important driving factor of practical adoption and deployment. System designers need to exploit any opportunity that allows for optimizing performance. This also involves choosing the right trade-off between security and efficiency in the sense of risk management. That is, threats that have high impact need to be prioritized over low impact ones. Moreover, looking into alternative cryptographic primitives that are lightweight, or optimize their implementation, while maintaining the required security guarantees is another effective venue to utilize.

Furthermore, reducing interaction between participants is beneficial. It speeds up the service and promotes the system’s scalability. This can take the form of batching requests/replies between customers and servers to reduce costs and optimize resource allocation, in addition to batch or aggregate record verification on the blockchain.

Another important aspect is related to handling micropayments. Micropayments create a scalability problem as they produce a huge number of transactions that overwhelm the system and require large processing fees. Here, probabilistic schemes are useful in aggregating the small transactions into few larger ones before processing~\cite{Wheeler96,Rivest97}. In particular, payments take the form of lottery tickets, and only winning tickets are processed in the system with values that compensate properly for the tickets exchanged so far. Several fully-distributed micropayment schemes exist in the literature~\cite{Pass15,Chiesa17,Almashaqbeh20} that provide trade-offs between efficiency, anonymity, and security guarantees. \\

\noindent{\bf Testing and Deployment.} To examine the viability of the system, conventional practices of prototyping, benchmarking, and controlled deployment can be used to evaluate both efficiency and resistance to attacks. These provide a starting point to attract early adopters and test the system at a large scale. This stage may inspire designers to revisit specific parts of the system for further optimization based on the results of the conducted experiments, or feedback from the community based on a testnet deployment for example. Testing and improving also continue beyond the testing stage, i.e., after public launch, but deploying protocol modifications could be harder especially if they result in hard forks or community division.

\section{Impact of Financial Incentives on Service Delivery}
\vspace{-4pt}
In this section, we elaborate on one of the important issues in distributed resource markets, namely, service delivery. We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the servers. In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming servers' activity. We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impact the financial motivations of attackers. Such an issue is a great example of how cryptocurrency-based services introduce new economic aspects that may evolve over time, which need to be reflected on the system design. \\

\noindent{\bf An overview of the NuCypher network.} The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the ciphertext without revealing anything about the
decryption keys or the raw data to the intermediate servers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. Therefore, the stake value influences the service load an Ursula
may receive. This stake is also used to punish Ursula financially, by revoking part 
of it, if she cheats and this cheating is detected.

Alice joins the network by creating a policy to be implemented by a 
set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
need to answer requests coming from Bob(s), as well as the duration of the policy, which 
is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
Alice will lock an amount of Ether into the policy contract to be used to pay Ursulas for the re-encryption 
service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
NuCypher rules of preparing access control policies.

Bob, on the other hand, does not deal with currency in the system at all. He interacts with the storage 
network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
re-encryption service. \\

\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for the re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is inflation rewards, i.e., newly minted NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage adoption. It is expected that these rewards will disappear as the token cap is reached, similar to other cryptocurrencies in the space.

Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round. Confirming the status of being online is done by calling a 
simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online. Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.

Although this approach of rewards computation and activity monitoring was enough to reach a MVP, we acknowledge that it suffers from two main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation (both fees and inflation) is agnostic to the number of requests Ursula serves. Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or amalicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of rewards if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service. Ursula can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activityfunction. This allows Ursula to collect both inflation rewards and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire). 
\end{itemize}

Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity. Then we need to adapt the reward computation accordingly to factor in the amount of delivered service. These are introduced in the rest of this section. \\

\noindent{\bf Problem definition based on network operation stage.} The confirm activity problem is defined differently based on the stage of the network operation. In early network launch, when inflation rewards are 
still distributed, we are concerned with the availability of Ursulas and being willing to 
serve all requests coming from Bob. In other words, regardless of the number of requests served, the rewards value (both inflation and fees) will be computed based on the period during which Ursula 
is online and well-behaving. While in later stages, when inflation rewards disappear 
and only fees exist, confirm activity will be tied to providing the re-encryption 
service in the sense that the payment will be computed based on the amount of 
service provided. This requires Ursula to confirm its activity by proving that she served 
a given number of distinct re-encryption requests during a given period. To make the distinction 
clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
service activity}. \\

\noindent{\bf Confirm availability and service activity solutions.} In~\cite{confirm-activity-draft}, we introduce several solutions for both forms of the above problem. These solutions differ in the trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly in what follows. Before that, we review the adopted threat model.

\paragraph{Threat model.} We do not place trust in any party and we assume that all participants are rational and self-interested. Thus, they may follow the protocol or deviate from it, either acting on their own or in collusion with each other, based solely on what maximizes their utility gain.

However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically efficient, and hence, not an issue in our system. The reason is that the amount of work an Ursula does when replying to a re-encryption request is minimal. This means that colluding with Bob will save minimal resources, which makes this collusion case unappealing to rational Ursulas. This case is a great example of how traditional threat modeling and risk management practices differ from those economic-oriented ones in ruling out financially-inefficient threats.

Moreover, we assume that when sampling a subset of Ursulas in the network, at least one of them is honest. This assumption can be achieved by having a global assumption regarding the lower bound of the number of 
honest Ursulas with respect to the total number of Ursulas in the system.\footnote{Or it can be achieved by deploying a special entity like an external verifier, that changes on a periodic basis, or one by the NuCypher company, that is trusted to faithfully participate as a member of each sampled set. This verifier does not provide any other services in the system.}

\paragraph{Confirm availability solution.} Here we use a detect-and-punish approach embedded within an optimistic service monitoring process. This means that it is only invoked when Bob complains that an Ursula is unresponsiveness. In detail, for each round\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process. Then map each hash to an Ursula index as found in the list of working Ursulas recorded on the blockchain within the StakeEscrow smart contract of NuCypher. This process is repeated until a set of distinct Ursulas is selected. Note that anyone can perform this process and verify its outcome.} Bob proceeds as usual by contacting the list of working Ursulas received from Alice for the re-encryption service. If a working Ursula does not reply, Bob complains to a gateway Ursula and hands her the request. This gateway mediates the service process in order to check if Bob's claim is valid. In other words, she challenges the working Ursula by forwarding the request again and waiting for an answer. If one is received, the gateway forwards it to Bob and closes the complain.

On the other hand, meaning no response is received, the gateway notifies the rest of gateways selected for that round to repeat the same process. If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submit this proof to the NuCypher staking contract. At that time, a part of the working Ursula stake is slashed (with a value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment. This punishment makes cheating unprofitable, and hence, unappealing to rational working Ursulas. A detailed technical version of this solution is available in~\cite{confirm-activity-draft}.

As long as Ursula is behaving well and no valid complaints from Bob, this Ursula will collect both inflation rewards and service fees in proportion to her availability period and the number of policies she holds. In other words, reward computation follows the same current approach outlined earlier since our concern is to encourage adoption especially when service demand is low at the beginning.

\paragraph{Confirm service activity solutions.} Here we have three solutions that differ in their security assumptions and efficiency. We refer to them as zero knowledge proof-based (ZKP-based), committee-attestation, and commit/challenge/open-based. Again, we provide a high level description in what follows while a more complete version can be found in~\cite{confirm-activity-draft}.

As for the \emph{ZKP-based} solution, recall that in the NuCypher network each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}. We can combine the proofs of all served requests within a round into one attesting to the following statement: "An Ursula has served $\omega$ distinct requests correctly" for some positive integer $\omega$ representing the number of served requests. This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.

An alternative, possibly more efficient approach is to view the statement "An Ursula has served $\omega$ distinct requests correctly" as an instance of the arithmetic circuit satisfiability problem and utilize bulletproofs\footnote{Bulletproofs are a highly efficient ZKP system that does not require any trusted setup.} to prove its correctness in zero knowledge~\cite{bunz18}. That is, build a circuit that takes the set of correctness proofs of the served requests as well as their number $\omega$ as inputs, and then output 0 if number of correct distinct proofs equals to $\omega$. Then, invoke a circuit parser to convert the circuit into the bulletproof format, which allow the prover, Ursula in this case, to produce a single proof. Then, Ursula submits the proof to the service policy contract. Once the proof is verified, the contract disperses the service fee (in proportion to $\omega$) from Alice's escrow to Ursula's account.

As for the \emph{committee-attestation} approach, it also relies on electing a committee of Ursulas (and possibly outsider verifiers as mentioned previously) to attest for the work load an Ursula served. That is, a working Ursula sends all Bob requests she served along with the correctness proofs to this committee. After verifying all the proofs, the committee collectively signs a statement as above which is submitted to the policy contract so Ursula can claim her payment.

Lastly, we have a \emph{commit/challenge/open} approach, which is inspired from the Merkle tree-based ZKP system proposed in~\cite{dottling19}. Ursula constructs a Merkle hash tree of all served requests and their correctness proofs in a round. Then, it uses the root as a random beacon to be fed into an iterative hash process to select $n$ leaf nodes at random to open them (i.e., these are the challenges). Ursula signs the Merkle tree root, provides the challenge leaf nodes along with their membership paths to either a sidechain (which is maintained by round-selected committee) or to the policy contract to verify. As noted, the security provided here is statistical in the sense that we need to bound the probability by which an Ursula can cheat, like for example she may replicate requests in the tree and add fabricated ones to increase $\omega$.

\paragraph{Discussion.} Which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network. The ZKP-based solution (the one utilizing bulletproofs) provides several advantages including non-interactivity (as opposed to the committee-attestation one that needs interaction with the committee). It also supports computational soundness as opposed to the statistical one of the commit/challenge/open solution. Nonetheless, it could be the case that the other solutions are more efficient especially if we incorporate committee attestation or sidechains to support other functionalities in the network.

\section{Conclusion}
While centrally-managed systems provide reliable services, they introduce trust, cost, and transparency issues. This motivated developing non-traditional peer-assisted models to create distributed resource markets that are open to anyone to join and serve others while collecting payments in return. However, such a paradigm comes with security and performance challenges that need to be addressed before having any practical deployment. Our work puts forward a generic framework for designing efficient and secure resource markets. It also examines in a greater depth how financial incentives affect security measures deployment and system design choices.

{\footnotesize \bibliographystyle{acm}\vspace{-6pt}

\bibliography{marketBib}}

\normalsize

% that's all folks
\end{document}

### 2020-06-03 confirm-activity/tex/abstract.tex
add CESC submission

\begin{abstract}
In this document we introduce several aspects related to the confirm activity problem in 
the NuCypher network. These include the different definitions of this problem, the 
underlying threat model, the current adopted solution, and its relation 
to both service fees and inflation rewards. In particular, we consider two flavors of the confirm activity issue, namely, confirm availability 
and confirm service activity. The former confirms that Ursula is available all the time 
and replies to all requests coming from Bob, while the latter provides a proof that an 
Ursula has served a specific number of distinct re-encryption 
requests within a given a period. We present potential solutions 
for each of these flavors and discuss at 
what stage of the network operation they are likely to be used.
\end{abstract}

### 2020-06-03 CESC-submission/paper.tex
extend discussion

@@
 
+Another issue is regarding the payment computation.
+During early stages when the network launches, we anticipate a limited adoption and service demand.
+Thus, we reward Ursulas for just being online to encourage adoption.
+While in later stages, payments will be dispensed in proportion to the actual amount of service an Ursula provides.
+This is due to the fact that later on the inflation rewards will disappear, i.e., all tokens in the network will be minted, and the service fees are the only source of income.
+To incentivize Ursula to provide a correct and timely service, these rewards should be computed based on the actual amount of service.
+This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
+
 \section{Conclusion}

### 2020-06-04 CESC-submission/paper.tex
Edits & suggestions

--- 2020-06-03 CESC-submission/paper.tex
@@
 Among these solutions, peer-assisted models are gaining more popularity in replacing infrastructure-based (possibly) centralized approaches.
-Cryptocurrencies have strengthened this trend by providing a fully distributed mechanism to reward for the service, and their blockchains and consensus protocols offer a trustless and publicly verifiable way to govern the system.
+Cryptocurrencies have strengthened this trend by providing a fully distributed mechanism to compensate service provision, and their blockchains and consensus protocols offer a trustless and publicly verifiable way to govern the system.
 We present a generic framework for building distributed service markets by utilizing these new technologies.
-We also discuss the security and efficiency challenges, with a focus on how the economic aspects impact system design and threat mitigation, and conclude with some potential solutions.
+We also discuss the security and efficiency challenges, with a focus on how the economic considerations impact system design and threat mitigation, and conclude with some potential solutions.
 \end{abstract}
@@
 In order to encourage the collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources.
-This paradigm builds flexible systems, where anyone can start or stop the service at any time.
+This paradigm builds flexible systems, where customers can start or stop the service at any time.
 It also scales more easily with demand and extends the network coverage because peers from anywhere can join.
@@
 In addition, having monetary incentives motivates attackers to attack the system in novel ways to maximize their financial profits.
-Thus, traditional practices of secure systems design need to be modified and adapted to account for such factors.
+Thus, traditional practices of secure systems design need to be modified and expanded to account for such factors.
 
@@
 Such a model can guide designers in deploying the proper countermeasures, and evaluating the security level of a system.
-For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion.
+For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion or sybil attack.
 
@@
 
-It should be noted that the threat modeling step need to be revisited each time the system design is altered.
+It should be noted that the threat modeling steps need to be revisited each time the system design is altered.
 Furthermore, it should be performed as the last step before shipping the system to argue formally about its security.
@@
 However, this comes at a cost.
-Dealing with untrusted parties means that fair exchange is impossible~\cite{Even80,Pagnia99}, which raises the question of when to pay servers - before or after providing the service?
-If paid first, a malicious server may not serve the customer, and if served first, a malicious customer may not pay afterwards.
+Dealing with untrusted parties means that fair exchange is impossible~\cite{Even80,Pagnia99}, which raises the question of when to pay service-providers - before or after providing the service?
+If paid first, a malicious service-provider may not serve the customer, and if served first, a malicious customer may not pay afterwards.
 
@@
 For example, in content distribution, a publisher (e.g., Netflix) can hire caches to distribute content to its clients, and hence, it pays for the service.
-In this case, caches (or servers in general) and clients may collude so that clients pretend to be served, allowing servers to collect payments from the sponsor for free.
+In this case, caches (or service-providers in general) and clients may collude so that clients pretend to be served, allowing service-providers to collect payments from the sponsor for free.
 
@@
 Such a protocol represents the backbone of the resource market; if it fails the whole market fails.
-Servers will not be willing to participate if they are not being paid, and same for customers, they will not be willing to use the system if they pay for a service that they do not receive.
-Operating the market also requires devising mechanisms for service pricing, term negotiation for server recruiting, and matching protocols to match these servers with interested customers.
+Service-providers will not be willing to participate if they are not being paid, and same for customers, they will not be willing to use the system if they pay for a service that they do not receive.
+Operating the market also requires devising mechanisms for service pricing, term negotiation for service-provider recruiting, and matching protocols to match these service-providers with interested customers.
 \\
@@
 In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means.
-These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock a penalty deposit that is forfeited if he/she is caught cheating.
+These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock collateral that is forfeited if he/she is caught cheating.
 Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly.
-And third, designing service pricing policies that make it more profitable on the long run to act honestly in every service request than cheating (even if cheating is not detected).
-Such techniques make cheating unprofitable so that rational parties will choose to follow the protocol.
+And third, designing service pricing and payments mechanisms that make it more profitable on the long run to act honestly in every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable).
+Such techniques make cheating unprofitable so that the majority of rational parties will choose to follow the protocol.
 
@@
 For instance, one can pay for retrieving a file in small data chunks instead of paying for the full retrieval all at once.
-Hence, a server loses a small payment if a client does not pay after receiving a chunk.
-Similarly, a client loses a small payment if it pays in advance and the server does not send a data chunk in return.
+Hence, a service-provider loses a small payment if a client does not pay after receiving a chunk.
+Similarly, a client loses a small payment if it pays in advance and the service-provider does not send a data chunk in return.
 
@@
 The design of this puzzle follows the second category mentioned above, where solving the puzzle without doing the work is more expensive (resources-wise) than solving it after retrieving the content.
-In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a server is still storing the clients’ files with the agreed-upon number of replicas.
-Here, a detect-and-punish mechanism is used, where failing in providing a correct proof leads to slashing part of the deposit a server pledged when joining the system~\cite{filecoin}.
-Thus, the type of the provided service directly influences the delivery confirmation mechanism that need to be deployed.
+In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a service-provider is still storing the clients’ files with the agreed-upon number of replicas.
+Here, a detect-and-punish mechanism is used, where failing in providing a correct proof leads to slashing part of the deposit a service-provider pledged when joining the system~\cite{filecoin}.
+Thus, the type of the provided service directly influences the mechanisms for delivery confirmation, compensation and punishment that need to be deployed.
 \\
@@
 That is, threats that have high impact need to be prioritized over low impact ones.
-Moreover, looking into alternative cryptographic primitives that are lightweight, or optimize their implementation, while maintaining the required security guarantees is another effective venue to utilize.
+Moreover, looking into alternative cryptographic primitives that are lightweight, or optimize their implementation, while maintaining the required security guarantees is another effective avenue to utilize.
 
@@
 It speeds up the service and promotes the system’s scalability.
-This can take the form of batching requests/replies between customers and servers to reduce costs and optimize resource allocation, in addition to batch or aggregate record verification on the blockchain.
+This can take the form of batching requests/replies between customers and service-providers to reduce costs and optimize resource allocation, in addition to batch or aggregate record verification on the blockchain.
 
@@
 In this section, we elaborate on one of the important issues in distributed resource markets, namely, service delivery.
-We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the servers.
-In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming servers' activity.
+We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the service-providers.
+In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming service-providers' activity.
 We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impact the financial motivations of attackers.
@@
 documents through a public network. This network is composed of a set of semi-trusted
-re-encryption servers, or Ursulas, that implement access control policies created by data 
+re-encryption service-providers, or Ursulas, that implement access control policies created by data
 owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform
@@
 public key. This enables the latter to decrypt the ciphertext without revealing anything about the
-decryption keys or the raw data to the intermediate servers.
+decryption keys or the raw data to the intermediate service-providers.
 
@@
 pledged in the system. Therefore, the stake value influences the service load an Ursula
-may receive. This stake is also used to punish Ursula financially, by revoking part 
+may receive. This stake is also used to punish Ursula financially, by forfeiting part
 of it, if she cheats and this cheating is detected.
@@
 
-\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for the re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is inflation rewards, i.e., newly minted NU tokens, coming from the NuCypher network.
-The latter will be provided during the
-early stage of the network operation to encourage adoption. It is expected that these rewards will disappear as the token cap is reached, similar to other cryptocurrencies in the space.
+\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for the re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distribted on a schedule enforced by the NuCypher protocol.
+The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.
 
-Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round.
-Confirming the status of being online is done by calling a
-simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
+Currently, the subsidy size in each round or period are computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round.
+Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
 Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
 
-Although this approach of rewards computation and activity monitoring was enough to reach a MVP, we acknowledge that it suffers from two main problems:
+Although subsidy computation and collection based on activity monitoring is reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
 \begin{itemize}
 \setlength{\itemsep}{0pt}
-\item The rewards computation (both fees and inflation) is agnostic to the number of requests Ursula serves.
-Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or amalicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of rewards if they hold identical policies.
+\item The revenue computation (both fees and subsidies) is agnostic to the number of requests Ursula serves.
+Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
 
 \item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service.
-Ursula can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activityfunction.
-This allows Ursula to collect both inflation rewards and fees without doing any work.
-Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire).
+Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function.
+This allows Ursula to collect both subsidies and fees without doing all (or even most) of the necessary work.
+Even worse, Ursula will be able to get her stake back once it unlocks.
 \end{itemize}
 
-Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity.
-Then we need to adapt the reward computation accordingly to factor in the amount of delivered service.
+Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's minute-to-minute availability and service activity.
+Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient.
 These are introduced in the rest of this section.
@@
 \noindent{\bf Problem definition based on network operation stage.} The confirm activity problem is defined differently based on the stage of the network operation.
-In early network launch, when inflation rewards are
-still distributed, we are concerned with the availability of Ursulas and being willing to 
-serve all requests coming from Bob. In other words, regardless of the number of requests served, the rewards value (both inflation and fees) will be computed based on the period during which Ursula 
-is online and well-behaving. While in later stages, when inflation rewards disappear 
-and only fees exist, confirm activity will be tied to providing the re-encryption 
-service in the sense that the payment will be computed based on the amount of 
+In the first 5 to 8 years after launch, when subsidy rewards are
+still distributed, we are concerned with the availability of Ursulas and their willingness to
+serve all requests coming from Bob.
+In other words, regardless of the number of requests served, the revenue total (both subsidies and fees) will be computed based on the length of time in which Ursula
+is online and well-behaved. In later stages, when subsidies disappear
+and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption
+service, in the sense that the payment will be partially computed based on the amount of
 service provided. This requires Ursula to confirm its activity by proving that she served 
@@
 \noindent{\bf Confirm availability and service activity solutions.} In~\cite{confirm-activity-draft}, we introduce several solutions for both forms of the above problem.
-These solutions differ in the trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly in what follows.
+These solutions differ with respect to trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly in what follows.
 Before that, we review the adopted threat model.
@@
 
-However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically efficient, and hence, not an issue in our system.
+However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically advantageous, and hence, not an issue in our system.
 The reason is that the amount of work an Ursula does when replying to a re-encryption request is minimal.
-This means that colluding with Bob will save minimal resources, which makes this collusion case unappealing to rational Ursulas.
+This means that colluding with Bob to fake re-encryptions will save minimal resources and has no clear economic gain (such as extra subsidies), which makes this collusion case unappealing to rational Ursulas.
 This case is a great example of how traditional threat modeling and risk management practices differ from those economic-oriented ones in ruling out financially-inefficient threats.
@@
 \paragraph{Confirm availability solution.} Here we use a detect-and-punish approach embedded within an optimistic service monitoring process.
-This means that it is only invoked when Bob complains that an Ursula is unresponsiveness.
+This means that it is only invoked when Bob complains that an Ursula is unresponsive.
 In detail, for each round\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process.
@@
 This gateway mediates the service process in order to check if Bob's claim is valid.
-In other words, she challenges the working Ursula by forwarding the request again and waiting for an answer.
-If one is received, the gateway forwards it to Bob and closes the complain.
+In other words, she challenges the working Ursula by forwarding the request again and waiting for an answer (which must arrive within a specified, universal time window).
+If one is received, the gateway forwards it to Bob and closes the complaint.
 
@@
 If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submit this proof to the NuCypher staking contract.
-At that time, a part of the working Ursula stake is slashed (with a value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment.
+At that time, a part of the working Ursula stake is slashed (with a minimum value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment.
 This punishment makes cheating unprofitable, and hence, unappealing to rational working Ursulas.
@@
 
-As long as Ursula is behaving well and no valid complaints from Bob, this Ursula will collect both inflation rewards and service fees in proportion to her availability period and the number of policies she holds.
-In other words, reward computation follows the same current approach outlined earlier since our concern is to encourage adoption especially when service demand is low at the beginning.
+As long as Ursula is behaving well and no valid complaints from Bob, this Ursula will collect both subsidies and service fees in proportion to her availability period and the number of policies she holds.
+In other words, revenue computation follows the same current approach outlined earlier since our concern is to encourage adoption especially when service demand is low at the beginning.
 
@@
 
-As for the \emph{ZKP-based} solution, recall that in the NuCypher network each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}.
+As for the \emph{ZKP-based} solution, in the NuCypher network each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}.
 We can combine the proofs of all served requests within a round into one attesting to the following statement: "An Ursula has served $\omega$ distinct requests correctly" for some positive integer $\omega$ representing the number of served requests.
@@
 
+Another issue is regarding the payment computation.
+During early stages when the network launches, we anticipate a limited adoption and service demand.
+Thus, we reward Ursulas for just being online to encourage adoption.
+While in later stages, payments will be dispensed partially in proportion to the actual amount of service requests an Ursula answers.
+This is due to the fact that later on the subsidies will effectively disappear, i.e., the majority of tokens in the network will be minted, and the service fees are the only source of income.
+To incentivize Ursula to provide a correct and timely service, these fees should be computed based on the actual amount of service.
+This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
+
 \section{Conclusion}

### 2020-06-04 CESC-submission/paper.tex
test to see if line breaks show edits
Minor edits.

@@
 Usually, when obtaining digital services, we deal with traditional systems that are centrally managed.
-Most of the time, we resort to third party providers, e.g., commercial companies,  to obtain services like file storage, content distribution, computation outsourcing, and many others.
+Most of the time, we resort to third party providers, e.g.
+commercial companies, to obtain services like file storage, content distribution, outsourced computation, and many others.
 Despite being effective and widely deployed, this centrally-managed paradigm introduces several trust, cost, and transparency issues.
 It requires establishing complex business relationships with these companies, where customers usually overprovision their needs in order to handle future peak demands~\cite{Kassa13,Nicolae14}.
-Also, it constrains the customers with the service specifications these companies can offer, like the geographic coverage and service speed, not to mention the limited visibility into the real status of the system regarding its performance and the available amount of resources.
+Also, it constrains the customers with the service specifications these companies can offer, such as geographic coverage and service speed, not to mention the limited visibility into the real status of the system regarding its performance and the available resources.
 
-These issues motivated the community to revisit old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others.
-In order to encourage the collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources.
+These issues motivated the community to revisit the old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others.
+In order to encourage collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources.
 This paradigm builds flexible systems, where customers can start or stop the service at any time.
@@
 Although monetary-incentivized P2P-based systems are an old idea, especially for content sharing, most of existing solutions introduce some form of centralization or trust.
-They either rely on centralized payment services, place trust in specific parties to handle these payments and solve disputes, or even rely on some centralized entities to manage participants and defend against some security threats~\cite{Kassa13,Nair08,Zhang09}.
+They either rely on centralized payment services, place trust in specific parties to handle these payments and resolve disputes, or even rely on centralized entities to manage participants and defend against security threats~\cite{Kassa13,Nair08,Zhang09}.
 Such design choices bring us back to the central management model and the trust issues of traditional solutions.
@@
 This framework accounts for the economic aspects of this service paradigm covering both market viability (compared with traditional ones) and the impact of monetary incentives on system security (in terms of identifying financially-motivated threats and building economic or game-theoretic mitigation techniques).
-We conclude with zooming on one of the important security facets of monetary-incentivized decentralized services, namely, addressing accounting attacks, i.e., how to prove that service has been delivered, or alternatively payments are well deserved.
+We conclude with focusing on one of the important security facets of monetary-incentivized decentralized services, namely, addressing accounting attacks, i.e., how to prove that service has been delivered, or alternatively payments are well deserved.
 We elaborate on our experience in designing distributed access control services at NuCypher~\cite{nucypher} and the solutions we developed to thwart these attacks.
@@
 In this section, we discuss the main steps and challenging issues that need to be considered when designing a distributed service system.
-These steps are captured at a high level in Figure~\ref{design-steps}, which we discuss in greater details in the following paragraphs.
+These steps are captured at a high level in Figure~\ref{design-steps}, which we discuss in greater detail in the following paragraphs.
 \\
@@
 Can the system match the reliability and performance offered by these traditional solutions?
-and does providing the service require large amounts of resources that exceed the capabilities of average end-users?
+Does providing the service require large amounts of resources that exceed the capabilities of average end-users?
 Such a viability study is an important step to assess the potential for practical adoption before investing time and effort into building the system.
@@
 In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means.
-These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock collateral that is forfeited if he/she is caught cheating.
+These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock collateral that is forfeited if they are caught cheating.
 Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly.
-And third, designing service pricing and payments mechanisms that make it more profitable on the long run to act honestly in every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable).
-Such techniques make cheating unprofitable so that the majority of rational parties will choose to follow the protocol.
+And third, designing service pricing and payments mechanisms that make it more profitable in the long run to act honestly for every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable).
+Such techniques make cheating unprofitable so that the majority of rational parties will choose to adhere to the protocol.
 
@@
 In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a service-provider is still storing the clients’ files with the agreed-upon number of replicas.
-Here, a detect-and-punish mechanism is used, where failing in providing a correct proof leads to slashing part of the deposit a service-provider pledged when joining the system~\cite{filecoin}.
+Here, a detect-and-punish mechanism is used, where failure to provide a correct proof leads to slashing part of the deposit a service-provider pledged when joining the system~\cite{filecoin}.
 Thus, the type of the provided service directly influences the mechanisms for delivery confirmation, compensation and punishment that need to be deployed.
@@
 It speeds up the service and promotes the system’s scalability.
-This can take the form of batching requests/replies between customers and service-providers to reduce costs and optimize resource allocation, in addition to batch or aggregate record verification on the blockchain.
+This can take the form of batching requests/replies between customers and service-providers to reduce costs and optimize resource allocation, in addition to batching or aggregating record verification on the blockchain.
 
@@
 \noindent{\bf An overview of the NuCypher network.} The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management
-system, encryption, and access control service. It uses proxy re-encryption, namely, the
+system, encryption, and access control service. It uses threshold proxy re-encryption, namely, the
 Umbral scheme~\cite{umbral2018}, to delegate access to encrypted
@@
 re-encryption service-providers, or Ursulas, that implement access control policies created by data
-owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform
+owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing a quorum of Ursulas to transform
 ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
@@
 may receive. This stake is also used to punish Ursula financially, by forfeiting part
-of it, if she cheats and this cheating is detected.
+of it for detectable malfeasance.
 
-Alice joins the network by creating a policy to be implemented by a 
+Alice uses the network by creating a policy to be implemented by a
 set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
@@
 
-\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for the re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distribted on a schedule enforced by the NuCypher protocol.
+\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distributed on a schedule enforced by the NuCypher protocol.
 The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.
 
-Currently, the subsidy size in each round or period are computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round.
+Currently, the subsidy size in each round or period is computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round.
 Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
@@
 If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submit this proof to the NuCypher staking contract.
-At that time, a part of the working Ursula stake is slashed (with a minimum value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment.
-This punishment makes cheating unprofitable, and hence, unappealing to rational working Ursulas.
+At that time, a portion of the Ursula's stake is slashed (with a minimum value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment.
+This punishment makes cheating unprofitable, and hence, unappealing to rational Ursulas.
 A detailed technical version of this solution is available in~\cite{confirm-activity-draft}.
@@
 Thus, we reward Ursulas for just being online to encourage adoption.
-While in later stages, payments will be dispensed partially in proportion to the actual amount of service requests an Ursula answers.
+While in later stages, payments will be dispensed partially in proportion to the actual number of service requests an Ursula answers.
 This is due to the fact that later on the subsidies will effectively disappear, i.e., the majority of tokens in the network will be minted, and the service fees are the only source of income.
@@
 Our work puts forward a generic framework for designing efficient and secure resource markets.
-It also examines in a greater depth how financial incentives affect security measures deployment and system design choices.
+It also examines in greater depth how financial incentives affect security measures and system design choices.
 

### 2020-06-08 CESC-submission/paper.tex
include arj/derek/ravial's comments/edits

@@
 We present a generic framework for building distributed service markets by utilizing these new technologies.
-We also discuss the security and efficiency challenges, with a focus on how the economic considerations impact system design and threat mitigation, and conclude with some potential solutions.
+We also discuss the security and efficiency challenges, with a focus on how the economic considerations impact system design and threat mitigation, along with some potential solutions.
 \end{abstract}
@@
 \section{Introduction}
-Usually, when obtaining digital services, we deal with traditional systems that are centrally managed.
-Most of the time, we resort to third party providers, e.g.
-commercial companies, to obtain services like file storage, content distribution, outsourced computation, and many others.
+When obtaining digital services, usually we deal with traditional systems that are centrally managed.
+Most of the time, we resort to third party providers, e.g., commercial companies,  to obtain services like file storage, content distribution, computation outsourcing, and many others.
 Despite being effective and widely deployed, this centrally-managed paradigm introduces several trust, cost, and transparency issues.
 It requires establishing complex business relationships with these companies, where customers usually overprovision their needs in order to handle future peak demands~\cite{Kassa13,Nicolae14}.
-Also, it constrains the customers with the service specifications these companies can offer, such as geographic coverage and service speed, not to mention the limited visibility into the real status of the system regarding its performance and the available resources.
+Also, it constrains the customers with the service specifications these companies can offer, such as geographic coverage and service speed, not to mention the limited visibility into the real status of the system regarding its performance and the available amount of resources.
 
 These issues motivated the community to revisit the old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others.
-In order to encourage collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources.
-This paradigm builds flexible systems, where customers can start or stop the service at any time.
-It also scales more easily with demand and extends the network coverage because peers from anywhere can join.
+In order to encourage collaborative work and compliance with the protocol, payments are provided in return; this creates a market for trading resources.
+This paradigm builds flexible systems, scales more easily with demand, and extends the network coverage since peers from anywhere can join.
 Furthermore, this paradigm builds transparent and equitable ecosystems in which participants can negotiate service terms and price directly instead of having a few entities monopolizing the market.
@@
 \label{service-examples}
-%\vspace{-10 pt}
+\vspace{6 pt}
 \centering 
@@
 Although monetary-incentivized P2P-based systems are an old idea, especially for content sharing, most of existing solutions introduce some form of centralization or trust.
-They either rely on centralized payment services, place trust in specific parties to handle these payments and resolve disputes, or even rely on centralized entities to manage participants and defend against security threats~\cite{Kassa13,Nair08,Zhang09}.
+They either rely on centralized payment services, place trust in specific parties to handle these payments and resolve disputes, or even rely on some centralized entities to manage participants and defend against some security threats~\cite{Kassa13,Nair08,Zhang09}.
 Such design choices bring us back to the central management model and the trust issues of traditional solutions.
@@
 
-To address these issues, in this talk we present a generic framework for designing secure, scalable, and equitable resource markets to provide services in a fully distributed way.
+To address these issues, we present a generic framework for designing secure, scalable, and equitable resource markets to provide services in a fully distributed way.
 This framework accounts for the economic aspects of this service paradigm covering both market viability (compared with traditional ones) and the impact of monetary incentives on system security (in terms of identifying financially-motivated threats and building economic or game-theoretic mitigation techniques).
-We conclude with focusing on one of the important security facets of monetary-incentivized decentralized services, namely, addressing accounting attacks, i.e., how to prove that service has been delivered, or alternatively payments are well deserved.
+We conclude with focusing on one of the important security facets of monetary-incentivized decentralized services - namely, addressing accounting attacks, i.e., how to prove that service has been delivered, or alternatively payments are well deserved.
 We elaborate on our experience in designing distributed access control services at NuCypher~\cite{nucypher} and the solutions we developed to thwart these attacks.
@@
 \section{Distributed Resource Markets Design}
-One of the effective ideas for building fully decentralized and equitable services is to build distributed markets to trade resources.
+One effective idea for building fully decentralized and equitable services is to build distributed markets to trade resources.
 That is, implement a protocol that allows anyone to join to serve others and collect payments in return.
@@
 \noindent{\bf Viability Assessment.} Before looking into building a distributed resource market, one has to assess its viability.
-This includes studying the demand side (who is interested in the service) and the supply side (who can provide it) to answer several questions; Are there tangible advantages to encourage replacing traditional solutions with fully distributed ones?
+This includes studying the demand side (who is interested in the service) and the supply side (who can provide it) to answer several questions; are there tangible advantages to encourage replacing traditional solutions with fully distributed ones?
 Can the system match the reliability and performance offered by these traditional solutions?
@@
 Such a model can guide designers in deploying the proper countermeasures, and evaluating the security level of a system.
-For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion or sybil attack.
+For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion or Sybil attacks.
 
@@
 ABC enables building comprehensive threat models by holistically analyzing the threat space while managing its complexity, and distilling the impactful cases that need to be neutralized to secure the system.
-It also allows classifying threats based on their mitigation techniques, i.e., threats that can be addressed cryptographically or algorithmically, and these that require game theoretic means, thus providing insights about the proper measures to deploy.
+It also allows for classifying threats based on their mitigation techniques, i.e., threats that can be addressed cryptographically or algorithmically, and these that require game theoretic means, thus providing insights about the proper measures to deploy.
 
-It should be noted that the threat modeling steps need to be revisited each time the system design is altered.
+It should be noted that the threat modeling step need to be revisited each time the system design is altered.
 Furthermore, it should be performed as the last step before shipping the system to argue formally about its security.
@@
 
-Furthermore, accounting attacks, in which participants collude with each other pretending that the service has been delivered, could be a hammer that may destroy the market.
+Furthermore, accounting attacks, in which participants collude with each other, pretending that the service has been delivered, could be a hammer that destroys the market.
 This is a particular problem in systems that require sponsoring service requests.
 For example, in content distribution, a publisher (e.g., Netflix) can hire caches to distribute content to its clients, and hence, it pays for the service.
-In this case, caches (or service-providers in general) and clients may collude so that clients pretend to be served, allowing service-providers to collect payments from the sponsor for free.
+In this case, caches (or servers in general) and clients may collude so that clients pretend to be served, allowing servers to collect payments from the sponsor for free.
 
@@
 Such a protocol represents the backbone of the resource market; if it fails the whole market fails.
-Service-providers will not be willing to participate if they are not being paid, and same for customers, they will not be willing to use the system if they pay for a service that they do not receive.
-Operating the market also requires devising mechanisms for service pricing, term negotiation for service-provider recruiting, and matching protocols to match these service-providers with interested customers.
+Servers will not be willing to participate if they are not being paid.
+The same is true for customers; they will not be willing to use the system if they pay for a service that they do not receive.
+Operating the market also requires devising mechanisms for service pricing, term negotiation for server recruiting, and matching protocols to match these servers with interested customers.
 \\
 
+\vspace{-4pt}
 \noindent{\bf Financial and Cryptographic Security Measures.} Usually, security threats are mitigated by using cryptographic means (e.g., encryption and digital signatures), or algorithmic approaches (e.g., ordering the actions in a way that enforces secure behavior).
@@
 In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means.
-These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock collateral that is forfeited if they are caught cheating.
+These fall into three categories.
+First, detect-and-punish mechanisms, where any participant is required to lock a collateral that is forfeited if they are caught cheating.
 Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly.
-And third, designing service pricing and payments mechanisms that make it more profitable in the long run to act honestly for every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable).
-Such techniques make cheating unprofitable so that the majority of rational parties will choose to adhere to the protocol.
+And third, designing service pricing and payments mechanisms that make it more profitable on the long run to act honestly in every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable).
+Such techniques make cheating unprofitable so that rational parties will choose to adhere to the protocol.
 
@@
 For instance, one can pay for retrieving a file in small data chunks instead of paying for the full retrieval all at once.
-Hence, a service-provider loses a small payment if a client does not pay after receiving a chunk.
+Hence, a server loses a small payment if a client does not pay after receiving a chunk.
 Similarly, a client loses a small payment if it pays in advance and the service-provider does not send a data chunk in return.
@@
 The design of this puzzle follows the second category mentioned above, where solving the puzzle without doing the work is more expensive (resources-wise) than solving it after retrieving the content.
-In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a service-provider is still storing the clients’ files with the agreed-upon number of replicas.
-Here, a detect-and-punish mechanism is used, where failure to provide a correct proof leads to slashing part of the deposit a service-provider pledged when joining the system~\cite{filecoin}.
-Thus, the type of the provided service directly influences the mechanisms for delivery confirmation, compensation and punishment that need to be deployed.
+In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a server is still storing the clients’ files with the agreed-upon number of replicas.
+Here, a detect-and-punish mechanism is used, where failure to provide a correct proof leads to slashing part of the deposit a server pledged when joining the system~\cite{filecoin}.
+Thus, the type of the provided service directly influences the delivery confirmation mechanism that need to be deployed.
 \\
@@
 
+\vspace{-4pt}
 \noindent{\bf Testing and Deployment.} To examine the viability of the system, conventional practices of prototyping, benchmarking, and controlled deployment can be used to evaluate both efficiency and resistance to attacks.
@@
 \section{Impact of Financial Incentives on Service Delivery}
-\vspace{-4pt}
 In this section, we elaborate on one of the important issues in distributed resource markets, namely, service delivery.
 We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the service-providers.
-In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming service-providers' activity.
-We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impact the financial motivations of attackers.
-Such an issue is a great example of how cryptocurrency-based services introduce new economic aspects that may evolve over time, which need to be reflected on the system design.
+In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming servers' activity.
+We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impacts the financial motivations of attackers.
 \\
@@
 
-\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distributed on a schedule enforced by the NuCypher protocol.
+\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distribted on a schedule enforced by the NuCypher protocol.
 The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.
@@
 
-Although subsidy computation and collection based on activity monitoring is reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
+Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
 \begin{itemize}
 \setlength{\itemsep}{0pt}
-\item The revenue computation (both fees and subsidies) is agnostic to the number of requests Ursula serves.
+\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves.
 Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
@@
 Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function.
-This allows Ursula to collect both subsidies and fees without doing all (or even most) of the necessary work.
+This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work.
 Even worse, Ursula will be able to get her stake back once it unlocks.
@@
 
-Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's minute-to-minute availability and service activity.
+Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity.
 Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient.
-These are introduced in the rest of this section.
+We introduce these topics in the remainder of the section.
 \\
@@
 serve all requests coming from Bob.
-In other words, regardless of the number of requests served, the revenue total (both subsidies and fees) will be computed based on the length of time in which Ursula
+In other words, regardless of the number of requests served, the revenue total value (both subsidy and fees) will be computed based on the length of time during which Ursula
 is online and well-behaved. In later stages, when subsidies disappear 
@@
 \noindent{\bf Confirm availability and service activity solutions.} In~\cite{confirm-activity-draft}, we introduce several solutions for both forms of the above problem.
-These solutions differ with respect to trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly in what follows.
+These solutions differ with respect to trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly below.
 Before that, we review the adopted threat model.
@@
 
-However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically advantageous, and hence, not an issue in our system.
+However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically efficient, and hence, not an issue in our system.
 The reason is that the amount of work an Ursula does when replying to a re-encryption request is minimal.
@@
 This means that it is only invoked when Bob complains that an Ursula is unresponsive.
-In detail, for each round\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process.
+In detail, for each round,\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process.
 Then map each hash to an Ursula index as found in the list of working Ursulas recorded on the blockchain within the StakeEscrow smart contract of NuCypher.
@@
 On the other hand, meaning no response is received, the gateway notifies the rest of gateways selected for that round to repeat the same process.
-If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submit this proof to the NuCypher staking contract.
+If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submits this proof to the NuCypher staking contract.
 At that time, a portion of the Ursula's stake is slashed (with a minimum value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment.
@@
 
-As for the \emph{ZKP-based} solution, in the NuCypher network each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}.
-We can combine the proofs of all served requests within a round into one attesting to the following statement: "An Ursula has served $\omega$ distinct requests correctly" for some positive integer $\omega$ representing the number of served requests.
+For the \emph{ZKP-based} solution, in the NuCypher network, each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}.
+We can combine the proofs of all served requests within a round into one attesting to the following statement: \emph{``An Ursula has served $\omega$ distinct requests correctly"} for some positive integer $\omega$ representing the number of served requests.
 This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.
 
-An alternative, possibly more efficient approach is to view the statement "An Ursula has served $\omega$ distinct requests correctly" as an instance of the arithmetic circuit satisfiability problem and utilize bulletproofs\footnote{Bulletproofs are a highly efficient ZKP system that does not require any trusted setup.} to prove its correctness in zero knowledge~\cite{bunz18}.
+An alternative, possibly more efficient approach, is to view the statement \emph{``An Ursula has served $\omega$ distinct requests correctly"} as an instance of the arithmetic circuit satisfiability problem and utilize bulletproofs\footnote{Bulletproofs are a highly efficient ZKP system that does not require any trusted setup.} to prove its correctness in zero knowledge~\cite{bunz18}.
 That is, build a circuit that takes the set of correctness proofs of the served requests as well as their number $\omega$ as inputs, and then output 0 if number of correct distinct proofs equals to $\omega$.
@@
 Ursula constructs a Merkle hash tree of all served requests and their correctness proofs in a round.
-Then, it uses the root as a random beacon to be fed into an iterative hash process to select $n$ leaf nodes at random to open them (i.e., these are the challenges).
+Then, she uses the root as a random beacon to be fed into an iterative hash process to select $n$ leaf nodes at random to open them (i.e., these are the challenges).
 Ursula signs the Merkle tree root, provides the challenge leaf nodes along with their membership paths to either a sidechain (which is maintained by round-selected committee) or to the policy contract to verify.
-As noted, the security provided here is statistical in the sense that we need to bound the probability by which an Ursula can cheat, like for example she may replicate requests in the tree and add fabricated ones to increase $\omega$.
+As noted, the security provided here is statistical in the sense that we need to bound the probability by which an Ursula can cheat, such as replicating requests in the tree and adding fabricated ones to increase $\omega$.
 
@@
 
-Another issue is regarding the payment computation.
-During early stages when the network launches, we anticipate a limited adoption and service demand.
+Another issue pertains to the payment computation.
+During early stages when the network launches, we anticipate  limited adoption and service demand.
 Thus, we reward Ursulas for just being online to encourage adoption.
@@
 While centrally-managed systems provide reliable services, they introduce trust, cost, and transparency issues.
-This motivated developing non-traditional peer-assisted models to create distributed resource markets that are open to anyone to join and serve others while collecting payments in return.
+This has motivated developing non-traditional peer-assisted models to create distributed resource markets that are open to anyone to join and serve others while collecting payments in return.
 However, such a paradigm comes with security and performance challenges that need to be addressed before having any practical deployment.

### 2020-06-08 CESC-submission/paper.tex
add figure for PCD solution

@@
 This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.
+Figure~\ref{pcd-based-sol} for a high level diagram describing this solution (here $x_i$ is the $i^{th}$ request coming from Bob, $cFarg_i$ is the fragment of the transformed ciphertext (the reply for the re-encryption service request), $\pi_i$ is the correctness proof for handling this request, and $\hat{\pi}_i$ is the aggregated proof covering all proofs for requests $1, \dots, i$.
+
+\begin{figure}[t!]
+\centerline{
+\includegraphics[height= 0.7in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
+\caption{PCD/IVC-based solution diagram. Ursula starts a round in the idle state. When 
+the first request arrives, Ursula responds to the request and starts composing the 
+proofs as new requests arrive. At the end of the round, Ursula announces the number of 
+served requests and a single proof attesting to its claim to the network. }
+\label{pcd-based-sol}
+\end{figure}
 

### 2020-06-18 confirm-activity/tex/intro.tex
sync intro with CESC submission

--- 2020-05-05 tex/intro.tex
@@
 \label{intro}
-The NuCypher network~\cite{egorov2017nucypher} is a decentralized key management 
-system, encryption, and access control service. It uses proxy re-encryption, namely, the 
+The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management 
+system, encryption, and access control service. It uses threshold proxy re-encryption, namely, the 
 Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
 documents through a public network. This network is composed of a set of semi-trusted 
-re-encryption servers, or Ursulas, that implement access control policies created by data 
-owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
+re-encryption service-providers, or Ursulas, that implement access control policies created by data 
+owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing a quorum of Ursulas to transform 
 ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
 public key. This enables the latter to decrypt the ciphertext without revealing anything about the
-decryption keys or the raw data to the intermediate servers.
+decryption keys or the raw data to the intermediate service-providers.
 
@@
 and the monetary incentives paid to provide the service. In order to join the 
-system, Ursula needs to stake an amount of NU tokens for a specific period
+system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
 which will be released when the pre-specified staking period is over. Alice chooses an
 Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
-pledged in the system. Therefore, the stake value influences the amount of service load an Ursula
-may receive. This stake is also used to punish Ursula financially, by revoking part 
-of it, if she cheats and this cheating is detected.
+pledged in the system. Therefore, the stake value influences the service load an Ursula
+may receive. This stake is also used to punish Ursula financially, by forfeiting part 
+of it for detectable malfeasance.
 
-Alice joins the network by creating a policy to be implemented by a 
+Alice uses the network by creating a policy to be implemented by a 
 set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
@@
 is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
-Alice will lock an amount of Ether into the policy to be used to pay Ursulas for the re-encryption 
+Alice will lock an amount of Ether into the policy contract to be used to pay Ursulas for the re-encryption 
 service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
@@
 
-Bob, on the other hand, does not deal with currency in the system. It interacts with the storage 
+Bob, on the other hand, does not deal with currency in the system at all. He interacts with the storage 
 network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
@@
 \subsection{Monetary Incentives in the NuCypher Network}
-Ursulas are rewarded for the re-encryption service by using two sources; 
-the first is the service fees collected from the policy  
-owner Alice, while the second is inflation rewards, i.e., newly minted
-NU tokens, coming from the NuCypher network. The latter will be provided during the 
-early stage of the network operation to encourage 
-adoption. It is expected that these rewards will disappear as the token cap is 
-reached, similar to other cryptocurrencies in the space.
+Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distributed on a schedule enforced by the NuCypher protocol.
+The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.
 
-Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round.
-Confirming the status of being online is done by calling a
-simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
-
-As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
+Currently, the subsidy size in each round or period is computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round.
+Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
+Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
 
 \subsection{Problems with Current Reward Computation Approach}
-The current approach of computing Ursula's inflation rewards and service fees suffers from two
-main problems:
+Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
 \begin{itemize}
 \setlength{\itemsep}{0pt}
-\item The rewards computation (both fees and inflation) is agnostic to the number of 
-requests Ursula serves. Thus, an active Ursula who may serve a huge number of 
-re-encryption requests, and one who does not receive any requests (or a
-malicious/lazy Ursula that does not answer Bob's requests), will 
-both collect the same amount of rewards if they hold identical policies.
+\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves.
+Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
 
-\item Confirming being online is flawed in the sense that this function does 
-not require any input or proofs from Ursula on providing the service. Ursula 
-can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activity
-function. This allows Ursula to collect both inflation rewards 
-and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire). 
+\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service.
+Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function.
+This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work.
+Even worse, Ursula will be able to get her stake back once it unlocks.
 \end{itemize}
 
+Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity.
+Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient.
+We introduce these topics in the remainder of the section.
+
 \subsection{Problem Statement}
-The confirm activity problem is defined differently based on the stage of the 
-NuCypher network. In early network operation, when inflation rewards are 
-still distributed, we are concerned with the availability of Ursulas and being willing to 
-serve all requests coming from Bob. In other words, regardless of the number of 
-requests served, the rewards value will be computed based on the period during which Ursula 
-is online and well-behaving. While in later stages, when inflation rewards disappear 
-and only fees exist, confirm activity will be tied to providing the re-encryption 
-service in the sense that the payment will be computed based on the amount of 
-service provided. Thus, Ursula needs to confirm its activity by proving that she served 
+The confirm activity problem is defined differently based on the stage of the network operation. In the first 5 to 8 years after launch, when subsidy rewards are 
+still distributed, we are concerned with the availability of Ursulas and their willingness to 
+serve all requests coming from Bob.
+In other words, regardless of the number of requests served, the revenue total value (both subsidy and fees) will be computed based on the length of time during which Ursula
+is online and well-behaved. In later stages, when subsidies disappear 
+and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption 
+service, in the sense that the payment will be partially computed based on the amount of 
+service provided. This requires Ursula to confirm its activity by proving that she served 
 a given number of distinct re-encryption requests during a given period. To make the distinction 
-clear, we refer to the first as confirm availability, and for the second as confirm 
-service activity.
+clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
+service activity}.
 

### 2020-08-03 confirm-activity/tex/abstract.tex
edit abstract

@@
 \begin{abstract}
-In this document we introduce several aspects related to the confirm activity problem in 
-the NuCypher network. These include the different definitions of this problem, the 
-underlying threat model, the current adopted solution, and its relation 
-to both service fees and inflation rewards. In particular, we consider two flavors of the confirm activity issue, namely, confirm availability 
-and confirm service activity. The former confirms that Ursula is available all the time 
-and replies to all requests coming from Bob, while the latter provides a proof that an 
-Ursula has served a specific number of distinct re-encryption 
-requests within a given a period. We present potential solutions 
-for each of these flavors and discuss at 
-what stage of the network operation they are likely to be used.
+In this document we study the confirm activity problem in the NuCypher network.
+This problem is concerned with devising secure techniques that allow Ursula to prove being online and responsive during any time period.
+We consider two flavors of the problem based on the network operation stage, namely, confirm availability and confirm service activity.
+The former is about confirming that Ursula is available all the time and replies to all Bob requests, while the latter is about proving that an Ursula has served a specific number of distinct re-encryption requests within a given period.
+We present several potential solutions for each of these types, discuss the characteristics of these solutions with respect to their security guarantees and efficiency, and provide recommendations to when each of them should be used.
 \end{abstract}

### 2020-08-03 confirm-activity/tex/confirm-service-activity.tex
fix intro and reorganize the paper

--- 2020-05-06 tex/confirm-service-activity.tex
@@
 
-The rest of this section provides an overview of the underlying cryptographic primitives and 
-protocols, after which it discusses the proposed solutions along with an analysis of 
+The rest of this section discusses the proposed solutions along with an analysis of 
 their security and efficiency aspects. Lastly, the section concludes with directions of 
 future work on the confirm service activity issue.
-
-\subsection{Preliminaries}
-\label{prelim}
-This section provides an overview of two concepts that we use in the 
-proposed solutions. These include the framework of proof carrying data (PCD) 
-and the collective signing (CoSi) protocol.
-
-\subsubsection{Proof Carrying Data (PCD).}
-The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
-computation involving untrusted parties. It produces a single proof for the output 
-that attests not only the correctness of the final result, but also 
-the correctness of the entire history of intermediate computations that produced 
-this result. Correctness here is defined as a polynomially computable predicate that 
-abstracts the properties, or invariants, that must be satisfied.
-
-\begin{figure}[h!]
-\centerline{
-\includegraphics[height= 1.3in, width = 1.0\columnwidth]{figures/pcd-diagram.pdf}}
-\caption{An example of a PCD application. A distributed computation involving parties $P_i$, for 
-$i \in \{1, \dots, 6\}$, each 
-of which has a local input $x_i$ and produces an output $y_i$ with a proof $\pi_i$. }
-\label{pcd-diagram}
-\end{figure}
-
-To clarify how PDC works, consider a distributed computation task that involves 
-the set of parties shown in Figure~\ref{pcd-diagram}. Party $P_1$ starts the computation with its 
-own input, produces an intermediate output with a proof saying that it performed 
-the computation as defined by the protocol. It then sends both the output and the proof 
-to the next party, which is $P_2$ in this case. Here, $P_2$ will 
-have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) 
-as input to the computation it will perform. Similarly, $P_2$ will produce another 
-intermediate output and a proof. This proof not only attests to the correctness of the 
-computation done by $P_2$, but also the history that lead to the result $y_2$. In other 
-words, it implicitly includes 
-the proof from $P_1$. The same process continues until the full computation is finished. 
-Anyone can verify the correctness or compliance of the whole distributed protocol by 
-only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.
-
-As shown, PCDs enable untrusted parties to work with each other in a fully distributed 
-fashion, without overwhelming the system with the storage and verification of individual 
-proofs for each step of the performed protocol. Also, they attest to correctness or compliance  
-to the prescribed protocol without re-executing any of the intermediate computations. Thus, 
-they provide a promising paradigm for confirming service activity in a compact way.
-
-\subsubsection{Collective Signing (CoSi).}
-\label{cosi}
-CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
-statement together in a way that produces a single signature. As such, both the 
-verification time and the space requirements are just like having a single signer. The 
-difference is that this signature attests that all parties agree with the signed 
-statement instead of only one.
-
-CoSi builds upon Schnorr 
-multisignatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines 
-them with communication trees to speed up the signing process in 
-case of a large number of cosigners. In what follows, we only present the protocol
-with a plain communication architecture as it suffices for the confirm service activity 
-solution introduced in this document.
-
-Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and 
-generator $g$, such that the discrete log is believed to be hard in this group. 
-Take $n$ parties that want to sign a statement together. 
-Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key 
-$pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$. To sign a message $m$, 
-one of these parties, let's say $P_1$, coordinates the signing process as follows: 
-\begin{enumerate}
-\setlength{\itemsep}{0pt}
-\item $P_1$ prepares a message $m$ and sends it to the rest of the signers.
-
-\item Each party $P_i$, possibly after verifying 
-$m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and compute $V_i = g^{\tau_i}$, 
-then it sends $V_i$ back to $P_1$.
-
-\item $P_1$ aggregates all random values received from 
-the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.
-
-\item $P_1$ then computes 
-$c = H(V||m)$, where $H$ is an appropriate hash function. $P_1$ then 
-sends $c$ to the rest of the parties.
-
-\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and 
-sends it to $P_1$.
-
-\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the 
-collective signature over $m$ as $(c, r)$.
-\end{enumerate}
-
-Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with 
-one difference. An aggregated public key $pk$ is used in the verification process, 
-which is computed as $pk = \Pi_{i=1}^{n} pk_i$.
-
-The work in~\cite{syta2016keeping} tackles several issues related to 
-the availability of the 
-signing parties, and optimizing the communication between them. 
-We believe that such techniques can be used in the NuCypher network if we adopt the 
-CoSi-based solution for the confirm service activity issue.
 
@@
 hand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.
-
-\subsection{Discussion and Analysis}
-\label{analysis}
-Here we will discuss the security, financial, and performance implications of the 
-proposed solutions to choose the best. This will be delayed until we crystallize the 
-details of each of the solutions.
-
-\subsection{Future Work}
-\label{future-work}
-Most of the future work on the confirm service activity issue 
-will be dedicated to construct a concrete PCD-based solution. This 
-includes the following:
-\begin{itemize}
-\item Understand PCD and its applications in a greater depth. This 
-also requires exploring NIZK in general and SNARKs in specific.
-
-\item Define an efficient output correctness predicate that characterizes 
-the correctness of the statement that PCD will attest for. This could be 
-hard for the confirm activity issue as the value of the output is dynamic 
-based on the workload Ursula may receive.
-
-\item Define a way to compose the proofs efficiently and produce 
-a single proof at the end. This will be tied to the formulated predicate.
-
-\item Argue about the correctness and security of the concrete scheme.
-\end{itemize}

### 2020-08-03 confirm-activity/tex/discussion.tex
fix intro and reorganize the paper

--- 2020-06-08 CESC-submission/paper.tex
@@
-\documentclass{llncs}
-\pdfoutput=1
-
-\usepackage{algorithm, algpseudocode}
-\renewcommand{\algorithmiccomment}[1]{/*#1*/}
-\usepackage{epsfig, endnotes, url, color, graphicx}
-\usepackage{mathtools, amsmath, amsfonts}
-\usepackage{diagbox, booktabs, colortbl}
-\usepackage{breakurl, listings, framed}
-\usepackage{multirow, caption, subcaption}
-\usepackage[hidelinks]{hyperref}
-\usepackage{xspace, slashbox, enumitem, bm}
-\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
-
-\pagestyle{plain}
-
-\captionsetup[subfigure]{justification=raggedright}
-
-\captionsetup{compatibility=false}
-\def\UrlBreaks{\do\/\do-}
-{\renewcommand{\arraystretch}{1.2}
-\makeatletter
-\newcommand{\@chapapp}{\relax}%
-\makeatother
-
-\usepackage[title]{appendix}
-
-\newcommand{\tabitem}{~~\llap{\textbullet}~~}
-
-\newcommand{\ignore}[1]{}
-\newcommand\ghada[1]{\nbc{GA}{#1}{blue}}
-\newcommand{\fake}[1]{{\color{magenta} [fake: #1]}}
-
-\input{annotations}
-
-% Ghada: added to remove running headers
-\pagestyle{plain}
-
-\begin{document}
-%
-% paper title
-\title{\Large \bf Rethinking Service Systems: \\
-A Path Towards Secure and Equitable Resource Markets
-}
-
-\author{Ghada Almashaqbeh} 
-%
-\authorrunning{G. Almashaqbeh}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{NuCypher \\
-\email{ghada@nucypher.com}}
-
-\maketitle
-
-\begin{abstract}
-Escalating demand for digital services has motivated building non-traditional solutions to reduce costs and achieve a greater level of flexibility.
-Among these solutions, peer-assisted models are gaining more popularity in replacing infrastructure-based (possibly) centralized approaches.
-Cryptocurrencies have strengthened this trend by providing a fully distributed mechanism to compensate service provision, and their blockchains and consensus protocols offer a trustless and publicly verifiable way to govern the system.
-We present a generic framework for building distributed service markets by utilizing these new technologies.
-We also discuss the security and efficiency challenges, with a focus on how the economic considerations impact system design and threat mitigation, along with some potential solutions.
-\end{abstract}
-
-\section{Introduction}
-When obtaining digital services, usually we deal with traditional systems that are centrally managed.
-Most of the time, we resort to third party providers, e.g., commercial companies,  to obtain services like file storage, content distribution, computation outsourcing, and many others.
-Despite being effective and widely deployed, this centrally-managed paradigm introduces several trust, cost, and transparency issues.
-It requires establishing complex business relationships with these companies, where customers usually overprovision their needs in order to handle future peak demands~\cite{Kassa13,Nicolae14}.
-Also, it constrains the customers with the service specifications these companies can offer, such as geographic coverage and service speed, not to mention the limited visibility into the real status of the system regarding its performance and the available amount of resources.
-
-These issues motivated the community to revisit the old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others.
-In order to encourage collaborative work and compliance with the protocol, payments are provided in return; this creates a market for trading resources.
-This paradigm builds flexible systems, scales more easily with demand, and extends the network coverage since peers from anywhere can join.
-Furthermore, this paradigm builds transparent and equitable ecosystems in which participants can negotiate service terms and price directly instead of having a few entities monopolizing the market.
-
-\begin{table}[t!]
-\caption{Examples of centrally-managed digital services and their counterparts of P2P-based ones.} 
-\label{service-examples}
-\vspace{6 pt}
-\centering 
-\begin{tabular}{| p{0.32\columnwidth}  | p{0.32\columnwidth} | p{0.32\columnwidth} |}\hline\hline
-
-{\bf Service Type} & {\bf Traditional Solution} & {\bf P2P-based Solution}  \\[0.5ex] \hline \hline
-
-Payments & Banks & Bitcoin  \\[0.5ex] \hline
-
-File storage & Dropbox~\cite{dropbox} &  Filecoin~\cite{filecoin}  \\ [0.5ex]  \hline
-
-Content distribution & Akamai~\cite{akamai} & CacheCash~\cite{almashaqbeh2019cachecash}  \\ [0.5ex]  \hline
-
-Key management system & Azure Key Vault~\cite{azure} & NuCypher~\cite{nucypher}  \\ [0.5ex]  \hline
-
-\end{tabular}
-\end{table}
-
-Although monetary-incentivized P2P-based systems are an old idea, especially for content sharing, most of existing solutions introduce some form of centralization or trust.
-They either rely on centralized payment services, place trust in specific parties to handle these payments and resolve disputes, or even rely on some centralized entities to manage participants and defend against some security threats~\cite{Kassa13,Nair08,Zhang09}.
-Such design choices bring us back to the central management model and the trust issues of traditional solutions.
-
-The evolution of cryptocurrencies and blockchain technology~\cite{bitcoin,ethereum} has provided templates for reshaping large-scale distributed systems and services.
-Cryptocurrencies implement a decentralized virtual currency exchange medium that permits participants to be rewarded without any pre-authentication or identification requirements.
-And their underlying blockchains and consensus protocols support public verifiability, auditing, and decentralized governance without needing to place trust in any entity.
-These features can be exploited in P2P-based schemes to manage and pay for the correct service without driving the system toward centralization (see Table~\ref{service-examples} for examples of traditional service solutions and their P2P counterparts).
-
-However, the open access environment of P2P networks (i.e., allowing anyone to join and dealing with untrusted participants) introduces several security and performance challenges that need to be addressed before having any practical deployment.
-In addition, having monetary incentives motivates attackers to attack the system in novel ways to maximize their financial profits.
-Thus, traditional practices of secure systems design need to be modified and expanded to account for such factors.
-
-To address these issues, we present a generic framework for designing secure, scalable, and equitable resource markets to provide services in a fully distributed way.
-This framework accounts for the economic aspects of this service paradigm covering both market viability (compared with traditional ones) and the impact of monetary incentives on system security (in terms of identifying financially-motivated threats and building economic or game-theoretic mitigation techniques).
-We conclude with focusing on one of the important security facets of monetary-incentivized decentralized services - namely, addressing accounting attacks, i.e., how to prove that service has been delivered, or alternatively payments are well deserved.
-We elaborate on our experience in designing distributed access control services at NuCypher~\cite{nucypher} and the solutions we developed to thwart these attacks.
-We also show how the financial motivations of attackers vary based on the operation stage of the network (early launch vs.
-long term operation) and how threat mitigation techniques vary accordingly.
-
-\section{Distributed Resource Markets Design}
-One effective idea for building fully decentralized and equitable services is to build distributed markets to trade resources.
-That is, implement a protocol that allows anyone to join to serve others and collect payments in return.
-Such an approach needs to solve several challenges introduced by the open access and decentralized work environment.
-In other words, dealing with untrusted, possibly financially motivated participants requires deploying additional measures that may impact efficiency, usability, and compatibility with existing infrastructures.
-Consequently, there is a need for carefully-tailored threat mitigation techniques and efficiency optimization mechanisms in order to promote the adoption of these systems.
-
-\begin{figure}[ht!]
-\centerline{
-\includegraphics[height= 1.2in, width = 1.0\columnwidth]{figures/design-steps.pdf}}
-\caption{Design process of distributed resource markets.} \label{design-steps}
-\vspace{-12pt}
-\end{figure}
-
-In this section, we discuss the main steps and challenging issues that need to be considered when designing a distributed service system.
-These steps are captured at a high level in Figure~\ref{design-steps}, which we discuss in greater detail in the following paragraphs.
-\\
-
-\noindent{\bf Viability Assessment.} Before looking into building a distributed resource market, one has to assess its viability.
-This includes studying the demand side (who is interested in the service) and the supply side (who can provide it) to answer several questions; are there tangible advantages to encourage replacing traditional solutions with fully distributed ones?
-Can the system match the reliability and performance offered by these traditional solutions?
-Does providing the service require large amounts of resources that exceed the capabilities of average end-users?
-Such a viability study is an important step to assess the potential for practical adoption before investing time and effort into building the system.
-\\
-
-\noindent{\bf Threat Modeling.} Despite the many advantages they offer — decentralization, transparency, and lowered service costs — there is still a big gap between the promise of P2P-based systems and their performance in practice.
-Adding monetary incentives, by using another P2P-based payment service, i.e., cryptocurrencies, widens this gap.
-This is due to the perception that these systems are not secure, where the recent large number of security breaches give credence to these doubts~\cite{benebit-scam,binance-hack,bitcoin-cash-hack,bitcoingold-double-spending,exchange-hack-b,bitfloor-hack,korea-exchange-hack,eth-hack,ico-hack-b,exchange-hack,enigma-hack,mine-hack}.
-
-The best practice for designing a secure system requires a threat modeling step to investigate potential security risks.
-Such a model can guide designers in deploying the proper countermeasures, and evaluating the security level of a system.
-For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion or Sybil attacks.
-
-This observation encouraged the community to visit old threat modeling frameworks and adapt them to address these issues.
-For example, the ABC framework~\cite{Almashaqbeh19} was designed to achieve these goals by accounting for both the underlying cryptocurrency medium and the service provided on top of it.
-ABC enables building comprehensive threat models by holistically analyzing the threat space while managing its complexity, and distilling the impactful cases that need to be neutralized to secure the system.
-It also allows for classifying threats based on their mitigation techniques, i.e., threats that can be addressed cryptographically or algorithmically, and these that require game theoretic means, thus providing insights about the proper measures to deploy.
-
-It should be noted that the threat modeling step need to be revisited each time the system design is altered.
-Furthermore, it should be performed as the last step before shipping the system to argue formally about its security.
-\\
-
-\noindent{\bf Unique Aspects of Operating a Distributed Market.} The open access work environment helps to create flexible services and transparent ecosystems.
-However, this comes at a cost.
-Dealing with untrusted parties means that fair exchange is impossible~\cite{Even80,Pagnia99}, which raises the question of when to pay service-providers - before or after providing the service?
-If paid first, a malicious service-provider may not serve the customer, and if served first, a malicious customer may not pay afterwards.
-
-Furthermore, accounting attacks, in which participants collude with each other, pretending that the service has been delivered, could be a hammer that destroys the market.
-This is a particular problem in systems that require sponsoring service requests.
-For example, in content distribution, a publisher (e.g., Netflix) can hire caches to distribute content to its clients, and hence, it pays for the service.
-In this case, caches (or servers in general) and clients may collude so that clients pretend to be served, allowing servers to collect payments from the sponsor for free.
-
-The above security issues (an many others depending on the service type) require a careful design of a decentralized service-payment exchange protocol that can reduce the risks of dealing with untrusted, possibly colluding parties.
-Such a protocol represents the backbone of the resource market; if it fails the whole market fails.
-Servers will not be willing to participate if they are not being paid.
-The same is true for customers; they will not be willing to use the system if they pay for a service that they do not receive.
-Operating the market also requires devising mechanisms for service pricing, term negotiation for server recruiting, and matching protocols to match these servers with interested customers.
-\\
-
-\vspace{-4pt}
-\noindent{\bf Financial and Cryptographic Security Measures.} Usually, security threats are mitigated by using cryptographic means (e.g., encryption and digital signatures), or algorithmic approaches (e.g., ordering the actions in a way that enforces secure behavior).
-Monetary-incentivized systems introduce new types of attacks that cannot be addressed using conventional approaches.
-In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means.
-These fall into three categories.
-First, detect-and-punish mechanisms, where any participant is required to lock a collateral that is forfeited if they are caught cheating.
-Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly.
-And third, designing service pricing and payments mechanisms that make it more profitable on the long run to act honestly in every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable).
-Such techniques make cheating unprofitable so that rational parties will choose to adhere to the protocol.
-
-For example, to reduce the risks of the impossibility of fair exchange, micropayments can be employed.
-That is, instead of paying a large chunk of money for the full service, the payment is divided into small values, each of which is exchanged for a small service amount.
-For instance, one can pay for retrieving a file in small data chunks instead of paying for the full retrieval all at once.
-Hence, a server loses a small payment if a client does not pay after receiving a chunk.
-Similarly, a client loses a small payment if it pays in advance and the service-provider does not send a data chunk in return.
-
-On the other hand, to thwart accounting attacks, system designers need to incorporate suitable techniques to prove or confirm resource expenditure, and consequently, confirm that payments are well deserved.
-In online content delivery, for example, the CAPnet puzzle~\cite{Almashaqbeh19b} can be used to ensure that caches have delivered the requested content.
-The design of this puzzle follows the second category mentioned above, where solving the puzzle without doing the work is more expensive (resources-wise) than solving it after retrieving the content.
-In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a server is still storing the clients’ files with the agreed-upon number of replicas.
-Here, a detect-and-punish mechanism is used, where failure to provide a correct proof leads to slashing part of the deposit a server pledged when joining the system~\cite{filecoin}.
-Thus, the type of the provided service directly influences the delivery confirmation mechanism that need to be deployed.
-\\
-
-\noindent{\bf Optimize for Efficiency.} Although designing a secure system is the ultimate goal, efficiency is an important driving factor of practical adoption and deployment.
-System designers need to exploit any opportunity that allows for optimizing performance.
-This also involves choosing the right trade-off between security and efficiency in the sense of risk management.
-That is, threats that have high impact need to be prioritized over low impact ones.
-Moreover, looking into alternative cryptographic primitives that are lightweight, or optimize their implementation, while maintaining the required security guarantees is another effective avenue to utilize.
-
-Furthermore, reducing interaction between participants is beneficial.
-It speeds up the service and promotes the system’s scalability.
-This can take the form of batching requests/replies between customers and service-providers to reduce costs and optimize resource allocation, in addition to batching or aggregating record verification on the blockchain.
-
-Another important aspect is related to handling micropayments.
-Micropayments create a scalability problem as they produce a huge number of transactions that overwhelm the system and require large processing fees.
-Here, probabilistic schemes are useful in aggregating the small transactions into few larger ones before processing~\cite{Wheeler96,Rivest97}.
-In particular, payments take the form of lottery tickets, and only winning tickets are processed in the system with values that compensate properly for the tickets exchanged so far.
-Several fully-distributed micropayment schemes exist in the literature~\cite{Pass15,Chiesa17,Almashaqbeh20} that provide trade-offs between efficiency, anonymity, and security guarantees.
-\\
-
-\vspace{-4pt}
-\noindent{\bf Testing and Deployment.} To examine the viability of the system, conventional practices of prototyping, benchmarking, and controlled deployment can be used to evaluate both efficiency and resistance to attacks.
-These provide a starting point to attract early adopters and test the system at a large scale.
-This stage may inspire designers to revisit specific parts of the system for further optimization based on the results of the conducted experiments, or feedback from the community based on a testnet deployment for example.
-Testing and improving also continue beyond the testing stage, i.e., after public launch, but deploying protocol modifications could be harder especially if they result in hard forks or community division.
-
-\section{Impact of Financial Incentives on Service Delivery}
-In this section, we elaborate on one of the important issues in distributed resource markets, namely, service delivery.
-We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the service-providers.
-In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming servers' activity.
-We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impacts the financial motivations of attackers.
-\\
-
-\noindent{\bf An overview of the NuCypher network.} The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management 
-system, encryption, and access control service. It uses threshold proxy re-encryption, namely, the 
-Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
-documents through a public network. This network is composed of a set of semi-trusted 
-re-encryption service-providers, or Ursulas, that implement access control policies created by data 
-owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing a quorum of Ursulas to transform 
-ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
-public key. This enables the latter to decrypt the ciphertext without revealing anything about the
-decryption keys or the raw data to the intermediate service-providers.
-
-Joining the NuCypher network is governed by consensus rules defining the service setup
-and the monetary incentives paid to provide the service. In order to join the 
-system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
-which will be released when the pre-specified staking period is over. Alice chooses an
-Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
-pledged in the system. Therefore, the stake value influences the service load an Ursula
-may receive. This stake is also used to punish Ursula financially, by forfeiting part 
-of it for detectable malfeasance.
-
-Alice uses the network by creating a policy to be implemented by a 
-set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
-need to answer requests coming from Bob(s), as well as the duration of the policy, which 
-is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
-Alice will lock an amount of Ether into the policy contract to be used to pay Ursulas for the re-encryption 
-service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
-wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
-NuCypher rules of preparing access control policies.
-
-Bob, on the other hand, does not deal with currency in the system at all. He interacts with the storage 
-network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
-re-encryption service. \\
-
-\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distribted on a schedule enforced by the NuCypher protocol.
-The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.
-
-Currently, the subsidy size in each round or period is computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round.
-Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
-Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
-
-Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
-\begin{itemize}
-\setlength{\itemsep}{0pt}
-\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves.
-Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
-
-\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service.
-Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function.
-This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work.
-Even worse, Ursula will be able to get her stake back once it unlocks.
-\end{itemize}
-
-Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity.
-Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient.
-We introduce these topics in the remainder of the section.
-\\
-
-\noindent{\bf Problem definition based on network operation stage.} The confirm activity problem is defined differently based on the stage of the network operation.
-In the first 5 to 8 years after launch, when subsidy rewards are
-still distributed, we are concerned with the availability of Ursulas and their willingness to 
-serve all requests coming from Bob.
-In other words, regardless of the number of requests served, the revenue total value (both subsidy and fees) will be computed based on the length of time during which Ursula
-is online and well-behaved. In later stages, when subsidies disappear 
-and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption 
-service, in the sense that the payment will be partially computed based on the amount of 
-service provided. This requires Ursula to confirm its activity by proving that she served 
-a given number of distinct re-encryption requests during a given period. To make the distinction 
-clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
-service activity}. \\
-
-\noindent{\bf Confirm availability and service activity solutions.} In~\cite{confirm-activity-draft}, we introduce several solutions for both forms of the above problem.
-These solutions differ with respect to trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly below.
-Before that, we review the adopted threat model.
-
-\paragraph{Threat model.} We do not place trust in any party and we assume that all participants are rational and self-interested.
-Thus, they may follow the protocol or deviate from it, either acting on their own or in collusion with each other, based solely on what maximizes their utility gain.
-
-However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically efficient, and hence, not an issue in our system.
-The reason is that the amount of work an Ursula does when replying to a re-encryption request is minimal.
-This means that colluding with Bob to fake re-encryptions will save minimal resources and has no clear economic gain (such as extra subsidies), which makes this collusion case unappealing to rational Ursulas.
-This case is a great example of how traditional threat modeling and risk management practices differ from those economic-oriented ones in ruling out financially-inefficient threats.
-
-Moreover, we assume that when sampling a subset of Ursulas in the network, at least one of them is honest.
-This assumption can be achieved by having a global assumption regarding the lower bound of the number of
-honest Ursulas with respect to the total number of Ursulas in the system.\footnote{Or it can be achieved by deploying a special entity like an external verifier, that changes on a periodic basis, or one by the NuCypher company, that is trusted to faithfully participate as a member of each sampled set.
-This verifier does not provide any other services in the system.}
-
-\paragraph{Confirm availability solution.} Here we use a detect-and-punish approach embedded within an optimistic service monitoring process.
-This means that it is only invoked when Bob complains that an Ursula is unresponsive.
-In detail, for each round,\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process.
-Then map each hash to an Ursula index as found in the list of working Ursulas recorded on the blockchain within the StakeEscrow smart contract of NuCypher.
-This process is repeated until a set of distinct Ursulas is selected.
-Note that anyone can perform this process and verify its outcome.} Bob proceeds as usual by contacting the list of working Ursulas received from Alice for the re-encryption service.
-If a working Ursula does not reply, Bob complains to a gateway Ursula and hands her the request.
-This gateway mediates the service process in order to check if Bob's claim is valid.
-In other words, she challenges the working Ursula by forwarding the request again and waiting for an answer (which must arrive within a specified, universal time window).
-If one is received, the gateway forwards it to Bob and closes the complaint.
-
-On the other hand, meaning no response is received, the gateway notifies the rest of gateways selected for that round to repeat the same process.
-If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submits this proof to the NuCypher staking contract.
-At that time, a portion of the Ursula's stake is slashed (with a minimum value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment.
-This punishment makes cheating unprofitable, and hence, unappealing to rational Ursulas.
-A detailed technical version of this solution is available in~\cite{confirm-activity-draft}.
-
-As long as Ursula is behaving well and no valid complaints from Bob, this Ursula will collect both subsidies and service fees in proportion to her availability period and the number of policies she holds.
-In other words, revenue computation follows the same current approach outlined earlier since our concern is to encourage adoption especially when service demand is low at the beginning.
-
-\paragraph{Confirm service activity solutions.} Here we have three solutions that differ in their security assumptions and efficiency.
-We refer to them as zero knowledge proof-based (ZKP-based), committee-attestation, and commit/challenge/open-based.
-Again, we provide a high level description in what follows while a more complete version can be found in~\cite{confirm-activity-draft}.
-
-For the \emph{ZKP-based} solution, in the NuCypher network, each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}.
-We can combine the proofs of all served requests within a round into one attesting to the following statement: \emph{``An Ursula has served $\omega$ distinct requests correctly"} for some positive integer $\omega$ representing the number of served requests.
-This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.
-
-An alternative, possibly more efficient approach, is to view the statement \emph{``An Ursula has served $\omega$ distinct requests correctly"} as an instance of the arithmetic circuit satisfiability problem and utilize bulletproofs\footnote{Bulletproofs are a highly efficient ZKP system that does not require any trusted setup.} to prove its correctness in zero knowledge~\cite{bunz18}.
-That is, build a circuit that takes the set of correctness proofs of the served requests as well as their number $\omega$ as inputs, and then output 0 if number of correct distinct proofs equals to $\omega$.
-Then, invoke a circuit parser to convert the circuit into the bulletproof format, which allow the prover, Ursula in this case, to produce a single proof.
-Then, Ursula submits the proof to the service policy contract.
-Once the proof is verified, the contract disperses the service fee (in proportion to $\omega$) from Alice's escrow to Ursula's account.
-
-As for the \emph{committee-attestation} approach, it also relies on electing a committee of Ursulas (and possibly outsider verifiers as mentioned previously) to attest for the work load an Ursula served.
-That is, a working Ursula sends all Bob requests she served along with the correctness proofs to this committee.
-After verifying all the proofs, the committee collectively signs a statement as above which is submitted to the policy contract so Ursula can claim her payment.
-
-Lastly, we have a \emph{commit/challenge/open} approach, which is inspired from the Merkle tree-based ZKP system proposed in~\cite{dottling19}.
-Ursula constructs a Merkle hash tree of all served requests and their correctness proofs in a round.
-Then, she uses the root as a random beacon to be fed into an iterative hash process to select $n$ leaf nodes at random to open them (i.e., these are the challenges).
-Ursula signs the Merkle tree root, provides the challenge leaf nodes along with their membership paths to either a sidechain (which is maintained by round-selected committee) or to the policy contract to verify.
-As noted, the security provided here is statistical in the sense that we need to bound the probability by which an Ursula can cheat, such as replicating requests in the tree and adding fabricated ones to increase $\omega$.
-
-\paragraph{Discussion.} Which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network.
+\section{Discussion and Analysis}
+\label{discussion}
+Which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network.
 The ZKP-based solution (the one utilizing bulletproofs) provides several advantages including non-interactivity (as opposed to the committee-attestation one that needs interaction with the committee).
@@
 This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
-
-\section{Conclusion}
-While centrally-managed systems provide reliable services, they introduce trust, cost, and transparency issues.
-This has motivated developing non-traditional peer-assisted models to create distributed resource markets that are open to anyone to join and serve others while collecting payments in return.
-However, such a paradigm comes with security and performance challenges that need to be addressed before having any practical deployment.
-Our work puts forward a generic framework for designing efficient and secure resource markets.
-It also examines in greater depth how financial incentives affect security measures and system design choices.
-
-{\footnotesize \bibliographystyle{acm}\vspace{-6pt}
-
-\bibliography{marketBib}}
-
-\normalsize
-
-% that's all folks
-\end{document}

### 2020-08-03 confirm-activity/tex/intro.tex
fix intro and reorganize the paper

@@
 \label{intro}
-The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management 
-system, encryption, and access control service. It uses threshold proxy re-encryption, namely, the 
-Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
-documents through a public network. This network is composed of a set of semi-trusted 
-re-encryption service-providers, or Ursulas, that implement access control policies created by data 
+The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management system, encryption, and access control service.
+It uses threshold proxy re-encryption, namely, the Umbral scheme~\cite{umbral2018}, to delegate access to encrypted data through a public network.
+This network is composed of semi-trusted re-encryption service-providers, or Ursulas, that implement access control policies created by data
 owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing a quorum of Ursulas to transform 
-ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
-public key. This enables the latter to decrypt the ciphertext without revealing anything about the
-decryption keys or the raw data to the intermediate service-providers.
+ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's, public key.
+This enables the latter to decrypt the ciphertext without revealing anything about the decryption keys or the raw data to the intermediate service-providers.
 
-Joining the NuCypher network is governed by consensus rules defining the service setup
-and the monetary incentives paid to provide the service. In order to join the 
-system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
-which will be released when the pre-specified staking period is over. Alice chooses an
-Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
-pledged in the system. Therefore, the stake value influences the service load an Ursula
-may receive. This stake is also used to punish Ursula financially, by forfeiting part 
-of it for detectable malfeasance.
+Joining the NuCypher network is governed by consensus rules defining the service setup and the monetary incentives paid to provide the service.
+In order to join the system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period which will be released when the pre-specified staking period is over.
+Alice chooses an Ursula to hold an access control policy with a probability proportional to the stake this Ursula pledged in the system.
+Therefore, the stake value influences the service load an Ursula may receive.
+This stake is also used to punish Ursula financially, by forfeiting part of it for detectable malfeasance.
 
-Alice uses the network by creating a policy to be implemented by a 
-set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
-need to answer requests coming from Bob(s), as well as the duration of the policy, which 
-is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
-Alice will lock an amount of Ether into the policy contract to be used to pay Ursulas for the re-encryption 
-service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
-wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
-NuCypher rules of preparing access control policies.
+Alice uses the network by creating an access control policy to be implemented by a set of Ursulas.
+This policy specifies the re-encryption key fragments each Ursula will need to answer requests coming from Bob(s), as well as the duration of the policy, which is basically the timeframe during which Bob is authorized to access Alice's data.
+Furthermore, the policy contract requires Alice to lock an amount of Ether that will be used by the network to pay Ursulas for providing the re-encryption service.
+As noted, Alice is not exposed to the NU token.
+All that she needs is an Ethereum wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the NuCypher rules with respect to preparing access control policies.
 
-Bob, on the other hand, does not deal with currency in the system at all. He interacts with the storage 
-network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
-re-encryption service.
+Bob, on the other hand, does not deal with currency in the system at all.
+He interacts with the storage network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the re-encryption service after which he will be able to access the raw data of interest.
 
-\subsection{Monetary Incentives in the NuCypher Network}
+\paragraph{\bf Rewards and activity monitoring in the NuCypher network.}
 Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distributed on a schedule enforced by the NuCypher protocol.
-The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.
+The latter will be provided during the early stage of the network operation to encourage Ursula's participation and sustain their operations in lieu of a mature fee market.
 
@@
 Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
-Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
+Similarly, for service fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
 
-\subsection{Problems with Current Reward Computation Approach}
-Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
+\paragraph{\bf Motivation.} Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
 \begin{itemize}
@@
 
-\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service.
-Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function.
+\item Confirming being online is flawed in the sense that the function call that Ursula makes does not require any input or proofs on providing the service, or even being online and responsive.
+Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call this function.
 This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work.
@@
 Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient.
-We introduce these topics in the remainder of the section.
 
-\subsection{Problem Statement}
-The confirm activity problem is defined differently based on the stage of the network operation. In the first 5 to 8 years after launch, when subsidy rewards are 
-still distributed, we are concerned with the availability of Ursulas and their willingness to 
-serve all requests coming from Bob.
-In other words, regardless of the number of requests served, the revenue total value (both subsidy and fees) will be computed based on the length of time during which Ursula
-is online and well-behaved. In later stages, when subsidies disappear 
-and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption 
-service, in the sense that the payment will be partially computed based on the amount of 
-service provided. This requires Ursula to confirm its activity by proving that she served 
-a given number of distinct re-encryption requests during a given period. To make the distinction 
-clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
-service activity}.
+\paragraph{\bf Problem statement.}
+The confirm activity problem is defined differently based on the network operation stage.
+In the first 5 to 8 years after launch, when subsidy rewards are still distributed, we are concerned with the availability of Ursulas and their willingness to serve all requests coming from Bob.
+In other words, regardless of the number of requests served, the revenue total value (both subsidy and fees) will be computed based on the length of time during which Ursula is online and well-behaved.
 
-In this document, we introduce several solutions for both forms of confirming activity. 
-These solutions differ in the trust, efficiency, interactivity, and resource 
-requirements, in addition to their security guarantees. We divide the document into 
-two parts, the first is about confirm availability, while the second is about confirm 
-service activity. We begin with outlining the adopted threat model for each problem 
-definition, as well as the network model. Then, we present the proposed solutions, discuss the aforementioned
-trade-offs and requirements of each of them, with the goal of selecting one of these 
-solutions to be adopted for each stage of the NuCypher network operation.
+On the other hand, in later stages, when subsidies disappear and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption service, in the sense that the payment will be partially computed based on the amount of service provided.
+This requires Ursula to confirm its activity by proving that she served a given number of distinct re-encryption requests during a given period.
 
-\subsection{Threat and Network Models}
-\label{threat-network-model}
-This section describes a modification for the network model of NuCypher 
-required by the proposed solutions, in 
-addition to the threat model adopted in this work.
+To make the distinction clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm service activity}.
 
-\subsubsection{Network Model.}
-In order for the proposed solutions to work, we need to ensure freshness, 
-integrity, and authenticity of the requests (as well as service complaints as we will see later) issued by Bob. This can be achieved 
-by requiring Bob to sign each re-encryption request it issues and to include a timestamp, or 
-sequence number, in each request to ensure freshness. The keypair used for the 
-signature should be separate from the keypair Bob uses for proxy encryption in the 
-system.
+\paragraph{\bf Contributions.}
+In this document, we introduce several solutions for both forms of confirming activity. These solutions differ in the trust, security guarantees, interactivity, and efficiency.
 
-Until now we assume that Alice pays for the service by using the Ether she locks 
-in the policy contract. Other arrangement may emerge in the system like having 
-Bob pay for each requests he issues. Such an arrangement and its implication on the 
-confirm activity issue will be studied once it becomes part of the NuCypher 
-network protocol.
+For confirming availability, we employ a detect-and-punish approach embedded within an optimistic service monitoring process.
+This means that it is only invoked when Bob complains that an Ursula is unresponsive.
+The proposed solution labels Ursulas as working and gateway Ursulas.
+The former are contacted in a regular way to handle the re-encryption service, while the latter act as challengers that are contacted only when there is a complaint from Bob so they will attest whether a working Ursula is indeed unavailable.
+If that is the case, a quorum of gateways (who have challenged the working Ursula and found her unresponsive) will collectively sign a proof-of-unavailability that will cost the misbehaving working Ursula part of her stake.
+We discuss several aspects related to gateway selection and a variety of potential attacks on this approach along with mitigation techniques.
 
-\subsubsection{Threat Model.}
-In our threat model, we make the following set of assumptions:
-\begin{itemize}
-\item {\bf Self-interested parties:} We do not place trust in any party and we assume that all participants are 
-self-interested. This means that a party may decide to 
-follow the protocol or deviate from it, either on its own or by colluding 
-with other attackers, and such decision is solely based on what maximizes the financial profits
-of this party.
+For confirming service activity, we devise three solutions that allow producing a proof attesting to the statement \emph{``An Ursula has served $\omega$ distinct requests correctly"} for some positive integer $\omega$ representing the number of served requests.
+These solutions are refereed to as zero knowledge proof-based (ZKP-based), committee-attestation, and commit/challenge/open-based.
 
-\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out  
-its own Alice and/or Bob or collude with Alice. We do not consider collusion 
-between Bob and Ursula as a practical threat. This means that cases of Bob pretending  
-that he got service from Ursula (while no service is delivered) is not an issue. We do not 
-suspect this will be of any importance and there is no motivation to do it given that 
-the work Ursula does for re-encryption is minimal.
+For the \emph{ZKP-based} approach, we utilize the fact that in our network each Ursula already produces a ZKP attesting to the correctness of each re-encryption request she performs~\cite{umbral2018}.
+Our solution is to aggregate the proofs of all served requests within a round into one proof attesting to the above statement.
+This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.
+An alternative, possibly more efficient approach, is to view the above statement as an instance of arithmetic circuit satisfiability problem and combine it a highly efficient ZKP system, e.g.,~\cite{bunz18}.
+That is, build a circuit that takes the set of correctness proofs and their count $\omega$ as inputs.
+If the number of correct distinct proofs equals to $\omega$, i.e., the circuit output 1,  then a valid proof will be produced.
+Ursula can submit this proof to the network to claim her payments.
 
-The above non-collusion assumption does not affect the solutions proposed to handle 
-the confirm service activity discussed in Section~\ref{confirm-service-activity}. This 
-means that these solutions provide higher 
-security guarantees and address the issue of potential collusion between Bob and Ursula. 
-It could be the case that relaxing the requirement of 
-addressing this collusion case allows deploying more efficient solutions. 
-In order to make an educated decision of the plausibility of this threat, we need 
-more data about the system operation and the behavior of the participants 
-once the inflation rewards disappears in the system. Therefore, we leave this 
-issue until later when fees become the only source of rewards for Ursulas.
+As for the \emph{committee-attestation} approach, it shares a similar theme to confirm availability solution mentioned previously.
+For each round, a committee of Ursulas (and possibly outsider verifiers) is elected to attest for the work load an Ursula served.
+In detail, the working Ursula sends all Bob requests she served along with the correctness proofs to this committee.
+After verifying all the proofs, the committee collectively signs the \emph{``An Ursula has served $\omega$ distinct requests correctly"} statement, while replacing $\omega$ with the actual number of served requests.
+The committee (or the working Ursula) submits the signed statement to the network so the working Ursula can claim her payments.
 
-\item {\bf Honest Ursulas:} We also assume that when sampling a subset of Ursulas in the network, 
-at least one of them is honest. This assumption can be achieved by 
-having a global assumption regarding the lower bound of the number of 
-honest Ursulas with respect to the total number of Ursulas in the system. 
-(Or it can be achieved by deploying a special entity like an external verifier, 
-that changes on a periodic basis, or one by the NuCypher company, that is
-trusted to faithfully participate as a member of each samples set. This 
-verifier does not provide any other services 
-in the system.)
-\end{itemize}
+For the \emph{commit/challenge/open} approach, we introduce a mechanism inspired from the Merkle tree-based ZKP system proposed in~\cite{dottling19}.
+For each round a working Ursula constructs a Merkle hash tree of all served requests and their correctness proofs.
+Then, she uses the root as a random beacon to be fed into an iterative hash process to select $n$ leaf nodes at random to open them (i.e., these are the challenges).
+Ursula signs the Merkle tree root and the activity proof will be composed of the signed root, the challenge leaf nodes along with their openings, and membership paths of the challenge leaves.
+Ursula sends this proof to either a sidechain (maintained by round-selected committee) or to the main network to verify.
+Once verified, Ursula will be rewarded with the service payment.
 
-Other than the above, we have usual assumptions like dealing with 
-computationally bounded adversaries 
-that cannot break secure cryptographic primitives with non-negligible probability. 
-(We may need to work in the random oracle model, but this depends on the 
-security requirements of the proposed solutions.)
+Lastly, we discuss the trade-offs of each of these solutions in terms of security guarantees, assumptions, and efficiency.
+We also outline some recommendations regarding which solution should be used at what stage of the network operation.
+
+\paragraph{\bf Organization.}
+We begin with outlining the adopted threat and network model, in Section~\ref{threat-network-model}, followed by an overview of some of the cryptographic primitives that we use in Section~\ref{prelim}.
+Then, we present the proposed solutions for confirm availability in Section~\ref{confirm-availability} and those for confirming service activity in Section~\ref{confirm-service-activity}.
+After that, we briefly discuss the trade-offs and requirements of each of these solutions along with some usage recommendations in Section~\ref{discussion}.
+Lastly, in Section~\ref{future-work} we conclude with highlighting some of our future work directions.

### 2020-08-03 confirm-activity/tex/prelim.tex
fix intro and reorganize the paper

--- 2020-03-11 tex/prelim.tex
@@
 \label{prelim}
-This section provides an overview of two concepts that we use in the 
-proposed solutions. These include the framework of proof carrying data (PCD) 
-and the collective signing (CoSi) protocol.
+This section provides an overview of two concepts that we use in the proposed solutions. These include the framework of proof carrying data (PCD) and the collective signing (CoSi) protocol.
 
-\subsection{Proof Carrying Data (PCD)}
-The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
-computation involving untrusted parties. It produces a single proof for the output 
-that attests not only the correctness of the final result, but also 
-the correctness of the entire history of intermediate computations that produced 
-this result. Correctness here is defined as a polynomially computable predicate that 
-abstracts the properties, or invariants, that must be satisfied.
+\subsection{Proof Carrying Data (PCD).}
+The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed computation involving untrusted parties.
+It produces a single proof for the output that attests not only the correctness of the final result, but also the correctness of the entire history of intermediate computations that produced this result.
+Correctness here is defined as a polynomially computable predicate that abstracts the properties, or invariants, that must be satisfied.
 
@@
 
-To clarify how PDC works, consider a distributed computation task that involves 
-the set of parties shown in Figure~\ref{pcd-diagram}. Party $P_1$ starts the computation with its 
-own input, produces an intermediate output with a proof saying that it performed 
-the computation as defined by the protocol. It then sends both the output and the proof 
-to the next party, which is $P_2$ in this case. Here, $P_2$ will 
-have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) 
-as input to the computation it will perform. Similarly, $P_2$ will produce another 
-intermediate output and a proof. This proof not only attests to the correctness of the 
-computation done by $P_2$, but also the history that lead to the result $y_2$. In other 
-words, it implicitly includes 
-the proof from $P_1$. The same process continues until the full computation is finished. 
-Anyone can verify the correctness or compliance of the whole distributed protocol by 
-only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.
+To clarify how PDC works, consider a distributed computation task that involves the set of parties shown in Figure~\ref{pcd-diagram}.
+Party $P_1$ starts the computation with its own input, produces an intermediate output with a proof saying that it performed the computation as defined by the protocol.
+It then sends both the output and the proof to the next party, which is $P_2$ in this case.
+Here, $P_2$ will have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) as input to the computation it will perform.
+Similarly, $P_2$ will produce another intermediate output and a proof.
+This proof not only attests to the correctness of the computation done by $P_2$, but also the history that lead to the result $y_2$.
+In other
+words, it implicitly includes the proof from $P_1$.
+The same process continues until the full computation is finished.
+Anyone can verify the correctness or compliance of the whole distributed protocol by only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.
 
-As shown, PCDs enable untrusted parties to work with each other in a fully distributed 
-fashion, without overwhelming the system with the storage and verification of individual 
-proofs for each step of the performed protocol. Also, they attest to correctness or compliance  
-to the prescribed protocol without re-executing any of the intermediate computations. Thus, 
-they provide a promising paradigm for confirming service activity in a compact way.
+As shown, PCDs enable untrusted parties to work with each other in a fully distributed fashion, without overwhelming the system with the storage and verification of individual proofs for each step of the performed protocol.
+Also, they attest to correctness or compliance  to the prescribed protocol without re-executing any of the intermediate computations.
+Thus, they provide a promising paradigm for confirming service activity in a compact way.
 
-\subsection{Collective Signing (CoSi)}
+\subsection{Collective Signing (CoSi).}
 \label{cosi}
-CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
-statement together in a way that produces a single signature. As such, both the 
-verification time and the space requirements are just like having a single signer. The 
-difference is that this signature attests that all parties agree with the signed 
+CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a statement together in a way that produces a single signature.
+As such, both the verification time and the space requirements are just like having a single signer.
+The difference is that this signature attests that all parties agree with the signed
 statement instead of only one.
 
-CoSi builds upon Schnorr 
-multisignatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines 
-them with communication trees to speed up the signing process in 
-case of a large number of cosigners. In what follows, we only present the protocol
-with a plain communication architecture as it suffices for the confirm service activity 
-solution introduced in this document.
+CoSi builds upon Schnorr multisignatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines them with communication trees to speed up the signing process in case of a large number of cosigners.
+In what follows, we only present the protocol with a plain communication architecture as it suffices for the confirm service activity solution introduced in this document.
 
-Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and 
-generator $g$, such that the discrete log is believed to be hard in this group. 
+Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and generator $g$, such that the discrete log is believed to be hard in this group.
 Take $n$ parties that want to sign a statement together.
-Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key 
-$pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$. To sign a message $m$, 
-one of these parties, let's say $P_1$, coordinates the signing process as follows: 
+Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key $pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$.
+To sign a message $m$, one of these parties, let's say $P_1$, coordinates the signing process as follows:
 \begin{enumerate}
@@
 
-\item Each party $P_i$, possibly after verifying 
-$m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and compute $V_i = g^{\tau_i}$, 
-then it sends $V_i$ back to $P_1$.
+\item Each party $P_i$, possibly after verifying $m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and compute $V_i = g^{\tau_i}$, then it sends $V_i$ back to $P_1$.
 
-\item $P_1$ aggregates all random values received from 
-the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.
+\item $P_1$ aggregates all random values received from the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.
 
-\item $P_1$ then computes 
-$c = H(V||m)$, where $H$ is an appropriate hash function. $P_1$ then 
-sends $c$ to the rest of the parties.
+\item $P_1$ then computes $c = H(V||m)$, where $H$ is an appropriate hash function. $P_1$ then sends $c$ to the rest of the parties.
 
-\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and 
-sends it to $P_1$.
+\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and sends it to $P_1$.
 
-\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the 
-collective signature over $m$ as $(c, r)$.
+\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the collective signature over $m$ as $(c, r)$.
 \end{enumerate}
 
-Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with 
-one difference. An aggregated public key $pk$ is used in the verification process, 
-which is computed as $pk = \Pi_{i=1}^{n} pk_i$.
+Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with one difference.
+An aggregated public key $pk$ is used in the verification process, which is computed as $pk = \Pi_{i=1}^{n} pk_i$.
 
-The work in~\cite{syta2016keeping} tackles several issues related to 
-the availability of the 
-signing parties, and optimizing the communication between them. 
-We believe that such techniques can be used in the NuCypher network if we adopt the 
-CoSi-based solution for the confirm service activity issue.
+The work in~\cite{syta2016keeping} tackles several issues related to the availability of the signing parties, and optimizing the communication between them.
+We believe that such techniques can be used in the NuCypher network if we adopt the CoSi-based solution for the confirm service activity issue.

### 2020-08-03 confirm-activity/tex/threat-model.tex
fix intro and reorganize the paper

--- 2020-05-05 tex/intro.tex
@@
-\section{Introduction}
-\label{intro}
-The NuCypher network~\cite{egorov2017nucypher} is a decentralized key management 
-system, encryption, and access control service. It uses proxy re-encryption, namely, the 
-Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
-documents through a public network. This network is composed of a set of semi-trusted 
-re-encryption servers, or Ursulas, that implement access control policies created by data 
-owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
-ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
-public key. This enables the latter to decrypt the ciphertext without revealing anything about the
-decryption keys or the raw data to the intermediate servers.
-
-Joining the NuCypher network is governed by consensus rules defining the service setup
-and the monetary incentives paid to provide the service. In order to join the 
-system, Ursula needs to stake an amount of NU tokens for a specific period
-which will be released when the pre-specified staking period is over. Alice chooses an
-Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
-pledged in the system. Therefore, the stake value influences the amount of service load an Ursula
-may receive. This stake is also used to punish Ursula financially, by revoking part 
-of it, if she cheats and this cheating is detected.
-
-Alice joins the network by creating a policy to be implemented by a 
-set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
-need to answer requests coming from Bob(s), as well as the duration of the policy, which 
-is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
-Alice will lock an amount of Ether into the policy to be used to pay Ursulas for the re-encryption 
-service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
-wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
-NuCypher rules of preparing access control policies.
-
-Bob, on the other hand, does not deal with currency in the system. It interacts with the storage 
-network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
-re-encryption service.
-
-\subsection{Monetary Incentives in the NuCypher Network}
-Ursulas are rewarded for the re-encryption service by using two sources; 
-the first is the service fees collected from the policy  
-owner Alice, while the second is inflation rewards, i.e., newly minted
-NU tokens, coming from the NuCypher network. The latter will be provided during the 
-early stage of the network operation to encourage 
-adoption. It is expected that these rewards will disappear as the token cap is 
-reached, similar to other cryptocurrencies in the space.
-
-Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round.
-Confirming the status of being online is done by calling a
-simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.
-
-As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.
-
-\subsection{Problems with Current Reward Computation Approach}
-The current approach of computing Ursula's inflation rewards and service fees suffers from two
-main problems:
-\begin{itemize}
-\setlength{\itemsep}{0pt}
-\item The rewards computation (both fees and inflation) is agnostic to the number of 
-requests Ursula serves. Thus, an active Ursula who may serve a huge number of 
-re-encryption requests, and one who does not receive any requests (or a
-malicious/lazy Ursula that does not answer Bob's requests), will 
-both collect the same amount of rewards if they hold identical policies.
-
-\item Confirming being online is flawed in the sense that this function does 
-not require any input or proofs from Ursula on providing the service. Ursula 
-can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activity
-function. This allows Ursula to collect both inflation rewards 
-and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire). 
-\end{itemize}
-
-\subsection{Problem Statement}
-The confirm activity problem is defined differently based on the stage of the 
-NuCypher network. In early network operation, when inflation rewards are 
-still distributed, we are concerned with the availability of Ursulas and being willing to 
-serve all requests coming from Bob. In other words, regardless of the number of 
-requests served, the rewards value will be computed based on the period during which Ursula 
-is online and well-behaving. While in later stages, when inflation rewards disappear 
-and only fees exist, confirm activity will be tied to providing the re-encryption 
-service in the sense that the payment will be computed based on the amount of 
-service provided. Thus, Ursula needs to confirm its activity by proving that she served 
-a given number of distinct re-encryption requests during a given period. To make the distinction 
-clear, we refer to the first as confirm availability, and for the second as confirm 
-service activity.
-
-In this document, we introduce several solutions for both forms of confirming activity. 
-These solutions differ in the trust, efficiency, interactivity, and resource 
-requirements, in addition to their security guarantees. We divide the document into 
-two parts, the first is about confirm availability, while the second is about confirm 
-service activity. We begin with outlining the adopted threat model for each problem 
-definition, as well as the network model. Then, we present the proposed solutions, discuss the aforementioned
-trade-offs and requirements of each of them, with the goal of selecting one of these 
-solutions to be adopted for each stage of the NuCypher network operation.
-
-\subsection{Threat and Network Models}
+\section{Threat and Network Models}
 \label{threat-network-model}
-This section describes a modification for the network model of NuCypher 
-required by the proposed solutions, in 
+This section describes a modification for the network model of NuCypher required by the proposed solutions, in 
 addition to the threat model adopted in this work.
 
-\subsubsection{Network Model.}
-In order for the proposed solutions to work, we need to ensure freshness, 
-integrity, and authenticity of the requests (as well as service complaints as we will see later) issued by Bob. This can be achieved 
-by requiring Bob to sign each re-encryption request it issues and to include a timestamp, or 
-sequence number, in each request to ensure freshness. The keypair used for the 
-signature should be separate from the keypair Bob uses for proxy encryption in the 
-system.
+\subsection{Network Model}
+In order for the proposed solutions to work, we need to ensure freshness, integrity, and authenticity of the requests (as well as service complaints as we will see later) issued by Bob.
+This can be achieved by requiring Bob to sign each re-encryption request it issues and to include a timestamp, or sequence number, in each request to ensure freshness.
+The keypair used for the signature should be separate from the keypair Bob uses for proxy encryption in the system.
 
-Until now we assume that Alice pays for the service by using the Ether she locks 
-in the policy contract. Other arrangement may emerge in the system like having 
-Bob pay for each requests he issues. Such an arrangement and its implication on the 
-confirm activity issue will be studied once it becomes part of the NuCypher 
-network protocol.
+Until now we assume that Alice pays for the service by using the Ether she locks in the policy contract.
+Other arrangement may emerge in the system like having Bob pay for each requests he issues.
+Such an arrangement and its implication on the confirm activity issue will be studied once it becomes part of the NuCypher network protocol.
 
-\subsubsection{Threat Model.}
+\subsection{Threat Model}
 In our threat model, we make the following set of assumptions:
@@
 \item {\bf Self-interested parties:} We do not place trust in any party and we assume that all participants are 
-self-interested. This means that a party may decide to 
-follow the protocol or deviate from it, either on its own or by colluding 
-with other attackers, and such decision is solely based on what maximizes the financial profits
+self-interested.
+This means that a party may decide to follow the protocol or deviate from it, either on its own or by colluding with other attackers, and such decision is solely based on what maximizes the financial profits
 of this party.
 
-\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out  
-its own Alice and/or Bob or collude with Alice. We do not consider collusion 
-between Bob and Ursula as a practical threat. This means that cases of Bob pretending  
-that he got service from Ursula (while no service is delivered) is not an issue. We do not 
-suspect this will be of any importance and there is no motivation to do it given that 
-the work Ursula does for re-encryption is minimal.
+\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out  its own Alice and/or Bob or collude with Alice.
+We do not consider collusion between Bob and Ursula as a practical threat.
+This means that cases of Bob pretending  that he got service from Ursula (while no service is delivered) is not an issue.
+We do not
+suspect this will be of any importance and there is no motivation to do it given that the work Ursula does for re-encryption is minimal.
 
-The above non-collusion assumption does not affect the solutions proposed to handle 
-the confirm service activity discussed in Section~\ref{confirm-service-activity}. This 
-means that these solutions provide higher 
-security guarantees and address the issue of potential collusion between Bob and Ursula. 
-It could be the case that relaxing the requirement of 
-addressing this collusion case allows deploying more efficient solutions. 
-In order to make an educated decision of the plausibility of this threat, we need 
-more data about the system operation and the behavior of the participants 
-once the inflation rewards disappears in the system. Therefore, we leave this 
+The above non-collusion assumption does not affect the solutions proposed to handle the confirm service activity discussed in Section~\ref{confirm-service-activity}.
+This means that these solutions provide higher security guarantees and address the issue of potential collusion between Bob and Ursula.
+It could be the case that relaxing the requirement of addressing this collusion case allows deploying more efficient solutions.
+In order to make an educated decision of the plausibility of this threat, we need more data about the system operation and the behavior of the participants once the inflation rewards disappears in the system.
+Therefore, we leave this
 issue until later when fees become the only source of rewards for Ursulas.
 
-\item {\bf Honest Ursulas:} We also assume that when sampling a subset of Ursulas in the network, 
-at least one of them is honest. This assumption can be achieved by 
-having a global assumption regarding the lower bound of the number of 
-honest Ursulas with respect to the total number of Ursulas in the system. 
-(Or it can be achieved by deploying a special entity like an external verifier, 
-that changes on a periodic basis, or one by the NuCypher company, that is
-trusted to faithfully participate as a member of each samples set. This 
-verifier does not provide any other services 
-in the system.)
+\item {\bf Honest Ursulas:} We also assume that when sampling a subset of Ursulas in the network, at least one of them is honest.
+This assumption can be achieved by having a global assumption regarding the lower bound of the number of honest Ursulas with respect to the total number of Ursulas in the system.
+(Or it can be achieved by deploying a special entity like an external verifier, that changes on a periodic basis, or one by the NuCypher company, that is trusted to faithfully participate as a member of each samples set.
+This verifier does not provide any other services in the system.)
 \end{itemize}
 
-Other than the above, we have usual assumptions like dealing with 
-computationally bounded adversaries 
+Other than the above, we have usual assumptions like dealing with computationally bounded adversaries 
 that cannot break secure cryptographic primitives with non-negligible probability.
-(We may need to work in the random oracle model, but this depends on the 
-security requirements of the proposed solutions.)
+(We may need to work in the random oracle model, but this depends on the security requirements of the proposed solutions.)

### 2020-08-03 confirm-activity/tex/confirm-availability.tex
fix intro and reorganize the paper
more reorganizing

--- 2020-05-06 tex/confirm-availability.tex
@@
-\section{Confirm Availability}
-In this section, we present a solution for confirming availability of 
-Ursulas. As mentioned before, in the early operation stage of the network we only 
-require Ursulas to be online and responsive to the re-encryption 
+\section{Confirm Availability Solution}
+\label{confirm-availability}
+In this section, we present a solution for confirming availability of Ursulas.
+As mentioned before, in the early operation stage of the network we only require Ursulas to be online and responsive to the re-encryption
 requests issued by Bob.
+
+The proposed solution is called \emph{Optimistic Challenge-based Approach}, which is centered around two important concepts: requiring minimal changes to the current network implementation, and minimizing the additional overhead.
 
@@
 
-\subsection{Optimistic Challenge-based Approach}
-The proposed solution is centered around two important concepts: requiring minimal 
-changes to the current network implementation, and minimizing the additional overhead. \\
-
-\noindent{\bf Discovering Working Ursulas.} Recall that in the NuCypher network, Bob receives a map from Alice containing 
+\paragraph{\bf Discovering working Ursulas.} 
+Recall that in the NuCypher network, Bob receives a map from Alice containing 
 the set of Ursulas that has the key fragments needed to implement the access control policy. 
@@
 We call this keypair a stamp, and we require an Ursula to use her stamp when signing all messages related to the proposed confirm availability protocol.
-\\
 
-\noindent{\bf Optimistic Ursula Challenging.} Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests.
+\paragraph{\bf Optimistic Ursula challenging.} 
+Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests.
 As noted, this communication is one-to-one meaning that no other Ursulas (or any
@@
 Once the proof-of-unavailability is verified, part of the working Ursula's stake will be slashed as a punishment.
-\\
 
-\noindent{\bf Gateways Selection.} For each round a set of $n$ gateways Ursulas will be selected.
+\paragraph{\bf Gateways Selection.} 
+For each round a set of $n$ gateways Ursulas will be selected.
 A proof-of-unavailability will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).
@@
 Alternatively, and to avoid the random oracle assumption, we can use randomness extractors to produce a high entropy beacon from the block hashes which itself could be low entropy~\cite{bonneau2015bitcoin}.
-\\
 
-\noindent{\bf Proof-of-unavailability processing.} As mentioned previously, a proof-of-unavailability against a working Ursula is a statement stating that this Ursula was unavailable during a specific round signed by at least $t$ gateways out of the $n$ gateways selected for that round.
+\paragraph{\bf Proof-of-unavailability processing.} 
+As mentioned previously, a proof-of-unavailability against a working Ursula is a statement stating that this Ursula was unavailable during a specific round signed by at least $t$ gateways out of the $n$ gateways selected for that round.
 Such a proof is submitted to the \stakeescrow contract and is verified as follows:
@@
 Which option to use depends merely on efficiency considerations.
-\\
 
-\noindent{\bf Quantifying the Financial Punishment or Slashing Value.}
+\paragraph{\bf Quantifying the Financial Punishment or Slashing Value.}
 A question that comes to mind is how much should be revoked from Ursula's stake once a proof-of-unavailability is approved?
@@
 In fact, the \stakeescrow contract will process only one proof against a working Ursula per round to reduce computational costs in the system.
-\\
 
-\noindent{\bf Working Only During the Challenge Phase.}
+\paragraph{\bf Working Only During the Challenge Phase.}
 A potential issue under the proposed optimistic scheme is that a working Ursula may operate only during the challenge phase.
@@
 Hence, there is no incentive at all to follow this strategy, meaning that a rational Ursula will act honestly.
-\\
 
-\noindent{\bf DoS Attacks.} 
+\paragraph{\bf DoS Attacks.} 
 Another potential issue is exploiting the unavailability complaints to perform a DoS attack against the gateways and working Ursulas.
@@
 
-\noindent{\bf Unresponsive Gateways.}
+\paragraph{\bf Unresponsive Gateways.}
 A third issue that we may encounter in the proposed solution is that the gateways themselves could be unresponsive.

### 2020-08-03 confirm-activity/tex/confirm-service-activity.tex
more reorganizing

@@
-\section{Confirm Service Activity}
+\section{Confirm Service Activity Solutions}
 \label{confirm-service-activity}
@@
 
-\subsection{Potential Solutions}
-\label{solutions}
-This section outlines several potential solutions for how to let Ursula prove 
-that she served a given number of distinct requests in a publicly verifiable way. 
-One of these solutions, the PCD-based one, is still a work in progress. The goal 
-is to share the high-level idea of each of these solutions and to chose the best one,
-after we define the meaning of best, to be adopted by the NuCypher network.
-
-\subsubsection{PCD-based Scheme.}
+\subsection{PCD-based Scheme.}
 The main idea here is to adapt the PCD framework so that Ursula
@@
 
-\subsubsection{CoSi-based Scheme.}
+\subsection{CoSi-based Scheme.}
 This solution utilizes the idea of collective signing by electing a committee 
@@
 
-\subsubsection{Commit/Challenge/Open-based Scheme.}
+\subsection{Commit/Challenge/Open-based Scheme.}
 This solution utilizes the idea of commit/challenge/open protocols. 

### 2020-08-03 confirm-activity/tex/discussion.tex
fix threat model section

@@
 This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
+
+Until now we assume that Alice pays for the service by using the Ether she locks in the policy contract.
+Other arrangement may emerge in the system like having Bob pay for each requests he issues.
+Such an arrangement and its implication on the confirm activity issue will be studied once it becomes part of the NuCypher network protocol.

### 2020-08-03 confirm-activity/tex/threat-model.tex
fix threat model section

@@
 \label{threat-network-model}
-This section describes a modification for the network model of NuCypher required by the proposed solutions, in 
-addition to the threat model adopted in this work.
+This section describes the network and threat models adopted by the proposed solutions.
+In particular, it introduces a modification for the network model of NuCypher, and it describes the security assumptions and attacker collusion cases considered in this work.
 
 \subsection{Network Model}
-In order for the proposed solutions to work, we need to ensure freshness, integrity, and authenticity of the requests (as well as service complaints as we will see later) issued by Bob.
-This can be achieved by requiring Bob to sign each re-encryption request it issues and to include a timestamp, or sequence number, in each request to ensure freshness.
-The keypair used for the signature should be separate from the keypair Bob uses for proxy encryption in the system.
-
-Until now we assume that Alice pays for the service by using the Ether she locks in the policy contract.
-Other arrangement may emerge in the system like having Bob pay for each requests he issues.
-Such an arrangement and its implication on the confirm activity issue will be studied once it becomes part of the NuCypher network protocol.
+In order for the proposed solutions to work, we need to ensure freshness, integrity, and authenticity of the re-encryption requests (as well as service complaints as we will see later) issued by Bob.
+This can be achieved by requiring Bob to include a timestamp, or sequence number, in each request to ensure freshness, and to sign the request to ensure integrity and authenticity.
+The keypair used for the signature should be separate from the keypair Bob uses for proxy re-encryption in the system.
 
 \subsection{Threat Model}
-In our threat model, we make the following set of assumptions:
+The goal of this document is to address accounting attacks, namely, holding Ursula accountable for the service it provides and for claiming being available and responsive.
+In addressing this type of attacks we adopt a threat model that makes the following set of assumptions:
 \begin{itemize}
@@
 
-\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out  its own Alice and/or Bob or collude with Alice.
-We do not consider collusion between Bob and Ursula as a practical threat.
-This means that cases of Bob pretending  that he got service from Ursula (while no service is delivered) is not an issue.
-We do not
-suspect this will be of any importance and there is no motivation to do it given that the work Ursula does for re-encryption is minimal.
+\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out her own Alice/Bob instances or collude with Alice or Bob.
+That is, by creating Alice/Bob instances (or colluding with them), Ursula will receive larger number of policies and re-encryption requests.
+Such a collusion case could be profitable if the subsidy size is influenced by the amount of service delivered.
+However, this is not the case in NuCypher as mentioned before.
+Thus, such a collusion scenario is not appealing to a rational Ursula.
 
-The above non-collusion assumption does not affect the solutions proposed to handle the confirm service activity discussed in Section~\ref{confirm-service-activity}.
-This means that these solutions provide higher security guarantees and address the issue of potential collusion between Bob and Ursula.
-It could be the case that relaxing the requirement of addressing this collusion case allows deploying more efficient solutions.
-In order to make an educated decision of the plausibility of this threat, we need more data about the system operation and the behavior of the participants once the inflation rewards disappears in the system.
-Therefore, we leave this
-issue until later when fees become the only source of rewards for Ursulas.
+Moreover, we do not consider collusion between Bob and Ursula as a practical threat.
+This means that cases of Bob pretending that he obtained service from Ursula (while no service has been delivered) is not an issue.
+We do not suspect this will be of any importance and there is no motivation to do it given that the work Ursula does for any re-encryption request is minimal (as we will see shortly, the ciphertext size is very small since it encrypts a symmetric key instead of the whole data).
+
+We note that the above non-collusion assumption does not affect the solutions proposed to handle the confirm service activity  (Section~\ref{confirm-service-activity}).
+This means that these solutions provide stronger security guarantees than the confirm availability solution (Section~\ref{confirm-availability}), where they address the issue of potential collusion between Bob and Ursula.
+In order to make an educated decision of the plausibility of this threat, we need more data about the system operation and the behavior of the participants once subsidies stop in the system.
 
 \item {\bf Honest Ursulas:} We also assume that when sampling a subset of Ursulas in the network, at least one of them is honest.
-This assumption can be achieved by having a global assumption regarding the lower bound of the number of honest Ursulas with respect to the total number of Ursulas in the system.
+This assumption can be achieved by having a global assumption regarding the lower bound of the number of honest Ursulas with respect to the total number of Ursulas in the NuCypher network.
 (Or it can be achieved by deploying a special entity like an external verifier, that changes on a periodic basis, or one by the NuCypher company, that is trusted to faithfully participate as a member of each samples set.
 This verifier does not provide any other services in the system.)
+
+\item {\bf Efficient adversaries.}.
+We deal with computationally-bounded (or probabilistic polynomial time) adversaries that cannot break secure cryptographic primitives with non-negligible probability.
 \end{itemize}
 
-Other than the above, we have usual assumptions like dealing with computationally bounded adversaries 
-that cannot break secure cryptographic primitives with non-negligible probability.
-(We may need to work in the random oracle model, but this depends on the security requirements of the proposed solutions.)
+We also work in the random oracle model where hash functions are modeled as random oracles.

### 2020-08-04 confirm-activity/tex/prelim.tex
edit prelim section

--- 2020-03-11 tex/prelim.tex
@@
 \label{prelim}
-This section provides an overview of two concepts that we use in the 
-proposed solutions. These include the framework of proof carrying data (PCD) 
-and the collective signing (CoSi) protocol.
+This section provides an overview of several concepts used in the proposed solutions. These include the framework of proof carrying data (PCD), and the collective signing (CoSi) protocol.
 
 \subsection{Proof Carrying Data (PCD)}
-The paradigm of PCD~\cite{chiesa2010proof} allows proving to the correctness of a distributed 
-computation involving untrusted parties. It produces a single proof for the output 
-that attests not only the correctness of the final result, but also 
-the correctness of the entire history of intermediate computations that produced 
-this result. Correctness here is defined as a polynomially computable predicate that 
-abstracts the properties, or invariants, that must be satisfied.
+The paradigm of PCD~\cite{chiesa2010proof} allows proving the correctness of a distributed computation performed by a set of untrusted parties.
+PCD produces a single proof that attests not only to the correctness of the final result, but also to the correctness of the entire history of intermediate computations that produced this result.
+Correctness here is defined as a polynomially computable predicate that abstracts the properties, or invariants, that must be satisfied.
 
@@
 
-To clarify how PDC works, consider a distributed computation task that involves 
-the set of parties shown in Figure~\ref{pcd-diagram}. Party $P_1$ starts the computation with its 
-own input, produces an intermediate output with a proof saying that it performed 
-the computation as defined by the protocol. It then sends both the output and the proof 
-to the next party, which is $P_2$ in this case. Here, $P_2$ will 
-have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) 
-as input to the computation it will perform. Similarly, $P_2$ will produce another 
-intermediate output and a proof. This proof not only attests to the correctness of the 
-computation done by $P_2$, but also the history that lead to the result $y_2$. In other 
-words, it implicitly includes 
-the proof from $P_1$. The same process continues until the full computation is finished. 
-Anyone can verify the correctness or compliance of the whole distributed protocol by 
-only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.
+To clarify how PCD works, consider a distributed computation task that involves the set of parties shown in Figure~\ref{pcd-diagram}.
+Party $P_1$ starts the computation with its own input, produces an intermediate output with a proof saying that it performed the computation as defined by the protocol.
+It then sends both the output and the proof to the next party, which is $P_2$ in this case.
+Here, $P_2$ will have its own input $x_2$, as well as everything it received from $P_1$ (including the proof) as inputs to the next step of the computation.
+Similarly, $P_2$ will produce another intermediate output and a proof.
+This proof not only attests to the correctness of the computation done by $P_2$, but also to the history that led to the result $y_2$.
+In other
+words, it implicitly includes, or accumulates, the proof from $P_1$.
+The same process continues until the full computation is finished.
+Anyone can verify the correctness or compliance of the whole distributed protocol by only verifying the last proof $\pi_6$ produced by the exit party, which is $P_6$ in the figure.
 
-As shown, PCDs enable untrusted parties to work with each other in a fully distributed 
-fashion, without overwhelming the system with the storage and verification of individual 
-proofs for each step of the performed protocol. Also, they attest to correctness or compliance  
-to the prescribed protocol without re-executing any of the intermediate computations. Thus, 
-they provide a promising paradigm for confirming service activity in a compact way.
+As shown, PCDs enable untrusted parties to work with each other in a fully distributed fashion, without overwhelming the system with the storage and verification of individual proofs for each step of the distributed computation, and without re-executing any of the intermediate computations.
 
@@
 \label{cosi}
-CoSi~\cite{syta2016keeping} is a protocol that enables a set of distributed parties to cosign a 
-statement together in a way that produces a single signature. As such, both the 
-verification time and the space requirements are just like having a single signer. The 
-difference is that this signature attests that all parties agree with the signed 
-statement instead of only one.
+CoSi~\cite{syta2016keeping} is a protocol that enables a set of parties to cosign a statement together while producing a single signature.
+Thus, both the verification time and the space requirements are just like having a single signer.
+However, this signature holds all parties accountable for the statement they agreed to sign.
 
-CoSi builds upon Schnorr 
-multisignatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines 
-them with communication trees to speed up the signing process in 
-case of large number of cosigners. In what follows, we only present the protocol 
-with a plain communication architecture as it suffices for the confirm service activity 
-solution introduced in this document.
+CoSi builds upon Schnorr multi-signatures~\cite{schnorr1991efficient, bellare2006multi, micali2001accountable}, but combines them with communication trees to speed up the signing process, especially when having a large number of cosigners.
+In what follows, we only present the protocol with a plain communication architecture as it suffices for the confirm service activity solution introduced in this document.
 
-Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and 
-generator $g$, such that the discrete log is believed to be hard in this group. 
+Schnorr signatures work in a group $\mathbb{G}$ of a prime order $q$ and generator $g$, such that the discrete log is believed to be hard in this group.
 Take $n$ parties that want to sign a statement together.
-Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key 
-$pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$. To sign a message $m$, 
-one of these parties, let's say $P_1$, coordinates the signing process as follows: 
+Each of these parties has a secret $sk_i \in \mathbb{Z}_q$ and a public key $pk_i \in \mathbb{G}$ such that $pk_i = g^{sk_i}$.
+To sign a message $m$, one of these parties, say $P_1$, coordinates the signing process as follows:
 \begin{enumerate}
@@
 
-\item Each party $P_i$, possibly after verifying 
-$m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and compute $V_i = g^{\tau_i}$, 
-then it sends $V_i$ back to $P_1$.
+\item Each party $P_i$, possibly after verifying $m$, selects a secret $\tau_i \in \mathbb{Z}_q$ and computes $V_i = g^{\tau_i}$, then it sends $V_i$ back to $P_1$.
 
-\item $P_1$ aggregates all random values received from 
-the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.
+\item $P_1$ aggregates all random values received from the signers, and its own, by computing $V = \Pi_{i =1}^n V_i$.
 
-\item $P_1$ then computes 
-$c = H(V||m)$, where $H$ is an appropriate hash function. $P_1$ then 
-sends $c$ to the rest of the parties.
+\item $P_1$ then computes $c = H(V||m)$, where $H$ is an appropriate hash function and $||$ is a concatenation operator. $P_1$ then sends $c$ to the rest of the parties.
 
-\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and 
-sends it to $P_1$.
+\item Each party computes a response $r_i = \tau_i - sk_i\cdot c$ and sends it to $P_1$.
 
-\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the 
-collective signature over $m$ as $(c, r)$.
+\item Lastly, $P_1$ computes $r = \sum_{i=1}^n r_i$, and outputs the collective signature over $m$ as $(c, r)$.
 \end{enumerate}
 
-Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with 
-one difference. An aggregated public key $pk$ is used in the verification process, 
-which is computed as $pk = \Pi_{i=1}^{n} pk_i$.
+Verifying the signature proceeds as in classical Schnorr signatures~\cite{schnorr1991efficient} with one difference.
+An aggregated public key $pk$ is used in the verification process, which is computed as $pk = \Pi_{i=1}^{n} pk_i$.
 
-The work in~\cite{syta2016keeping} tackles several issues related to 
-the availability of the 
-signing parties, and optimizing the communication between them. 
-We believe that such techniques can be used in the NuCypher network if we adopt the 
-CoSi-based solution for the confirm service activity issue.
+The work in~\cite{syta2016keeping} tackles several issues related to the availability of the signing parties, and optimizing the communication between them.
+We believe that such techniques can be used in the NuCypher network if we adopt the CoSi-based solution for the confirm service activity issue.

### 2020-08-04 confirm-activity/tex/confirm-availability.tex
fix confirm availability section

@@
 \label{confirm-availability}
-In this section, we present a solution for confirming availability of Ursulas.
-As mentioned before, in the early operation stage of the network we only require Ursulas to be online and responsive to the re-encryption
-requests issued by Bob.
-
-The proposed solution is called \emph{Optimistic Challenge-based Approach}, which is centered around two important concepts: requiring minimal changes to the current network implementation, and minimizing the additional overhead.
-
+In this section, we present a solution for confirming availability of Ursulas, which will be used during early operation stage of the network.
+The proposed solution is called \emph{Optimistic Challenge-based Approach}.
+It is centered around two important concepts: requiring minimal changes to the current network implementation, and minimizing the additional overhead.
 We introduce the design details of our solution, after which we discuss some potential security attacks and how to address them.
 
-\paragraph{\bf Discovering working Ursulas.} 
-Recall that in the NuCypher network, Bob receives a map from Alice containing 
-the set of Ursulas that has the key fragments needed to implement the access control policy. 
-When issuing a re-encryption request, Bob uses this map (in association with the network discovery protocol) to reach each of these Ursulas and obtain 
-the service.
+\paragraph{\bf Overview.} The optimistic challenge-based approach is based on a detect-and-punish technique.
+As long as everything work as expected, no extra measures will be invoked.
+In other words, investigating the status of a specific Ursula is activated only when Bob does not hear back regarding a re-encryption request he has issued.
+Thus, Bob proceeds as usual in requesting the service.
+If any of the contacted Ursulas does not reply, Bob submits a complaint claiming that this Ursula is unavailable.
+This complaint triggers the challenge phase in the network to verify Bob's claim, and hence, punish Ursula financially (by slashing part of her stake) in case the claim found to be valid.
 
-In particular, in the NuCypher network there is a separation between the role of a staker and a working Ursula.
+The proposed scheme labels Ursulas in the network under two classes: Working Ursulas, which is the conventional role of maintaining access policies and providing the re-encryption service.
+And gateway Ursulas, which is an additional role of handling Bob's complaints.
+Gateway Ursulas are a subset of the working Ursulas that is selected at random for each round.\footnote{A round is the time needed to mine a block or several blocks on the blockchain.} Hence, each working Ursula will get to serve as a gateway from time to time.
+
+Accordingly, Bob contacts working Ursulas listed in Alice's policy.
+If any of them does not reply, Bob reaches out to a gateway Ursula and forwards her the request.
+The gateway in turn mediates the service session by forwarding the request to the working Ursula again and waiting for a reply.
+If a reply is received, the gateway sends it to Bob and closes the case.
+
+On the other hand, if no reply is received, the gateway notifies other gateways selected for the current round to repeat the mediation process.
+If none of them receive a reply, they collectively sign (using the CoSi protocol described in Section~\ref{cosi}) a statement against the working Ursula, which we call a proof-of-unavailability.
+This proof is submitted to the \stakeescrow contract, and after being verified, part of the working Ursula's stake will be slashed as a punishment.
+
+\paragraph{\bf Working Ursulas discovery.} 
+In the NuCypher network there is a separation between the role of a staker and a working Ursula.
 All stakers' Ethereum addresses, along with their stake values, are recorded in one of the NuCypher network smart contracts, namely, the \stakeescrow contract.
@@
 
+For each access policy, Alice delegates the re-encryption service to a designated set of working Ursulas.
+Each of these Ursulas will be supplied with a re-encryption key fragment that converts a ciphertext encrypted under Alice's public key into a ciphertext fragment encrypted under Bob's public key.
+Once Bob gets a sufficient number of ciphretext fragment, based on some threshold, he can combine these fragments together to get the complete ciphertext, which he can decrypt.
+
 The \stakeescrow contract does not contain any information about how to reach a specific working Ursula.
-Thus, the map that Bob receives includes only the Ethereum addresses of the working Ursulas.
+Thus, and as part of the access policy, Bob receives a map from Alice containing the set of working Ursulas that has the key fragments, along with their Ethereum addresses.
 To allow the parties to communicate with each other, each participant, i.e., Alice, Bob, Ursula, employs a discovery protocol (more like a gossiping protocol) to discover the IP addresses and ports of the working Ursulas in the network.
+Hence, Bob uses the map (in association with the network discovery protocol) to reach each of these Ursulas and obtain the service.
 
@@
 
-\paragraph{\bf Optimistic Ursula challenging.} 
-Once Bob discovers the working Ursulas listed in the policy map, he can connect with each of them and start issuing service requests.
-As noted, this communication is one-to-one meaning that no other Ursulas (or any
-NuCypher network participant) mediates the communication between Bob and working  
-Ursula. This in turn means that no one can attest to whether Ursula has responded if Bob 
-complains later that he was not served.
-
-The main idea is to add a mediator, or potentially a witness, in the service process (if needed) to monitor a specific working Ursula and challenge its responsiveness.
-Hence, it is an optimistic protocol invoked only when Bob complains about not receiving the service.
-In detail, for each round (where a
-round is the time needed to mine a block or several blocks on the blockchain) a set of Ursulas is selected at random.
-We call these gateway Ursulas.
-Bob contacts a working Ursula asking for the re-encryption service as usual.
-If this Ursula does not respond, Bob complains to a gateway about it.
-At this point, the gateway will act as an intermediary and forwards Bob's request to this working Ursula on behalf of Bob and waits for the answer.
-If no answer is received, this gateway will trigger other gateways to perform the same process, i.e., forward the request on behalf of Bob and wait for an answer.
-If the working
-Ursula is still unresponsive, these gateways will collectively sign a proof-of-unavailability, which is basically a statement saying that the working Ursula was contacted by these gateways and she did not respond, and publish it through the \stakeescrow contract (see Section~\ref{cosi} for an overview of collective signing).
-Once the proof-of-unavailability is verified, part of the working Ursula's stake will be slashed as a punishment.
-
-\paragraph{\bf Gateways Selection.} 
-For each round a set of $n$ gateways Ursulas will be selected.
+\paragraph{\bf Gateway Ursulas selection.} 
+For each round a set of $n$ gateway Ursulas will be selected.
 A proof-of-unavailability will be accepted by the network if it is signed by at least $t$ gateways among this set (this threshold is a relaxation of requiring all gateways to sign since it could be the case that not all of them are active).
 
-A simple idea to select the gateways is to use a high entropy source of randomness to obtain a random beacon for each round.
+A simple idea to select the gateways, similar to the deterministic lottery protocol found in~\cite{almashaqbeh2020microcash}, is to use a high entropy source of randomness to obtain a random beacon for each round.
 Then feed this beacon into an iterative hashing process.
-After each iteration, map the hash to a working Ursula index as listed in the \stakeescrow contract.
+That is, let the random beacon of the $i^{th}$ round be $r_i$, and let a hash function be denoted as $H(\cdot)$.
+To select the first gateway, the hash $h_1 = H(r_i)$ is computed, and then it is mapped to a working Ursula index as listed in the \stakeescrow contract.
 That is, the working Ursula bonded with the first staker listed in the contract has index 0, the next has index 1, etc.
-Then, rehash the previous hash and map the output to an index, and so no.
-In case of a collision, i.e., an already selected index is produced again, discard it and proceed to the next hash iteration.
-This process is repeated until a set of distinct $n$ indices is computed.
+Then, to select the second gateway, hash the previous hash to obtain $h_2 = H(h_1)$ and map the output to a working Ursula index, and so no.
+In case of a collision, i.e., an already selected index is selected again, discard it and proceed to the next hash iteration.
+This process continues until a set of distinct $n$ indices is computed.
 
-Note that the selection process may contain Ursulas for which Bob does not have a contact information.
+It should be noted that since the random beacon is public, although it will be known only when round $i$ starts, any party can compute the set of selected indices.
+Thus, Bob performs the hash iterative process when needed to obtain the gateways.
+The selection can be also verified by repeating the hash iterative process by any other party.
+
+Furthermore, note that the selection process may produce Ursulas for which Bob does not have a contact information.
 Hence, Bob has to discover these Ursulas before being able to submit a complaint.
@@
 
-Furthermore, the above protocol assumes working in the random oracle model, meaning that hash functions are modeled as random oracles.
-Thus, the iterative hashing process selects at random the working Ursulas.
+The above protocol assumes working in the random oracle model, meaning that hash functions are modeled as random oracles.
+Thus, the iterative hashing process is conjectured as producing a random, unbiased output.
 Although, we believe this is sufficient for our purposes, this can be replaced with more sophisticated approaches to produce random strings (that are then mapped to indices), e.g., a verifiable random function~\cite{micali1999verifiable}.
-We leave this as part of our future work in case we decide to pursue this path.
 
-As for the high entropy source of randomness, there are several potential approaches here.
-We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon} or even a combination of multiple sources, for that.
-Or we can work also in the random oracle model and assume that block hashes are drawn from a uniform distribution, and thus, use the block hash as a random beacon.
-In particular, for the current round, the hash of the block that was mined $y$ rounds ago is used ($y$ is the confirmation interval in the underlying cryptocurrency system).
-Alternatively, and to avoid the random oracle assumption, we can use randomness extractors to produce a high entropy beacon from the block hashes which itself could be low entropy~\cite{bonneau2015bitcoin}.
+As for the high entropy source of randomness, there are several potential approaches to fulfill it.
+We can rely on an external source, e.g., the NIST random beacon~\cite{nist-beacon}, or even a combination of multiple sources.
+Or we can also resort to the random oracle model and assume that block hashes are drawn from a uniform distribution, and thus, use the hash of the block mined in the current round as a random beacon.\footnote{To handle inconsistencies of the blockchain view, the hash of the block that is confirmed at the current round can ebe used.
+This is the block that was mined $y$ rounds ago where $y$ is the confirmation interval in the underlying cryptocurrency system.} Alternatively, and to address concerns regarding the low entropy of block hashes, we can use randomness extractors to produce a high entropy beacon from the block hashes~\cite{bonneau2015bitcoin}.
 
@@
 \begin{itemize}
-\item Produce the list of gateways selected for the current round. This is done by using the same process described previously.
+\item Reproduce the list of gateways selected for the current round, by using the same process described previously, to verify the signing gateways are legitimate.
 
-\item Verify the collective signature over the signed statement (see Section~\ref{cosi}).
+\item Compute the collective verification key of the cosigners and verify the collective signature over the signed statement (see Section~\ref{cosi}).
 
-\item If everything is fine, the \stakeescrow contract revokes part of the stake bonded to the working Ursula as a punishment.
+\item If all checks pass, meaning that the proof-of-unavailability is valid, the \stakeescrow contract revokes part of the stake bonded to the working Ursula as a punishment.
 \end{itemize}
@@
 
-\paragraph{\bf Quantifying the Financial Punishment or Slashing Value.}
-A question that comes to mind is how much should be revoked from Ursula's stake once a proof-of-unavailability is approved?
-Quantifying this amount should be driven by two factors; the unavailability duration and the utility gain (or profits) of this cheating behavior in terms of the collected fees and inflation rewards for that duration.
+\paragraph{\bf Working only during the challenge phase.}
+A potential attack on our scheme is that a working Ursula may operate only during the challenge phase.
+That is, she ignores any fresh request coming from Bob, and just replies afterwards when receiving the same request again (i.e., when it is being forwarded by the gateways during the challenge phase).
 
-Accordingly, we can compute this value to be equal to the fees and inflation rewards that an Ursula is supposed to receive in a round (recall that a round is the time needed to mine a block or several blocks on the blockchain).
-Hence, the working Ursula will, first, lose her fees and inflation rewards from the network, and second, lose the same amount from her stake.
-Such a loss will take place even if a single proof-of-unavailability is received against a working Ursula within a round.
-In fact, the \stakeescrow contract will process only one proof against a working Ursula per round to reduce computational costs in the system.
-
-\paragraph{\bf Working Only During the Challenge Phase.}
-A potential issue under the proposed optimistic scheme is that a working Ursula may operate only during the challenge phase.
-That is, she ignores any fresh request coming from Bob, and just replies afterwards when receiving the same request again (i.e., when it is forwarded by the gateways during the challenge phase).
-
-We argue that such a behavior is not a practical issue since a rational Ursula will be online eitherway to monitor whether this is a challenge phase or not, and that the amount of work needed to respond to a re-encryption request is minimal.
+We argue that such an attack is not a practical issue since a rational Ursula will be online eitherway to monitor whether this is a challenge phase or not.
+Also, the amount of work needed to respond to a re-encryption request is minimal.
 Hence, there is no incentive at all to follow this strategy, meaning that a rational Ursula will act honestly.
 
-\paragraph{\bf DoS Attacks.} 
+\paragraph{\bf DoS attacks.} 
 Another potential issue is exploiting the unavailability complaints to perform a DoS attack against the gateways and working Ursulas.
-In detail, Bob may lie and issue complaints against working Ursulas even though they are responsive just to slash their stakes.
-Or an attacker may replay these complaints, or issue them on behalf of Bob, to slash a working Ursula.
-Or the goal could be to overwhelm the gateways with the challenge process and make them unavailable to perform the re-encryption service (recall that the gateways are originally working Ursulas in the NuCypher network).
+In detail, Bob may issue fake complaints against working Ursulas, even though they are responsive.
+Alternatively, an attacker (insider or outsider) may replay these complaints, or issue them on behalf of Bob.
+The goal could be to slash Ursula's stake or to overwhelm the gateways with the challenge process and make them unavailable to perform the re-encryption service (recall that the gateways are originally working Ursulas in the NuCypher network).
 
-This issues can be handled using a collection of techniques as follows:
+This issue can be handled using a collection of techniques as follows:
 \begin{itemize}
@@
 
-\paragraph{\bf Unresponsive Gateways.}
-A third issue that we may encounter in the proposed solution is that the gateways themselves could be unresponsive.
+Furthermore, since gateways Ursulas are selected fresh at random for each round, an Ursula will get the chance to be only a working Ursula during some rounds.
+This reduces the impact of gateway DoS attacks for any Ursula as the gateway role is rotating and not fixed.
+
+\paragraph{\bf Unresponsive gateways.}
+There is a chance that the gateways themselves could be unresponsive.
 This will stall the challenge phase and make it infeasible to prove that some working Ursula is unavailable.
@@
 
-Another mechanism is to incentivize the gateways to do the work in the form of a small fee paid out of the revoked stake.
+Moreover, to encourage gateway participation, a potential approach is to incentivize Ursulas to do the work by paying them a small fee.
+Such a fee could be out of the revoked stake (if any) or paid by Alice from her access policy funds.
 
-It could be the case that all gateways in a round are responsive (although we believe that the probability this happens is very low).
+It could be the case that all gateways in a round are unresponsive (although we believe that the probability this happens is very low).
 In this case, it could be viable to perform the challenge phase in a recursive way.
@@
 The previous round gateways will in turn challenge the current round gateways by forwarding Bob's complaint to them and sign a proof-of-unavailability if no response is received.
+
+\paragraph{\bf Quantifying the financial punishment.}
+A question that comes to mind is how much should be revoked from Ursula's stake once a proof-of-unavailability is approved?
+Quantifying this amount should be driven by two factors; the unavailability duration and the utility gain (or profits) of this cheating behavior in terms of the collected fees and subsides during that period.
+
+We can compute this value to be equal to the fees and subsidies that an Ursula is supposed to receive in a round.
+Hence, the working Ursula will, first, lose her round payments from the network (she will not get paid by Alice or by the network), and second, lose the same amount from her stake.
+Such a loss will take place even if a single proof-of-unavailability is received against a working Ursula within a round.
+In fact, the \stakeescrow contract will process only one proof against a working Ursula per round to reduce computational costs in the system.

### 2020-08-04 confirm-activity/tex/confirm-service-activity.tex
fix the discussion section

@@
 \label{confirm-service-activity}
-In this section, we present potential solutions for the confirm service activity 
-problem. The goal is to come up with provably secure solutions that allows an 
-Ursula to prove that it has served a given number of distinct re-encryption 
-requests within a given period.
+In this section, we present potential solutions for the confirm service activity problem.
+The goal is to come up with provably secure solutions that allows an Ursula to prove that it has served a given number of distinct re-encryption requests within a given period.
 
-The rest of this section discusses the proposed solutions along with an analysis of 
-their security and efficiency aspects. Lastly, the section concludes with directions of 
-future work on the confirm service activity issue.
+The rest of this section discusses the proposed solutions along with an analysis of their security and efficiency aspects.
+Lastly, the section concludes with directions of future work on the confirm service activity issue.
 
-\subsection{PCD-based Scheme.}
-The main idea here is to adapt the PCD framework so that Ursula
-can combine the correctness proofs she computes for Bobs' requests in a single proof 
-attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
-requests correctly."
+\subsection{ZKP-based Scheme}
+The main idea here is to adapt the PCD framework so that Ursula can combine the correctness proofs she computes for Bobs' requests in a single proof attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption requests correctly."
 
 Thus, in this setup, there is only one computation party, or prover, namely, Ursula.
-For each round, where a round could be the time needed to mine a block on the 
-blockchain, Ursula starts with input $x_1$, which is a signed and fresh request
-from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
-proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
-proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
-which is the input for the next step in the computation, Ursula answers 
-this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then 
-it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
-$\hat{\pi}_2$ does not only 
-attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
-two valid distinct requests until now. The same process is repeated until the end of the 
-round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
-served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
+For each round, where a round could be the time needed to mine a block on the blockchain, Ursula starts with input $x_1$, which is a signed and fresh requestfrom Bob.
+It answers this request with $cFrag_{x_1}$ and produces a correctness proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness proof $\hat{\pi}_1$ that will be used in the PCD composition.
+Then, when the next request $x_2$ arrives, which is the input for the next step in the computation, Ursula answers this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$.
+$\hat{\pi}_2$ does not only attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served two valid distinct requests until now.
+The same process is repeated until the end of the round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of served requests $\omega$.
+Figure~\ref{pcd-based-sol} depicts
 this process pictorially.
@@
 \includegraphics[height= 0.7in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
-\caption{PCD-based solution diagram. Ursula starts a round in the idle state. When 
-the first request arrives, Ursula responds to the request and starts composing the 
-proofs as new requests arrive. At the end of the round, Ursula announces the number of 
-served requests and a single proof attesting to its claim to the network. }
+\caption{PCD-based solution diagram.
+Ursula starts a round in the idle state.
+When the first request arrives, Ursula responds to the request and starts composing the proofs as new requests arrive.
+At the end of the round, Ursula announces the number of served requests and a single proof attesting to its claim to the network.
+}
 \label{pcd-based-sol}
@@
 
-The final proof will be processed by the contract that governs Alice's policy. A valid proof 
-allows Ursula to claim fees out of Alice's Ether escrow as a payment for $\omega$ re-encryption  
-requests.
+The final proof will be processed by the contract that governs Alice's policy. A valid proof allows Ursula to claim fees out of Alice's Ether escrow as a payment for $\omega$ re-encryption  requests.
 
-The above is a high level description of the idea. However, more time is need to 
-understand PCD and SNARKs in order to come up with a concrete construction 
-(if possible). Please see Section~\ref{future-work} for more information.
+The above is a high level description of the idea.
+However, more time is need to understand PCD and SNARKs in order to come up with a concrete construction (if possible).
+Please see Section~\ref{future-work} for more information.
 
-\subsection{CoSi-based Scheme.}
-This solution utilizes the idea of collective signing by electing a committee 
-that will sign a report submitted by a specific Ursula after verifying that 
-the report supports the claim that ``Ursula has served $\omega$ distinct 
-re-encryption requests correctly."
+\subsection{CoSi-based Scheme}
+This solution utilizes the idea of collective signing by electing a committee that will sign a report submitted by a specific Ursula after verifying that the report supports the claim that ``Ursula has served $\omega$ distinct re-encryption requests correctly."
 
-At a high level, the scheme works as follows. For each round, a working Ursula keeps 
-a full record of all the requests that she served during the round. These 
-include the signed requests received from Bob(s), and the produced $cFrag$ 
-and the correctness proof $\pi$ (as in the Umbral scheme) for 
-each request. At the end of the round, a committee of $t$ Ursulas is 
-elected, where $t$ is a small integer, e.g., $t = 5$. The working Ursula 
-initiates the CoSi protocol to sign the message $m$ stated above while 
-replacing $\omega$ with the actual number of served 
-requests in the round. This Ursula sends $m$ along with the full report to 
-each member in the committee. Each member Ursula (i.e., member in the 
-elected committee) verifies $m$ by checking the report as follows:
+At a high level, the scheme works as follows.
+For each round, a working Ursula keeps a full record of all the requests that she served during the round.
+These include the signed requests received from Bob(s), and the produced $cFrag$ and the correctness proof $\pi$ (as in the Umbral scheme) for each request.
+At the end of the round, a committee of $t$ Ursulas is elected, where $t$ is a small integer, e.g., $t = 5$.
+The working Ursula
+initiates the CoSi protocol to sign the message $m$ stated above while replacing $\omega$ with the actual number of served requests in the round.
+This Ursula sends $m$ along with the full report to each member in the committee.
+Each member Ursula (i.e., member in the elected committee) verifies $m$ by checking the report as follows:
 \begin{enumerate}
 \setlength{\itemsep}{0pt}
-\item Check that each request is distinct by checking the sequence 
-number of the request (or any value that is used for freshaness), and valid by verifying Bob's 
-signature over the request. (Here the policy will contain Bob's public 
-key to allow the committee use the right verification key.)
+\item Check that each request is distinct by checking the sequence number of the request (or any value that is used for freshaness), and valid by verifying Bob's signature over the request.
+(Here the policy will contain Bob's public key to allow the committee use the right verification key.)
 
-\item Verify the correctness of each $cFrag$ as in the Umbral 
-scheme.
+\item Verify the correctness of each $cFrag$ as in the Umbral scheme.
 
-\item Check that the value of $\omega$ inside $m$ agrees with the 
-record.
+\item Check that the value of $\omega$ inside $m$ agrees with the record.
 \end{enumerate}
 
-If everything is fine, each member of the committee and the working 
-Ursula finalize the CoSi signing protocol as described in Section~\ref{cosi}. 
-At the end, the working Ursula publishes the collective signature, which can be 
-verified using the accumulated public keys of the cosigning Ursulas.
+If everything is fine, each member of the committee and the working Ursula finalize the CoSi signing protocol as described in Section~\ref{cosi}.
+At the end, the working Ursula publishes the collective signature, which can be verified using the accumulated public keys of the cosigning Ursulas.
 
-\paragraph{On the committee election.} This can be done
-by using some deterministic computation over a block hash and mapping
-the output to Ursulas' public keys. So the selection is not determined by the
-working Ursula to prevent any potential collusion.
+\paragraph{\bf On the committee election.} 
+This can be done by using some deterministic computation over a block hash and mapping the output to Ursulas' public keys.
+So the selection is not determined by the working Ursula to prevent any potential collusion.
 The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.
 
-The above scheme works under the assumption that at least one Ursula
-in the elected committee is honest, which pertains to an assumption on the
-least number of honest Ursulas in the network. If the latter assumption is under threat, one mitigating approach is to increase $t$ (the committee size).
+The above scheme works under the assumption that at least one Ursula in the elected committee is honest, which pertains to an assumption on the least number of honest Ursulas in the network.
+If the latter assumption is under threat, one mitigating approach is to increase $t$ (the committee size).
 
-Another approach is to have a changing set of external verifiers, like
-trusted partners, that all working Ursulas must use for the CoSi signing
-of their records.
+Another approach is to have a changing set of external verifiers, like trusted partners, that all working Ursulas must use for the CoSi signing of their records.
 
-A third approach is to keep the deterministic selection of the committee
-but with an external member, e.g., either a trusted partner verifier
-or a special verifier node deployed and maintained by the NuCypher company.
-Thus, achieving the assumption of at least one member of the elected
-committee is honest.
+A third approach is to keep the deterministic selection of the committee but with an external member, e.g., either a trusted partner verifier or a special verifier node deployed and maintained by the NuCypher company.
+Thus, achieving the assumption of at least one member of the elected committee is honest.
 
-\paragraph{On the publicity of the signed records.} Having a 
-valid collective signature from a committee (that has at least one honest 
-member) suffices for the correctness of the signed statement. However, 
-it could be better to keep the records that produced the message $m$  
-available for a while so that any party can verify them (the verifying
-parties could maintain such a public record for a given period after which
-the logs can be discarded).
+\paragraph{\bf On the publicity of the signed records.} 
+Having a valid collective signature from a committee (that has at least one honest member) suffices for the correctness of the signed statement.
+However, it could be better to keep the records that produced the message $m$  available for a while so that any party can verify them (the verifying parties could maintain such a public record for a given period after which the logs can be discarded).
 
-We can resort to this option just at the beginning to convince the 
-participants of the trustworthiness of the committee or the validity of the
-assumption that at least one Ursula in the elected committee is honest.
+We can resort to this option just at the beginning to convince the participants of the trustworthiness of the committee or the validity of the assumption that at least one Ursula in the elected committee is honest.
 
-\paragraph{On compensating the committee.} This solution may 
-raise the question of why would the elected committee (especially if it 
-is composed of other Ursulas in the system) participate in the CoSi 
-process, which also involves verifying the full request record presented 
-by the working Ursula. This can be pictured as a collaborative
-work, the committee does the work so that others will do the same
-when the committee members play the role of working Ursulas.
+\paragraph{\bf On compensating the committee.} 
+This solution may raise the question of why would the elected committee (especially if it is composed of other Ursulas in the system) participate in the CoSi process, which also involves verifying the full request record presented by the working Ursula.
+This can be pictured as a collaborative work, the committee does the work so that others will do the same when the committee members play the role of working Ursulas.
 
-Another option is to pay the committee for their work, either as
-part of the inflation rewards, or by having working Ursulas pay for 
-it (however, this may complicate the system operation).
+Another option is to pay the committee for their work, either as part of the inflation rewards, or by having working Ursulas pay for it (however, this may complicate the system operation).
 
-\subsection{Commit/Challenge/Open-based Scheme.}
+\subsection{Commit/Challenge/Open-based Scheme}
 This solution utilizes the idea of commit/challenge/open protocols.
-In details, Ursula keeps track of the requests coming from Bob(s) 
-during a time round and assign each of them a unique sequence 
-number. That is, Ursula replies with $cFrag$ and the correctness proof 
-along with a sequence number showing the order of the request within 
-the batch of requests handled during a round. At the end of the round, 
-Ursula constructs a Merkle tree of all requests, where 
-the requests (and their replies) are the leaves of the tree ordered by the sequence
-numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
-a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
-to the network (recall that $\omega$ is the number of served requests).
+In details, Ursula keeps track of the requests coming from Bob(s) during a time round and assign each of them a unique sequence number.
+That is, Ursula replies with $cFrag$ and the correctness proof along with a sequence number showing the order of the request within the batch of requests handled during a round.
+At the end of the round, Ursula constructs a Merkle tree of all requests, where the requests (and their replies) are the leaves of the tree ordered by the sequence numbers.
+Ursula signs the root of the tree, denoted as $root$ to produce a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ to the network (recall that $\omega$ is the number of served requests).
 
 To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree.
-This can be done by having the policy contract select at random (e.g. based
-on the block hash or any other mechanism) the leaf IDs to be opened. If 
-Ursula fails to open them correctly within a predefined timeframe, she loses the 
-whole fee she was supposed to collect for serving $\omega$ requests.
+This can be done by having the policy contract select at random (e.g.
+based on the block hash or any other mechanism) the leaf IDs to be opened.
+If Ursula fails to open them correctly within a predefined timeframe, she loses the whole fee she was supposed to collect for serving $\omega$ requests.
 
-An alternative approach to the challenge/open scheme described above is to 
-have Ursula publish the full Merkle tree on some known public space but
-not on the blockchain, and make the full record available online for a specific period
-to allow anyone to verify the work. If no one files a complaint about the tree (we
-still need to define correctness properties, like checking all Bob public keys are 
-defined in the policy created by Alice, and that the response is valid by checking the 
-proof produced by Umbral), Ursula collects the fees for the provided service. On the other
-hand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.
+An alternative approach to the challenge/open scheme described above is to have Ursula publish the full Merkle tree on some known public space but not on the blockchain, and make the full record available online for a specific period to allow anyone to verify the work.
+If no one files a complaint about the tree (we still need to define correctness properties, like checking all Bob public keys are defined in the policy created by Alice, and that the response is valid by checking the proof produced by Umbral), Ursula collects the fees for the provided service.
+On the otherhand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.

### 2020-08-04 confirm-activity/tex/discussion.tex
fix the discussion section

--- 2020-08-03 confirm-activity/tex/discussion.tex
@@
-\section{Discussion and Analysis}
+\section{Discussion}
 \label{discussion}
-Which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network.
-The ZKP-based solution (the one utilizing bulletproofs) provides several advantages including non-interactivity (as opposed to the committee-attestation one that needs interaction with the committee).
+As we mentioned earlier, now in the NuCypher network, we have the naive confirm activity function calling approach, with a financial punishment of slashing the stake of any Ursula who does not log her activity periodically.
+Our early plans will be to replace this approach with the confirm availability solution introduced in Section~\ref{confirm-availability}.
+
+For the confirm service activity, which will be deployed at a later of the network, which solution to adopt will be based on benchmark testing and the development vision of the NuCypher network.
+The ZKP-based solution (the one utilizing bulletproofs) provides several advantages including non-interactivity, as opposed to the committee-attestation one that needs interaction with the committee.
 It also supports computational soundness as opposed to the statistical one of the commit/challenge/open solution.
-Nonetheless, it could be the case that the other solutions are more efficient especially if we incorporate committee attestation or sidechains to support other functionalities in the network.
+Nonetheless, it could be the case that the committee-attestation and the Merkle-tree based solutions are more efficient especially if we incorporate committee attestation or sidechains to support other functionalities in the network.
 
-Another issue pertains to the payment computation.
-During early stages when the network launches, we anticipate  limited adoption and service demand.
-Thus, we reward Ursulas for just being online to encourage adoption.
-While in later stages, payments will be dispensed partially in proportion to the actual number of service requests an Ursula answers.
-This is due to the fact that later on the subsidies will effectively disappear, i.e., the majority of tokens in the network will be minted, and the service fees are the only source of income.
-To incentivize Ursula to provide a correct and timely service, these fees should be computed based on the actual amount of service.
-This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
+Another related issue to confirm activity is the service payment strategy in the network.
+Until now we assume that Alice pays for the service by using the Ether she locks into the policy contract.
+Other arrangement may emerge in the system like having Bob pay for the requests he issues.
+Such an arrangement may have an implication on the confirm activity issue, and studying its impact, if it becomes part of the NuCypher network protocol, will be part pf our future work.

### 2020-08-04 confirm-activity/tex/intro.tex
more reorganizing
merge discussion and future work, and rename

@@
 \setlength{\itemsep}{0pt}
-\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves.
-Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
-
 \item Confirming being online is flawed in the sense that the function call that Ursula makes does not require any input or proofs on providing the service, or even being online and responsive.
@@
 Even worse, Ursula will be able to get her stake back once it unlocks.
+
+\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves.
+Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.
 \end{itemize}
@@
 Then, we present the proposed solutions for confirm availability in Section~\ref{confirm-availability} and those for confirming service activity in Section~\ref{confirm-service-activity}.
-After that, we briefly discuss the trade-offs and requirements of each of these solutions along with some usage recommendations in Section~\ref{discussion}.
-Lastly, in Section~\ref{future-work} we conclude with highlighting some of our future work directions.
+Lastly, we briefly discuss the trade-offs and requirements of each of these solutions along with some usage recommendations and future work directions in Section~\ref{discussion}.

### 2020-08-05 confirm-activity/tex/confirm-service-activity.tex
fix confirm service activity section and finish the document

--- 2020-08-03 confirm-activity/tex/confirm-service-activity.tex
@@
 \label{confirm-service-activity}
-In this section, we present potential solutions for the confirm service activity 
-problem. The goal is to come up with provably secure solutions that allows an 
-Ursula to prove that it has served a given number of distinct re-encryption 
-requests within a given period.
+As discussed previously, for confirm service activity we need secure solutions that allow an Ursula to prove that she has served a given number of distinct re-encryption requests within a given period.
+In particular, for every round an Ursula will need to produce a proof attesting to the statement ``Ursula has served $\omega$ distinct re-encryption requests correctly," for some positive integer $\omega$.
+In this section, we present three solutions to achieve this goal, which we refer to as zero knowledge proof-based (ZKP-based), committee-attestation, and commit/challenge/open-based.
+These solutions differ in their security assumptions, guarantees, proof technique, and efficiency.
+In what follows, we provide the design details of each of them.
 
-The rest of this section discusses the proposed solutions along with an analysis of 
-their security and efficiency aspects. Lastly, the section concludes with directions of 
-future work on the confirm service activity issue.
+\subsection{ZKP-based Scheme}
+In this solution, we utilize the fact that in the NuCypher network each Ursula already produces a ZKP attesting to the correctness of each re-encryption request she performs to be checked by Bob~\cite{umbral2018}.
+Such proofs can be aggregated into a single proof attesting to the statement outlined above.
+This accumulation can be done using two approaches: by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}, or by using a ZKP system for arithmetic circuits.
 
-\subsection{PCD-based Scheme.}
-The main idea here is to adapt the PCD framework so that Ursula
-can combine the correctness proofs she computes for Bobs' requests in a single proof 
-attesting to the following fact: ``Ursula has served $\omega$ distinct re-encryption 
-requests correctly."
-
-Thus, in this setup, there is only one computation party, or prover, namely, Ursula. 
-For each round, where a round could be the time needed to mine a block on the 
-blockchain, Ursula starts with input $x_1$, which is a signed and fresh request
-from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
-proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
-proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
-which is the input for the next step in the computation, Ursula answers 
-this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then 
-it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
-$\hat{\pi}_2$ does not only 
-attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
-two valid distinct requests until now. The same process is repeated until the end of the 
-round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
-served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
-this process pictorially.
+For the generic PCD/IVC approach, we have only one prover or computation party, namely, Ursula.
+For each round, Ursula starts with input $x_1$, which is a signed and fresh re-encryption request from Bob.
+It answers this request with a ciphertext fragment $cFrag_{x_1}$ and produces a correctness proof $\pi_1$ as defined in the Umbral scheme~\cite{umbral2018}.
+Then, when the next request $x_2$ arrives, which is the input for the next step in the computation, Ursula answers this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\pi_1$ to produce $\hat{\pi}_2$.
+$\hat{\pi}_2$ does not only attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served two valid distinct requests until now.
+The same process is repeated until all requests served in a round are covered.
+At the end, Ursula produces a single proof $\hat{\pi}_{\omega}$ along with the number of served requests $\omega$ as the final proof.
+Figure~\ref{pcd-based-sol} depicts this process pictorially.
 
@@
 \centerline{
-\includegraphics[height= 0.7in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
-\caption{PCD-based solution diagram. Ursula starts a round in the idle state. When 
-the first request arrives, Ursula responds to the request and starts composing the 
-proofs as new requests arrive. At the end of the round, Ursula announces the number of 
-served requests and a single proof attesting to its claim to the network. }
+\includegraphics[height= 2.5in, width = 1.0\columnwidth]{figures/pcd-based-sol.pdf}}
+\caption{PCD-based solution diagram.
+Ursula starts a round in the idle state.
+When the first request arrives, Ursula responds to the request and starts composing the proofs as new requests arrive.
+At the end of the round, Ursula informs the network (i.e., verifier) of the number of served requests and a single proof attesting to her claim.
+}
 \label{pcd-based-sol}
@@
 
-The final proof will be processed by the contract that governs Alice's policy. A valid proof 
-allows Ursula to claim fees out of Alice's Ether escrow as a payment for $\omega$ re-encryption  
-requests.
+An alternative, possibly more efficient approach, is to view the statement ``Ursula has served $\omega$ distinct re-encryption requests correctly" as an instance of the arithmetic circuit satisfiability problem and utilize a highly efficient ZKP system, e.g., Bulletproofs~\cite{bunz18}, to prove its correctness in zero knowledge.
+That is, build a circuit that takes the set of correctness proofs of the served requests as well as their number $\omega$ as inputs, and then output 1 if number of correct distinct proofs equals to $\omega$.
+Then, invoke a circuit parser~\cite{bunz18} to convert the circuit into the Bulletproof format, which allow the prover, Ursula in this case, to produce a single proof.
 
-The above is a high level description of the idea. However, more time is need to 
-understand PCD and SNARKs in order to come up with a concrete construction 
-(if possible). Please see Section~\ref{future-work} for more information.
+In both cases, Ursula submits a single proof to the service policy contract.
+Once the proof is verified, the contract disperses the service fee (in proportion to $\omega$) from Alice's locked Ether to Ursula's account.
 
-\subsection{CoSi-based Scheme.}
-This solution utilizes the idea of collective signing by electing a committee 
-that will sign a report submitted by a specific Ursula after verifying that 
-the report supports the claim that ``Ursula has served $\omega$ distinct 
-re-encryption requests correctly."
+\subsection{Committee-Attestation Scheme}
+This solution shares a similar theme to confirm availability solution discussed previously.
+It relies on electing a committee for each round that will endorse Ursula's claim of serving $\omega$ distinct and valid re-encryption requests in a given round.
+The endorsement is done by employing CoSi (see Section~\ref{cosi}) to permit the committee to collectively sign the statement ``Ursula has served $\omega$ distinct re-encryption requests correctly."
 
-At a high level, the scheme works as follows. For each round, a working Ursula keeps 
-a full record of all the requests that she served during the round. These 
-include the signed requests received from Bob(s), and the produced $cFrag$ 
-and the correctness proof $\pi$ (as in the Umbral scheme) for 
-each request. At the end of the round, a committee of $t$ Ursulas is 
-elected, where $t$ is a small integer, e.g., $t = 5$. The working Ursula 
-initiates the CoSi protocol to sign the message $m$ stated above while 
-replacing $\omega$ with the actual number of served 
-requests in the round. This Ursula sends $m$ along with the full report to 
-each member in the committee. Each member Ursula (i.e., member in the 
-elected committee) verifies $m$ by checking the report as follows:
+In detail, for each round, a committee of Ursulas (and possibly outsider verifiers) is elected to attest for the work load an Ursula served.
+At the end of a round, each working Ursula establishes a record of all the requests she served along with their individual correctness proofs and the ciphertext fragments she computed.
+Then, she initiates the CoSi protocol to sign the workload statement above, denoted as $m$, while replacing $\omega$ with the actual number of served requests in the round.
+Ursula sends $m$ along with the full service record to each member of the committee, which in turn verfiies the correctness of the report as follows:
+
 \begin{enumerate}
-\setlength{\itemsep}{0pt}
-\item Check that each request is distinct by checking the sequence 
-number of the request (or any value that is used for freshaness), and valid by verifying Bob's 
-signature over the request. (Here the policy will contain Bob's public 
-key to allow the committee use the right verification key.)
+\item Check that each request is distinct by checking the sequence number/timestamp of the request.
 
-\item Verify the correctness of each $cFrag$ as in the Umbral 
-scheme.
+\item Check that each request is valid by verifying Bob's signature over the request. (Here the policy will contain Bob's public key to allow the committee to use the right verification key.)
 
-\item Check that the value of $\omega$ inside $m$ agrees with the 
-record.
+\item Verify the ZKP correctness proof of each $cFrag$ as in the Umbral scheme.
+
+\item Check that the value of $\omega$ inside $m$ agrees with the record.
 \end{enumerate}
 
-If everything is fine, each member of the committee and the working 
-Ursula finalize the CoSi signing protocol as described in Section~\ref{cosi}. 
-At the end, the working Ursula publishes the collective signature, which can be 
-verified using the accumulated public keys of the cosigning Ursulas.
+If everything is fine, each member of the committee and the working Ursula finalize the CoSi signing protocol and produce one signature over $m$.
+At the end, the working Ursula publishes $m$ and the collective signature to the network, or the service policy contracts, which in turn verifies correctness as described in Section~\ref{cosi}.
 
-\paragraph{On the committee election.} This can be done
-by using some deterministic computation over a block hash and mapping
-the output to Ursulas' public keys. So the selection is not determined by the
-working Ursula to prevent any potential collusion.
+\paragraph{\bf On the committee election.} 
+For each round some reasonable number of Ursulas will be elected by using a similar technique to the ones described in Section~\ref{confirm-availability}, i.e., using the hash iterative process.
 The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance of them controlling the entire committee.
 
-The above scheme works under the assumption that at least one Ursula
-in the elected committee is honest, which pertains to an assumption on the
-least number of honest Ursulas in the network. If the latter assumption is under threat, one mitigating approach is to increase $t$ (the committee size).
+The above scheme works under the assumption that at least one Ursula in the elected committee is honest, which pertains to an assumption on the least number of honest Ursulas in the network.
+If the latter assumption is under threat, one mitigating approach is to increase the committee size.
+Another approach is to have a changing set of external verifiers, like trusted partners, as part of the elected committee.
+As long as there is one honest party in the committee, signing fraudulent records will not succeed since this honest party will not agree to do that.
 
-Another approach is to have a changing set of external verifiers, like
-trusted partners, that all working Ursulas must use for the CoSi signing
-of their records.
+\paragraph{\bf On the public verifiability of the signed records.} 
+Having a valid collective signature from a committee (that has at least one honest member) suffices for the correctness of the signed statement.
+However, it could be better to keep the records that produced the message $m$ available for a while so that any party can verify them (the verifying parties could maintain such a public record for a given period after which the logs can be discarded).
+We can resort to this option just at the beginning to convince the participants of the trustworthiness of the committee or the validity of the assumption that at least one Ursula in the elected committee is honest.
 
-A third approach is to keep the deterministic selection of the committee
-but with an external member, e.g., either a trusted partner verifier
-or a special verifier node deployed and maintained by the NuCypher company.
-Thus, achieving the assumption of at least one member of the elected
-committee is honest.
+\paragraph{\bf On compensating the committee.} 
+Similar to confirm availability, we need a mechanism to ensure that the elected committee is responsive and willing to handle the endorsement work.
+Ideally, this can be pictured as a collaborative work, the committee does the work so that others will do the same when the committee members want their workload to be signed.
+Alternatively, and as mentioned before, the committee can be paid for their work, either by Alice as part of her policy, or by the working Ursulas themselves since they are requesting this endorsement service (however, the latter may complicate the system operation).
 
-\paragraph{On the publicity of the signed records.} Having a 
-valid collective signature from a committee (that has at least one honest 
-member) suffices for the correctness of the signed statement. However, 
-it could be better to keep the records that produced the message $m$  
-available for a while so that any party can verify them (the verifying
-parties could maintain such a public record for a given period after which
-the logs can be discarded).
+\subsection{Commit/Challenge/Open-based Scheme}
+This solution is inspired from the Merkle tree-based ZKP system proposed in~\cite{dottling19}.
+Ursula keeps track of the requests coming from Bob(s) during a time round and assign each of them a unique sequence number.
+That is, Ursula replies with $cFrag$ and the correctness proof.
+At the end of the round, Ursula constructs a Merkle tree of all requests, where the requests (and their replies/correctness proofs) are the leaves of the tree ordered by their sequence numbers (recall that we require Bob to include a sequence number in his request to ensure freshness).
+Ursula signs the root of the tree, denoted as $root$ to produce a signature $\sigma_{root}$
 
-We can resort to this option just at the beginning to convince the 
-participants of the trustworthiness of the committee or the validity of the
-assumption that at least one Ursula in the elected committee is honest.
+To prove correctness of the claimed work amount, Ursula will be challenged to open some leaves in the Merkle tree.
+She uses the $root$ as a random beacon to be fed into an iterative hash process to select $n$ leaf nodes at random to open them (i.e., these are the challenges).
+Ursula provides the challenge leaf nodes along with their membership paths in the tree, along with $(\omega, root, \sigma_{root})$, either to a sidechain (which is maintained by round-elected committee) or to the policy contract to verify.
 
-\paragraph{On compensating the committee.} This solution may 
-raise the question of why would the elected committee (especially if it 
-is composed of other Ursulas in the system) participate in the CoSi 
-process, which also involves verifying the full request record presented 
-by the working Ursula. This can be pictured as a collaborative
-work, the committee does the work so that others will do the same
-when the committee members play the role of working Ursulas.
+The verification process involves verifying Ursula's signature on the $root$, verifying the freshness and correctness of the request in each opened leaf, and verifying the membership path of each of these leaves.
+If everything is fine, Ursula will be paid for serving the claimed $\omega$ request.
 
-Another option is to pay the committee for their work, either as
-part of the inflation rewards, or by having working Ursulas pay for 
-it (however, this may complicate the system operation).
-
-\subsection{Commit/Challenge/Open-based Scheme.}
-This solution utilizes the idea of commit/challenge/open protocols. 
-In details, Ursula keeps track of the requests coming from Bob(s) 
-during a time round and assign each of them a unique sequence 
-number. That is, Ursula replies with $cFrag$ and the correctness proof 
-along with a sequence number showing the order of the request within 
-the batch of requests handled during a round. At the end of the round, 
-Ursula constructs a Merkle tree of all requests, where 
-the requests (and their replies) are the leaves of the tree ordered by the sequence
-numbers. Ursula signs the root of the tree, denoted as $root$ to produce 
-a signature $\sigma_{root}$, then it publishes $(\omega, root, \sigma_{root})$ 
-to the network (recall that $\omega$ is the number of served requests).
-
-To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
-This can be done by having the policy contract select at random (e.g. based
-on the block hash or any other mechanism) the leaf IDs to be opened. If 
-Ursula fails to open them correctly within a predefined timeframe, she loses the 
-whole fee she was supposed to collect for serving $\omega$ requests.
-
-An alternative approach to the challenge/open scheme described above is to 
-have Ursula publish the full Merkle tree on some known public space but
-not on the blockchain, and make the full record available online for a specific period
-to allow anyone to verify the work. If no one files a complaint about the tree (we
-still need to define correctness properties, like checking all Bob public keys are 
-defined in the policy created by Alice, and that the response is valid by checking the 
-proof produced by Umbral), Ursula collects the fees for the provided service. On the other
-hand, a valid complaint or proof-of-cheating costs Ursula the full allocation of fees, or potentially involves slashing her stake.
+It should be noted that the security provided here is statistical, driven by the value of $n$, in the sense that we need to bound the probability by which an Ursula can cheat, such as replicating requests in the tree and adding fabricated ones to increase $\omega$.

### 2020-08-05 confirm-activity/tex/intro.tex
fix confirm service activity section and finish the document

@@
 
-Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity.
+Nonetheless, Ursula has an economic incentive to log her availability and provide a satisfactory level of service.
+If she ``cheats" she will risk devaluing her stake since the network will be less useful to users who will leave and cease paying fees.
+However, we recognize the long-term need for a more intelligent and specialized technique to hold Ursula accountable and prevent her from cheating the system.
 Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient.

### 2020-08-05 confirm-activity/tex/threat-model.tex
fix confirm service activity section and finish the document

@@
-\section{Threat and Network Models}
+\section{Network and Threat Models}
 \label{threat-network-model}
@@
 \begin{itemize}
-\item {\bf Self-interested parties:} We do not place trust in any party and we assume that all participants are 
+\setlength{\itemsep}{5pt}
+\item {\bf Self-interested parties.} We do not place trust in any party and we assume that all participants are 
 self-interested.
@@
 
-\item {\bf Attackers' collusion:} If it is profitable, an Ursula may, for example, spin out her own Alice/Bob instances or collude with Alice or Bob.
+\item {\bf Attackers' collusion.} If it is profitable, an Ursula may, for example, spin out her own Alice/Bob instances or collude with Alice or Bob.
 That is, by creating Alice/Bob instances (or colluding with them), Ursula will receive larger number of policies and re-encryption requests.
@@
 
-\item {\bf Honest Ursulas:} We also assume that when sampling a subset of Ursulas in the network, at least one of them is honest.
+\item {\bf Honest Ursulas.} We also assume that when sampling a subset of Ursulas in the network, at least one of them is honest.
 This assumption can be achieved by having a global assumption regarding the lower bound of the number of honest Ursulas with respect to the total number of Ursulas in the NuCypher network.
@@
 
-\item {\bf Efficient adversaries.}.
-We deal with computationally-bounded (or probabilistic polynomial time) adversaries that cannot break secure cryptographic primitives with non-negligible probability.
+\item {\bf Efficient adversaries.} We deal with computationally-bounded (or probabilistic polynomial time) adversaries that cannot break secure cryptographic primitives with non-negligible probability.
 \end{itemize}
